### 2022-12-15 doc/manuscript.Rmd
Add a skeleton of the pipeline (#2)

---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-targets, include=FALSE}

```

# Introduction

# Methods

# Results

# Discussion

# Conclusion

### 2023-01-24 doc/manuscript.Rmd
Add preliminary analysis

@@
 knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_knit$set(root.dir = "..")
+setwd("..")
+source("R/utils.R")
+source("R/model_builder_RQ1.R")
 ```
@@
 ```{r load-targets, include=FALSE}
+library(targets)
+library(gt)
+require(ggplot2)
+tar_load(model_list)
 
@@
 
+```{r out.width="100%"}
+
+model_list[[1]] |> 
+  plot_effects_RQ1(terms = c("pa_volume", "age_cat")) +
+  facet_grid(cols = vars(group))
+```
+
+## Model tables
+
+```{r results = "asis"}
+
+tables <- lapply(model_list, function(x) x$table)
+sapply(seq_len(length(tables)), function(x){
+
+  cat("## ", names(tables)[x])
+  tables[[x]] |> 
+    gt() |> 
+    apa_style() |> 
+    as_raw_html() |> 
+    cat()
+
+  cat("\\n")
+  cat("\\n")
+})
+
+```
+
 # Discussion

### 2023-01-24 R/clean_data.R

@@ -138,7 +138,7 @@ clean_data <- function(data_joined) {
     mutate(ses = factor(harmonized, levels = c("Low", "Medium", "High"))) %>%
     select(-harmonized)
 
-  d$age_cat <- cut(d$age, breaks = c(0, 18, 35, 65, 100), labels = c("0-18 years", "19-35 years", "36-65 years", "65+ years"))
+  d$age_cat <- cut(d$age, breaks = c(0, 11,  18, 35, 65, 100), labels = c("0-11 years","12-18 years", "19-35 years", "36-65 years", "65+ years"))
 
   d
 

### 2023-01-24 R/make_data_imp.R

@@ -22,7 +22,14 @@ make_data_imp <- function(data, n_imps = 3) {
   pred[, colnames(pred) %in% dont_imp] <- 0
 
   # Run imps with better settings
-  imps <- futuremice(data, m = n_imps, predictorMatrix = pred, method = meth, n.core = parallel::detectCores() - 1)
+  imps <-
+    futuremice(
+      data,
+      m = n_imps,
+      predictorMatrix = pred,
+      method = meth,
+      n.core = parallel::detectCores() - 1
+    )
 
   imps
 }

### 2023-01-24 R/utils.R

@@ -36,3 +36,25 @@ figure_theme <- function(){
       )
 
 }
+
+#' APA_style for gt
+
+apa_style <- function(x) {
+  x |>
+    opt_table_lines(extent = "none")|>
+    tab_options(
+      heading.border.bottom.width = 2,
+      heading.border.bottom.color = "black",
+      heading.border.bottom.style = "solid",
+      heading.title.font.size = 12,
+      table.font.size = 12,
+      heading.subtitle.font.size = 12,
+      table_body.border.bottom.color = "black",
+      table_body.border.bottom.width = 1,
+      table_body.border.bottom.style = "solid",
+      column_labels.border.bottom.color = "black",
+      column_labels.border.bottom.style = "solid",
+      column_labels.border.bottom.width = 1
+    ) |>
+    opt_table_font(font = "times")
+}

### 2023-01-24 packages.R

@@ -15,3 +15,4 @@ library(mice)
 library(data.table)
 library(papaja)
 library(future.apply)
+library(ggeffects)

### 2023-01-24 doc/manuscript.Rmd
make manuscript complete

@@
 knitr::opts_knit$set(root.dir = "..")
-setwd("..")
+#setwd("..")
 source("R/utils.R")

### 2023-01-25 R/clean_data.R
move to mixed model

@@ -138,9 +138,8 @@ clean_data <- function(data_joined) {
 
   # removing some variables we can't harmonise
   d <- d %>% select(-sleep_medications,
-  -ethnicity,
-  -maturational_status) %>%
-    dplyr::rename(ethnicity = ethinicity)
+  -ethinicity,
+  -maturational_status)
 
   # Clean the country names
   d <- d %>% mutate(country = str_to_title(country),
@@ -153,7 +152,7 @@ clean_data <- function(data_joined) {
     country == "Czechia" ~ "Czech Republic",
     TRUE ~ country
   ))
-  
+
   d$city[d$studyid == 105] <- "Prague"
   d$city[d$studyid == 117] <- "Madrid"
   d$country[d$studyid == 117] <- "Spain"
@@ -188,7 +187,7 @@ clean_data <- function(data_joined) {
 
   unique(d$studyid[is.na(d$city)])
   unique(d$studyid[is.na(d$country)])
-  
+
   d <- d %>% mutate(country = as.factor(country),
                     location = paste(city, country, sep = ", "))
 
@@ -210,13 +209,13 @@ clean_data <- function(data_joined) {
                     getSunlightTimes(data = .,
                                     keep = c("sunrise", "sunset"))
   sunlight$daylight_hours <- sunlight$sunset - sunlight$sunrise
-  d <- d %>% left_join(distinct(sunlight), 
+  d <- d %>% left_join(distinct(sunlight),
                     by = c("calendar_date" = "date",
                     "lat", "lon"))
   d$season <- mapply(get_season, date = d$calendar_date, lat = d$lat)
   d <- d %>% mutate(daylight_hours = as.numeric(daylight_hours)) %>%
   select(-lat, -lon, -sunrise, -sunset, -location)
-  
+
   # remove 106 hours because it could be anywhere in Aus
   d$daylight_hours[d$studyid == 106] <- NA
 

### 2023-01-25 R/make_model_list.R

@@ -16,7 +16,7 @@ make_model_list <- function(data_imp) {
 
   PA_vars <- c("pa_volume", "pa_intensity")
 
-  control_vars <- c("ethnicity", "ses", "sex", "bmi")
+  control_vars <- c("ethnicity","ses", "sex", "bmi")
 
   instructions <- list(
     "sleep_duration" = c("pa_volume * age + I(pa_volume^2) * age"),

### 2023-01-25 R/model_builder_RQ1.R

@@ -14,7 +14,7 @@ model_builder_RQ1 <-
   function(data_imp,
            outcome,
            predictors,
-           control_vars = c(),
+           control_vars = c("ses", "sex", "scale(bmi)"),
            table_only = TRUE) {
 
     formula <-
@@ -51,7 +51,7 @@ model_builder_RQ1 <-
           i = i + 1
       }
 
-      if(!conv) warning("No convergence with any optimizer")
+      if(!conv) stop("No convergence with any optimizer:" , cat(...))
 
       mod
     }

### 2023-01-25 packages.R

@@ -19,7 +19,9 @@ library(ggeffects)
 library(gt)
 library(gtsummary)
 library(languageserver)
-library(glmmTMB)
+library(optimx)
+library(lme4)
+library(dfoptim)
 library(broom.mixed)
 library(lubridate)
 library(suncalc)

### 2023-01-27 R/make_data_imp.R
add figures for RQ1

@@ -31,5 +31,26 @@ make_data_imp <- function(data, n_imps = 3) {
       n.core = parallel::detectCores() - 1
     )
 
-  imps
+  # include_scale_variables
+
+  variables_to_scale <-
+    c(
+      "sleep_duration",
+      "sleep_efficiency",
+      "sleep_onset",
+      "sleep_regularity",
+      "pa_volume",
+      "pa_intensity"
+    )
+  scale_names <- paste0("scale_", variables_to_scale)
+
+  imp_list <- data.table(complete(imps, action = "long", include = TRUE))
+
+  for(v in seq_along(variables_to_scale)) {
+    imp_list[, (eval(scale_names[v])) := as.numeric(scale(eval(parse(text = variables_to_scale[v])))), by = ".imp"]
+
+  }
+
+  as.mids(imp_list)
+
 }

### 2023-01-27 R/make_model_list.R

@@ -9,27 +9,22 @@
 #' @export
 make_model_list <- function(data_imp) {
 
-  sleep_vars <- c("sleep_duration",
-                  "sleep_efficiency",
-                  "sleep_onset",
-                  "sleep_regularity")
 
   PA_vars <- c("pa_volume", "pa_intensity")
 
   control_vars <- c("ses", "sex", "bmi")
 
-
   instructions.rq1 <-
     expand.grid(
       sleep_measure = c(
-        "sleep_duration",
-        "sleep_efficiency",
-        "sleep_onset",
-        "sleep_regularity"
+        "scale_sleep_duration",
+        "scale_sleep_efficiency",
+        "scale_sleep_onset",
+        "scale_sleep_regularity"
       ),
       exercise = c(
-        "pa_volume * age + I(pa_volume^2) * age",
-        "pa_intensity * age + I(pa_intensity^2) * age"
+        "scale_pa_volume * age + I(scale_pa_volume^2) * age",
+        "scale_pa_intensity * age + I(scale_pa_intensity^2) * age"
       ),
       stringsAsFactors = FALSE
     )
@@ -39,13 +34,16 @@ make_model_list <- function(data_imp) {
   out <- lapply(
     seq_len(length(instructions.rq1[,1])),
     FUN = function(i) {
-      model_builder_RQ1(
+    model <-  model_builder_RQ1(
         data_imp,
         outcome = instructions.rq1[i, 1],
-        predictors = instructions.rq1[i,2],
+        predictors = instructions.rq1[i, 2],
         control_vars = control_vars,
         table_only = FALSE
       )
+
+    attr(model, "terms") <- c(paste0(gsub(" .*", "" ,instructions.rq1[i, 2]), "[-4:4 by = 0.1]"), "age [11, 18, 35, 65]")
+    model
 
     }
   )

### 2023-01-27 R/model_builder_RQ1.R

@@ -109,24 +109,26 @@ model_builder_RQ1 <-
 
   }
 
-#' plot_effects_RQ1
+#' get_effects_RQ1
 #'
 #' Plot an effects display for a RQ1 model
 #' @param model a list delivered by model_builder_RQ1
 #' @param terms character. variables to plot
 #' @param engine ggeffects function
-#' @param return_data if TRUE only data is returned
+#' @param plot if TRUE plot is returned
+#' @param ... additional arguments passed to the ggeffect engine
 #' @example model = rq1_example_model, terms = c("pa_intensity", "pa_volume")
 
-plot_effects_RQ1 <- function(model, terms, engine = ggeffects::ggpredict, return_data = FALSE){
+get_effects_RQ1 <- function(model, terms, engine = ggeffects::ggpredict, plot = FALSE,
+                            ...){
 
-  effects <- model$model |>
-    lapply(function(m) {
-      engine(m, terms = terms)
+  effects <-
+    lapply(seq_len(length(model$model)), function(i) {
+      engine(model$model[[i]], terms = attr(model, "terms"), ...)
     }) |>
     ggeffects::pool_predictions()
 
-  if (return_data)
+  if (!plot)
     return(effects)
   effects |>
     plot() +

### 2023-01-27 R/produce_purdy_pictures.R

@@ -7,8 +7,9 @@
 #' @return
 #' @author conig
 #' @export
-produce_purdy_pictures <- function(model) {
+produce_purdy_pictures <- function(model_list) {
 
   NULL
 
 }
+

### 2023-01-27 _targets.R

@@ -32,6 +32,7 @@ list(
 
   # Figures
   tar_target(explore_img, make_explore_img_list(data_holdout)),
+  tar_target(RQ1_figure, make_RQ1_figure(model_list)),
 
   tar_target(purdy_pictures, produce_purdy_pictures()),
 

### 2023-01-27 packages.R

@@ -12,6 +12,8 @@ library(targets)
 library(tidyverse)
 library(chron)
 library(mice)
+library(miceadds)
+library(TAM)
 library(data.table)
 library(papaja)
 library(future.apply)

### 2023-01-27 R/clean_data.R
include RQ3 in outputs

@@ -143,7 +143,6 @@ clean_data <- function(data_joined) {
 
   # removing some variables we can't harmonise
   d <- d %>% select(-sleep_medications,
-  -ethinicity,
   -maturational_status)
 
   # Clean the country names

### 2023-01-27 R/make_RQ1_figure.R

@@ -12,6 +12,7 @@ make_RQ1_figure <- function(model_list){
     dt$x_name = terms[1]
     dt$group_name = terms[2]
     dt$outcome = gsub(" .*","",names(model_list)[[i]])
+    dt$RQ <- attr(m, "RQ")
     dt
 
   })
@@ -28,8 +29,8 @@ make_RQ1_figure <- function(model_list){
 
   require(ggplot2)
 
-  p <- function(x_var, x_lab){
-  fig <- ggplot(plot_dat[x_name == x_var], aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
+  p <- function(x_var, x_lab, rq){
+  fig <- ggplot(plot_dat[x_name == x_var & RQ == rq], aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
     geom_line() +
     geom_ribbon(alpha = .5) +
     facet_grid(rows = vars(outcome), cols = vars(group)) +
@@ -45,9 +46,16 @@ make_RQ1_figure <- function(model_list){
 
   }
 
+  # Research Question 1
+  p("pa_intensity", "PA intensity (z)", rq = 1)
+  p("pa_volume", "PA volume (z)", rq = 1)
 
-  p("pa_intensity", "PA intensity (z)")
-  p("pa_volume", "PA volume (z)")
+  # Research Question 3
+  # p("scale_sleep_duration_lag", "Sleep duration (z)", rq = 3)
+  # p("scale_sleep_efficiency_lag", "Sleep efficiency (z)", rq = 3)
+  # p("scale_sleep_onset_lag", "Sleep onset (z)", rq = 3)
+  # p("scale_sleep_regularity_lag", "Sleep regularity (z)", rq = 3)
+
   NULL
 
 }

### 2023-01-27 R/make_data_imp.R

@@ -32,16 +32,19 @@ make_data_imp <- function(data, n_imps = 3) {
     )
 
   # include_scale_variables
+  sleep_vars <- c("sleep_duration",
+                  "sleep_efficiency",
+                  "sleep_onset",
+                  "sleep_regularity")
+
 
   variables_to_scale <-
-    c(
-      "sleep_duration",
-      "sleep_efficiency",
-      "sleep_onset",
-      "sleep_regularity",
+    c(sleep_vars,
       "pa_volume",
-      "pa_intensity"
+      "pa_intensity",
+      paste0(sleep_vars, "_lag")
     )
+
   scale_names <- paste0("scale_", variables_to_scale)
 
   imp_list <- data.table(complete(imps, action = "long", include = TRUE))

### 2023-01-27 R/make_model_list.R

@@ -9,45 +9,58 @@
 #' @export
 make_model_list <- function(data_imp) {
 
+  sleep_vars <- c("scale_sleep_duration",
+                    "scale_sleep_efficiency",
+                    "scale_sleep_onset",
+                    "scale_sleep_regularity")
 
-  PA_vars <- c("pa_volume", "pa_intensity")
+  sleep_lag_vars <- paste0(sleep_vars, "_lag")
+
+  PA_vars <- c("scale_pa_volume", "scale_pa_intensity")
 
   control_vars <- c("ses", "sex", "bmi")
 
+  make_quadratic <- function(x) glue::glue("{x} * age + I({x}^2) * age")
+
   instructions.rq1 <-
     expand.grid(
-      sleep_measure = c(
-        "scale_sleep_duration",
-        "scale_sleep_efficiency",
-        "scale_sleep_onset",
-        "scale_sleep_regularity"
-      ),
-      exercise = c(
-        "scale_pa_volume * age + I(scale_pa_volume^2) * age",
-        "scale_pa_intensity * age + I(scale_pa_intensity^2) * age"
-      ),
+      outcome = sleep_vars,
+      predictors = make_quadratic(PA_vars),
+      RQ = 1,
       stringsAsFactors = FALSE
     )
 
-  instructions.rq1$model_name <- with(instructions.rq1, glue::glue("{sleep_measure} by {gsub(' .*', '', exercise)}"))
+
+  instructions.rq3 <-
+    expand.grid(
+      outcome = PA_vars,
+      predictors = make_quadratic(sleep_lag_vars),
+      RQ = 3,
+      stringsAsFactors = FALSE
+    )
+
+  instructions <- rbind(instructions.rq1, instructions.rq3)
+
+  instructions$model_name <- with(instructions, glue::glue("{outcome} by {gsub(' .*', '', predictors)}"))
 
   out <- lapply(
-    seq_len(length(instructions.rq1[,1])),
+    seq_len(length(instructions[,1])),
     FUN = function(i) {
     model <-  model_builder_RQ1(
         data_imp,
-        outcome = instructions.rq1[i, 1],
-        predictors = instructions.rq1[i, 2],
+        outcome = instructions[i, "outcome"],
+        predictors = instructions[i, "predictors"],
         control_vars = control_vars,
         table_only = FALSE
       )
 
[…]

### 2023-01-27 doc/manuscript.Rmd
move to mixed model
add figures for RQ1
include RQ3 in outputs
clean up, appease mike

--- 2022-12-15 doc/manuscript.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_knit$set(root.dir = "..")
+#setwd("..")
+source("R/utils.R")
+source("R/model_builder_RQ1.R")
+```
+```{r load-libraries}
+library(targets)
+library(gt)
+require(ggplot2)
+library(papaja)
 ```
@@
 ```{r load-targets, include=FALSE}
+tar_load(model_list)
+tar_load(data_clean)
+pretty <- function(x) format(x, big.mark = ",")
+```
+
+# Results
+
+The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
+Table \@ref(demo) shows demographic information.
+A table of study characteristics can be found in supplementary materials.
+
+## The effects of physical activity on sleep
+
+We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity and age
+
+## Model tables
+
+```{r results = "asis"}
+
+tables <- lapply(model_list, function(x) x$table)
+sapply(seq_len(length(tables)), function(x){
+
+  cat("## ", names(tables)[x])
+  tables[[x]] |> 
+    gt() |> 
+    apa_style() |> 
+    as_raw_html() |> 
+    cat()
+
+  cat("\\n")
+  cat("\\n")
+})
 
 ```
-
-# Introduction
-
-# Methods
-
-# Results
 

### 2023-01-27 R/make_RQ1_figure.R

@@ -1,14 +1,14 @@
-#' make_RQ1_figure
+#' make_figures
 #' @param model_list list of RQ1 models
 
-make_RQ1_figure <- function(model_list){
+produce_purdy_pictures <- function(model_list){
 
   dat_list <- lapply(seq_len(length(model_list)), function(i){
 
     m <- model_list[[i]]
     terms <- attr(m, "terms")
 
-    dt <- data.table(get_effects_RQ1(m, terms = terms))
+    dt <- data.table(get_effects(m, terms = terms))
     dt$x_name = terms[1]
     dt$group_name = terms[2]
     dt$outcome = gsub(" .*","",names(model_list)[[i]])

### 2023-01-27 R/make_model_list.R

@@ -45,7 +45,7 @@ make_model_list <- function(data_imp) {
   out <- lapply(
     seq_len(length(instructions[,1])),
     FUN = function(i) {
-    model <-  model_builder_RQ1(
+    model <-  model_builder(
         data_imp,
         outcome = instructions[i, "outcome"],
         predictors = instructions[i, "predictors"],

### 2023-01-27 R/produce_purdy_pictures.R

@@ -1,15 +1,72 @@
-#' .. content for \description{} (no empty lines) ..
-#'
-#' .. content for \details{} ..
-#'
-#' @title
+#' produce_purdy_pictures
+#' @param model_list list of RQ1 models
 
-#' @return
-#' @author conig
-#' @export
-produce_purdy_pictures <- function(model_list) {
+produce_purdy_pictures <- function(model_list){
+
+  dat_list <- lapply(seq_len(length(model_list)), function(i){
+
+    m <- model_list[[i]]
+    terms <- attr(m, "terms")
+
+    dt <- data.table(get_effects(m, terms = terms))
+    dt$x_name = terms[1]
+    dt$group_name = terms[2]
+    dt$outcome = gsub(" .*","",names(model_list)[[i]])
+    dt$RQ <- attr(m, "RQ")
+    dt
+
+  })
+
+  plot_dat <- data.table::rbindlist(dat_list)
+  plot_dat$x_name <- gsub("scale_","",plot_dat$x_name)
+  plot_dat$outcome <- gsub("scale_", "", plot_dat$outcome) |>
+    gsub("_", " ", x = _) |>
+    stringr::str_to_title() |>
+    paste("(z)")
+  plot_dat$group <- paste(plot_dat$group, "years")
+  plot_dat$x_name <- gsub("\\[.*","", plot_dat$x_name)
+
+
+  require(ggplot2)
+
+  p <- function(x_var, x_lab, rq){
+    pdat <- plot_dat[x_name == x_var & RQ == rq]
+
+  fig <- ggplot(pdat, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
+    geom_line() +
+    geom_ribbon(alpha = .5) +
+    facet_grid(rows = vars(outcome), cols = vars(group)) +
+      labs(x = x_lab,
+           fill = "Age") +
+      figure_theme() +
+    theme(legend.position = "none")
+
+    outcome <- unique(gsub(" .*","", pdat$outcome))
+    if(length(outcome) > 1) stop("Outcome length is greater than 1")
+
+    filename <- "Figures/{outcome} on {x_var}.jpg" |>
+      glue::glue()
+
+    if(outcome == "Sleep"){
+      height = 15
+    } else{
+      height = 9
+    }
+
[…]

### 2023-01-30 doc/manuscript.Rmd

@@
 ---
-title: "Untitled Draft"
-author: "Report Author"
-date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: html_document
+title             : "The title"
+shorttitle        : "Title"
+
+author: 
+  - name          : "First Author"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "my@email.com"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - "Conceptualization"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Ernst-August Doelle"
+    affiliation   : "1,2"
+    role:
+      - "Writing - Review & Editing"
+      - "Supervision"
+
+affiliation:
+  - id            : "1"
+    institution   : "Wilhelm-Wundt-University"
+  - id            : "2"
+    institution   : "Konstanz Business School"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
+wordcount         : "X"
+
+floatsintext      : no
+linenumbers       : yes
+draft             : no
+mask              : no
+
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+
+classoption       : "man"
+output            : papaja::apa6_docx
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_knit$set(root.dir = "..")
 #setwd("..")
 source("R/utils.R")
-source("R/model_builder_RQ1.R")
 ```
+
 ```{r load-libraries}
@@
 
-We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity and age
+We explored the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effect of physical activity on sleep by age.
+The results are presented in Tables \@ref(tab:sleep-by-volume)
 
-## Model tables
+```{r sleep-by-volume}
+note <- "Adjusted for SES, BMI, and sex. "
 
-```{r results = "asis"}
+format_table <- function(tab){
+  tab$term <- gsub("I\\(","", tab$term) |> 
+    gsub("_", " ", x = _) |> 
+    gsub("\\^2\\)","$^2$", x = _)
+  tab
+}
 
-tables <- lapply(model_list, function(x) x$table)
-sapply(seq_len(length(tables)), function(x){
-
-  cat("## ", names(tables)[x])
-  tables[[x]] |> 
-    gt() |> 
-    apa_style() |> 
-    as_raw_html() |> 
-    cat()
-
-  cat("\\n")
-  cat("\\n")
-})
+model_list$`scale_sleep_duration by scale_pa_volume`$table |> 
+  format_table() |> 
+  papaja::apa_table(caption = "The quadratic effect of physical activity (volume) on sleep duration by age",
+                    note = note,
+                    escape = FALSE)
 
 ```
-
-# Discussion
-
-# Conclusion

### 2023-03-14 doc/manuscript.Rmd
Add table and figure for PA volume on sleep

@@
 classoption       : "man"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
-#setwd("..")
 source("R/utils.R")
+options(warn = -1)
 ```
@@
 
-## The effects of physical activity on sleep
+## The effects of physical activity volume on sleep
 
 We explored the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity on sleep by age.
-The results are presented in Tables \@ref(tab:sleep-by-volume)
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-by-volume) and Figure \@ref(fig:sleep-by-volume-fig).
+There was no meaningful relationship between physical activity volume and sleep duration.
+However, a positive curvilinear relationship was observed between physical activity volume and sleep efficiency, onset, and regularity, which interacted with age.
+Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
+Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
+There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
+For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.
 
-```{r sleep-by-volume}
+\renewcommand{\arraystretch}{0.8}
+
+```{r sleep-by-exercise}
 note <- "Adjusted for SES, BMI, and sex. "
@@
 
-model_list$`scale_sleep_duration by scale_pa_volume`$table |> 
-  format_table() |> 
-  papaja::apa_table(caption = "The quadratic effect of physical activity (volume) on sleep duration by age",
+sleep_names <- c("scale_sleep_duration by scale_pa_volume", "scale_sleep_efficiency by scale_pa_volume", 
+"scale_sleep_onset by scale_pa_volume", "scale_sleep_regularity by scale_pa_volume")
+
+sleep_outcomes <- lapply(model_list[sleep_names], function(x){
+tab <- format_table(x$table)  
+# Remove BMI, sex and ses from table
+tab <- tab[!grepl("^ses", tab$term),]
+tab <- tab[!grepl("^sex", tab$term),]
+tab <- tab[!grepl("^bmi", tab$term),]
+tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
+tab$term <- stringr::str_to_sentence(tab$term)
+names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
+tab
+})
+names(sleep_outcomes) <- gsub("scale_", "", names(sleep_outcomes)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  stringr::str_to_sentence()
+
+  papaja::apa_table(sleep_outcomes,
+                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
                     note = note,
                     escape = FALSE)
+```
+
+```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
+knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)
 

### 2023-03-14 doc/manuscript.tex
Add table and figure for PA volume on sleep

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The title}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\shorttitle{Title}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing, Supervision.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{%
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{results}{%
\section{Results}\label{results}}

The aggregated data-set describes 316,835 observations of daily physical activity and sleep from 24,935 unique participants. Table \ref{demo} shows demographic information. A table of study characteristics can be found in supplementary materials.

\hypertarget{the-effects-of-physical-activity-volume-on-sleep}{%
\subsection{The effects of physical activity volume on sleep}\label{the-effects-of-physical-activity-volume-on-sleep}}

We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \ref{tab:sleep-by-volume} and Figure \ref{fig:sleep-by-volume-fig}. There was no meaningful relationship between physical activity volume and sleep duration. However, a positive curvilinear relationship was observed between physical activity volume and sleep efficiency, onset, and regularity, which interacted with age. Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals. Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity. There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants. For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.

\renewcommand{\arraystretch}{0.8}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:sleep-by-exercise}Sleep on physical activity volume controlling for SES, gender and BMI}

\begin{tabular}{lllll}
\toprule
Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
\midrule
Sleep duration &  &  &  & \\
\ \ \ (Intercept) & -0.37 [-0.94, 0.20] & 0.29 & -1.28 & .291\\
\ \ \ Scale  pa  volume & 0.03 [0.00, 0.07] & 0.02 & 1.96 & .050\\
\ \ \ Age & 0.00 [-0.01, 0.00] & 0.00 & -0.29 & .797\\
\ \ \ Scale  pa  volume$^2$ & 0.00 [-0.01, 0.01] & 0.00 & 0.11 & .912\\
\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.92 & .359\\
\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.94 & .349\\
Sleep efficiency &  &  &  & \\
\ \ \ (Intercept) & -0.90 [-1.29, -0.50] & 0.20 & -4.46 & .001\\
\ \ \ Scale  pa  volume & 0.23 [0.20, 0.27] & 0.02 & 12.97 & < .001\\
\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 9.99 & .002\\
\ \ \ Scale  pa  volume$^2$ & -0.02 [-0.03, -0.01] & 0.00 & -4.77 & < .001\\
\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -5.16 & < .001\\
\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.50 & .617\\
Sleep onset &  &  &  & \\
\ \ \ (Intercept) & -0.98 [-1.50, -0.47] & 0.26 & -3.77 & .060\\
\ \ \ Scale  pa  volume & 0.11 [0.09, 0.14] & 0.01 & 8.32 & < .001\\
\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.81 & .007\\
\ \ \ Scale  pa  volume$^2$ & -0.01 [-0.02, -0.01] & 0.00 & -4.73 & < .001\\
\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -8.70 & < .001\\
\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.34 & .034\\
Sleep regularity &  &  &  & \\
\ \ \ (Intercept) & -0.13 [-0.39, 0.13] & 0.13 & -0.96 & .415\\
\ \ \ Scale  pa  volume & 0.33 [0.29, 0.36] & 0.02 & 19.10 & < .001\\
\ \ \ Age & 0.01 [0.00, 0.01] & 0.00 & 5.07 & .019\\
\ \ \ Scale  pa  volume$^2$ & -0.03 [-0.03, -0.02] & 0.00 & -5.74 & < .001\\
\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.64 & .540\\
\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -3.33 & .006\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}
\includegraphics[width=7.08in]{../Figures/sleep on pa_volume} \caption{Sleep metrics on Physical activity volume}\label{fig:sleep-by-volume-fig}
\end{figure}

\end{document}

### 2023-03-14 R/fetch_data.R

@@ -33,6 +33,7 @@ fetch_data <- function(cloudstor_user = Sys.getenv("CLOUD_USER"),
                          "221 Whitehall/221_Whitehall.csv"
                        ),
                        shared = FALSE) {
+  message("Remember to first connect to the VPN. Sometimes you first need to log into cloudstor to warm up the API")
   if(shared){
     base_folder <- paste0("Shared/", base_folder)
   message(base_folder)
@@ -56,3 +57,4 @@ fetch_data <- function(cloudstor_user = Sys.getenv("CLOUD_USER"),
 
   invisible(downloaded_files)
 }
+

### 2023-03-14 doc/manuscript.Rmd
Fix tag for table 1
Prepare to apply tabulation to other outcomes.

@@
 
-\renewcommand{\arraystretch}{0.8}
+\renewcommand{\arraystretch}{0.7}
 
-```{r sleep-by-exercise}
+```{r sleep-by-volume}
 note <- "Adjusted for SES, BMI, and sex. "
 
-format_table <- function(tab){
-  tab$term <- gsub("I\\(","", tab$term) |> 
+format_table <- function(tab) {
+  tab$term <- gsub("I\\(", "", tab$term) |>
     gsub("_", " ", x = _) |>
-    gsub("\\^2\\)","$^2$", x = _)
+    gsub("\\^2\\)", "$^2$", x = _ )
+  tab <- tab[!grepl("^ses", tab$term), ]
+  tab <- tab[!grepl("^sex", tab$term), ]
+  tab <- tab[!grepl("^bmi", tab$term), ]
+  tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
+  tab$term <- stringr::str_to_sentence(tab$term)
+  names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
   tab
@@
 
-sleep_outcomes <- lapply(model_list[sleep_names], function(x){
+sleep_outcomes_by_PA <- lapply(model_list[sleep_names], function(x){
 tab <- format_table(x$table)  
-# Remove BMI, sex and ses from table
-tab <- tab[!grepl("^ses", tab$term),]
-tab <- tab[!grepl("^sex", tab$term),]
-tab <- tab[!grepl("^bmi", tab$term),]
-tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
-tab$term <- stringr::str_to_sentence(tab$term)
-names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
 tab
 })
-names(sleep_outcomes) <- gsub("scale_", "", names(sleep_outcomes)) |> 
+
+names(sleep_outcomes_by_PA) <- gsub("scale_", "", names(sleep_outcomes_by_PA)) |> 
   gsub("\\sby.*", "", x = _ ) |> 
@@
 
-  papaja::apa_table(sleep_outcomes,
+  papaja::apa_table(sleep_outcomes_by_PA,
                     caption = "Sleep on physical activity volume controlling for SES, gender and BMI",

### 2023-03-14 doc/manuscript.Rmd
Add PA intensity models

@@
 
-sleep_outcomes_by_PA <- lapply(model_list[sleep_names], function(x){
+sleep_outcomes_by_PA_volume <- lapply(model_list[sleep_names], function(x){
 tab <- format_table(x$table)  
@@
 
-names(sleep_outcomes_by_PA) <- gsub("scale_", "", names(sleep_outcomes_by_PA)) |> 
+names(sleep_outcomes_by_PA_volume) <- gsub("scale_", "", names(sleep_outcomes_by_PA_volume)) |> 
   gsub("\\sby.*", "", x = _ ) |> 
@@
 
-  papaja::apa_table(sleep_outcomes_by_PA,
+  papaja::apa_table(sleep_outcomes_by_PA_volume,
                     caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
@@
 knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)
+```
 
+## The effects of physical activty intensity on sleep
+
+```{r sleep-by-intensity}
+sleep_names <- c("scale_sleep_duration by scale_pa_intensity", "scale_sleep_efficiency by scale_pa_intensity", 
+"scale_sleep_onset by scale_pa_intensity", "scale_sleep_regularity by scale_pa_intensity")
+
+sleep_outcomes_by_PA_intens <- lapply(model_list[sleep_names], function(x){
+tab <- format_table(x$table)  
+tab
+})
+
+names(sleep_outcomes_by_PA_intens) <- gsub("scale_", "", names(sleep_outcomes_by_PA_intens)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  stringr::str_to_sentence()
+
+  papaja::apa_table(sleep_outcomes_by_PA_intens,
+                    caption = "Sleep on physical activity intensity controlling for SES, gender and BMI",
+                    note = note,
+                    escape = FALSE)
 ```
+
+```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
+knitr::include_graphics(here::here("Figures/sleep on pa_intensity.jpg"), error = FALSE)
+```

### 2023-03-14 doc/manuscript.tex
Fix tag for table 1
Prepare to apply tabulation to other outcomes.
Add PA intensity models

@@
 
-\renewcommand{\arraystretch}{0.8}
+\renewcommand{\arraystretch}{0.7}
 
@@
 
-\caption{\label{tab:sleep-by-exercise}Sleep on physical activity volume controlling for SES, gender and BMI}
+\caption{\label{tab:sleep-by-volume}Sleep on physical activity volume controlling for SES, gender and BMI}
 
@@
 
+\hypertarget{the-effects-of-physical-activty-intensity-on-sleep}{%
+\subsection{The effects of physical activty intensity on sleep}\label{the-effects-of-physical-activty-intensity-on-sleep}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sleep-by-intensity}Sleep on physical activity intensity controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+Sleep duration &  &  &  & \\
+\ \ \ (Intercept) & -0.41 [-0.97, 0.15] & 0.28 & -1.44 & .243\\
+\ \ \ Scale  pa  intensity & 0.09 [0.04, 0.13] & 0.02 & 3.60 & .001\\
+\ \ \ Age & 0.00 [0.00, 0.00] & 0.00 & 0.14 & .900\\
+\ \ \ Scale  pa  intensity$^2$ & -0.01 [-0.03, 0.02] & 0.01 & -0.61 & .542\\
+\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.43 & .165\\
+\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.52 & .604\\
+Sleep efficiency &  &  &  & \\
+\ \ \ (Intercept) & -1.00 [-1.41, -0.60] & 0.21 & -4.87 & < .001\\
+\ \ \ Scale  pa  intensity & 0.13 [0.04, 0.22] & 0.05 & 2.75 & .062\\
+\ \ \ Age & 0.01 [0.01, 0.02] & 0.00 & 10.22 & .002\\
+\ \ \ Scale  pa  intensity$^2$ & 0.01 [-0.02, 0.04] & 0.01 & 0.78 & .436\\
+\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.95 & .113\\
+\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.71 & .088\\
+Sleep onset &  &  &  & \\
+\ \ \ (Intercept) & -0.96 [-1.49, -0.44] & 0.27 & -3.60 & .065\\
+\ \ \ Scale  pa  intensity & -0.04 [-0.07, -0.01] & 0.02 & -2.46 & .015\\
+\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.64 & .007\\
+\ \ \ Scale  pa  intensity$^2$ & 0.00 [-0.02, 0.02] & 0.01 & 0.38 & .703\\
+\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -0.37 & .714\\
+\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 1.51 & .143\\
+Sleep regularity &  &  &  & \\
+\ \ \ (Intercept) & -0.24 [-0.47, -0.02] & 0.11 & -2.09 & .123\\
+\ \ \ Scale  pa  intensity & 0.30 [0.25, 0.34] & 0.02 & 13.30 & < .001\\
+\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 6.88 & .004\\
+\ \ \ Scale  pa  intensity$^2$ & -0.05 [-0.07, -0.02] & 0.01 & -3.48 & .001\\
+\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -6.20 & < .001\\
+\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.33 & .743\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
+\end{figure}
+
 \end{document}

### 2023-03-14 doc/manuscript.Rmd
Add all tables and figures.

@@
   tab <- tab[!grepl("^bmi", tab$term), ]
-  tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
   tab$term <- stringr::str_to_sentence(tab$term)
+  tab$term <- gsub(" pa ", " PA ", tab$term)
   names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
   tab
+}
+
+fix_model_names <- function(x){
+  x <- stringr::str_to_sentence(x)
+  x <- gsub("Pa", "PA", x)
+  x
 }
@@
   gsub("_", " ", x = _ ) |> 
-  stringr::str_to_sentence()
+  fix_model_names()
 
@@
 ```
+
+## The effects of sleep duration on physical activity
+
+```{r PA-by-sleep-duration}
+var_names <- c(
+  "scale_pa_volume by scale_sleep_duration_lag",
+  "scale_pa_intensity by scale_sleep_duration_lag"
+)
+
+PA_by_sleep_duration <- lapply(model_list[var_names], function(x){
+tab <- format_table(x$table)  
+tab
+})
+
+names(PA_by_sleep_duration) <- gsub("scale_", "", names(PA_by_sleep_duration)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  fix_model_names()
+
+  papaja::apa_table(PA_by_sleep_duration,
+                    caption = "Physical activity  by sleep duration controlling for SES, gender and BMI",
+                    note = note,
+                    escape = FALSE)
+```
+
+```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
+knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag.jpg"), error = FALSE)
+```
+
+## The effects of sleep efficiency on physical activity
+
+```{r PA-by-sleep-efficiency}
+var_names <- c(
+  "scale_pa_volume by scale_sleep_efficiency_lag",
+  "scale_pa_intensity by scale_sleep_efficiency_lag"
+)
+
+PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x){
+tab <- format_table(x$table)  
+tab
+})
+
+names(PA_by_sleep_efficiency) <- gsub("scale_", "", names(PA_by_sleep_efficiency)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  fix_model_names()
+
+  papaja::apa_table(PA_by_sleep_efficiency,
+                    caption = "Physical activity by sleep efficiency controlling for SES, gender and BMI",
+                    note = note,
+                    escape = FALSE)
+```
+
+```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
+knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag.jpg"), error = FALSE)
+```
+
+## The effects of sleep onset on physical activity
+
+```{r PA-by-sleep-onset}
+var_names <- c(
+  "scale_pa_volume by scale_sleep_onset_lag",
+  "scale_pa_intensity by scale_sleep_onset_lag"
+)
+
+PA_by_sleep_onset <- lapply(model_list[var_names], function(x){
+tab <- format_table(x$table)  
+tab
+})
+
+names(PA_by_sleep_onset) <- gsub("scale_", "", names(PA_by_sleep_onset)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  fix_model_names()
+
+  papaja::apa_table(PA_by_sleep_onset,
+                    caption = "Physical activity by sleep onset controlling for SES, gender and BMI",
+                    note = note,
+                    escape = FALSE)
+```
+
+```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
+knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag.jpg"), error = FALSE)
+```
+
+## The effects of sleep regularity on physical activity
+
+```{r PA-by-sleep-regularity}
+var_names <- c(
+  "scale_pa_volume by scale_sleep_regularity_lag",
+  "scale_pa_intensity by scale_sleep_regularity_lag"
+)
+
+PA_by_sleep_regularity <- lapply(model_list[var_names], function(x){
+tab <- format_table(x$table)  
+tab
+})
+
+names(PA_by_sleep_regularity) <- gsub("scale_", "", names(PA_by_sleep_regularity)) |> 
+  gsub("\\sby.*", "", x = _ ) |> 
+  gsub("_", " ", x = _ ) |> 
+  fix_model_names()
+
+  papaja::apa_table(PA_by_sleep_regularity,
+                    caption = "Physical activity by sleep regularity controlling for SES, gender and BMI",
+                    note = note,
+                    escape = FALSE)
+```
+
+```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
+knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag.jpg"), error = FALSE)
+```

### 2023-03-14 doc/manuscript.tex
Add all tables and figures.

--- 2023-03-14 doc/manuscript.tex
@@
 \ \ \ (Intercept) & -0.37 [-0.94, 0.20] & 0.29 & -1.28 & .291\\
-\ \ \ Scale  pa  volume & 0.03 [0.00, 0.07] & 0.02 & 1.96 & .050\\
+\ \ \ Scale PA volume & 0.03 [0.00, 0.07] & 0.02 & 1.96 & .050\\
 \ \ \ Age & 0.00 [-0.01, 0.00] & 0.00 & -0.29 & .797\\
-\ \ \ Scale  pa  volume$^2$ & 0.00 [-0.01, 0.01] & 0.00 & 0.11 & .912\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.92 & .359\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.94 & .349\\
+\ \ \ Scale PA volume$^2$ & 0.00 [-0.01, 0.01] & 0.00 & 0.11 & .912\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.92 & .359\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.94 & .349\\
 Sleep efficiency &  &  &  & \\
 \ \ \ (Intercept) & -0.90 [-1.29, -0.50] & 0.20 & -4.46 & .001\\
-\ \ \ Scale  pa  volume & 0.23 [0.20, 0.27] & 0.02 & 12.97 & < .001\\
+\ \ \ Scale PA volume & 0.23 [0.20, 0.27] & 0.02 & 12.97 & < .001\\
 \ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 9.99 & .002\\
-\ \ \ Scale  pa  volume$^2$ & -0.02 [-0.03, -0.01] & 0.00 & -4.77 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -5.16 & < .001\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.50 & .617\\
+\ \ \ Scale PA volume$^2$ & -0.02 [-0.03, -0.01] & 0.00 & -4.77 & < .001\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & -5.16 & < .001\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.50 & .617\\
 Sleep onset &  &  &  & \\
 \ \ \ (Intercept) & -0.98 [-1.50, -0.47] & 0.26 & -3.77 & .060\\
-\ \ \ Scale  pa  volume & 0.11 [0.09, 0.14] & 0.01 & 8.32 & < .001\\
+\ \ \ Scale PA volume & 0.11 [0.09, 0.14] & 0.01 & 8.32 & < .001\\
 \ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.81 & .007\\
-\ \ \ Scale  pa  volume$^2$ & -0.01 [-0.02, -0.01] & 0.00 & -4.73 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -8.70 & < .001\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.34 & .034\\
+\ \ \ Scale PA volume$^2$ & -0.01 [-0.02, -0.01] & 0.00 & -4.73 & < .001\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & -8.70 & < .001\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.34 & .034\\
 Sleep regularity &  &  &  & \\
 \ \ \ (Intercept) & -0.13 [-0.39, 0.13] & 0.13 & -0.96 & .415\\
-\ \ \ Scale  pa  volume & 0.33 [0.29, 0.36] & 0.02 & 19.10 & < .001\\
+\ \ \ Scale PA volume & 0.33 [0.29, 0.36] & 0.02 & 19.10 & < .001\\
 \ \ \ Age & 0.01 [0.00, 0.01] & 0.00 & 5.07 & .019\\
-\ \ \ Scale  pa  volume$^2$ & -0.03 [-0.03, -0.02] & 0.00 & -5.74 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.64 & .540\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -3.33 & .006\\
+\ \ \ Scale PA volume$^2$ & -0.03 [-0.03, -0.02] & 0.00 & -5.74 & < .001\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.64 & .540\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -3.33 & .006\\
 \bottomrule
@@
 
+\hypertarget{the-effects-of-physical-activty-intensity-on-sleep}{%
+\subsection{The effects of physical activty intensity on sleep}\label{the-effects-of-physical-activty-intensity-on-sleep}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sleep-by-intensity}Sleep on physical activity intensity controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+Sleep duration &  &  &  & \\
+\ \ \ (Intercept) & -0.41 [-0.97, 0.15] & 0.28 & -1.44 & .243\\
+\ \ \ Scale PA intensity & 0.09 [0.04, 0.13] & 0.02 & 3.60 & .001\\
+\ \ \ Age & 0.00 [0.00, 0.00] & 0.00 & 0.14 & .900\\
+\ \ \ Scale PA intensity$^2$ & -0.01 [-0.03, 0.02] & 0.01 & -0.61 & .542\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.43 & .165\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.52 & .604\\
+Sleep efficiency &  &  &  & \\
+\ \ \ (Intercept) & -1.00 [-1.41, -0.60] & 0.21 & -4.87 & < .001\\
+\ \ \ Scale PA intensity & 0.13 [0.04, 0.22] & 0.05 & 2.75 & .062\\
+\ \ \ Age & 0.01 [0.01, 0.02] & 0.00 & 10.22 & .002\\
+\ \ \ Scale PA intensity$^2$ & 0.01 [-0.02, 0.04] & 0.01 & 0.78 & .436\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.95 & .113\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.71 & .088\\
+Sleep onset &  &  &  & \\
+\ \ \ (Intercept) & -0.96 [-1.49, -0.44] & 0.27 & -3.60 & .065\\
+\ \ \ Scale PA intensity & -0.04 [-0.07, -0.01] & 0.02 & -2.46 & .015\\
+\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.64 & .007\\
+\ \ \ Scale PA intensity$^2$ & 0.00 [-0.02, 0.02] & 0.01 & 0.38 & .703\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -0.37 & .714\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 1.51 & .143\\
+Sleep regularity &  &  &  & \\
+\ \ \ (Intercept) & -0.24 [-0.47, -0.02] & 0.11 & -2.09 & .123\\
+\ \ \ Scale PA intensity & 0.30 [0.25, 0.34] & 0.02 & 13.30 & < .001\\
+\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 6.88 & .004\\
+\ \ \ Scale PA intensity$^2$ & -0.05 [-0.07, -0.02] & 0.01 & -3.48 & .001\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -6.20 & < .001\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.33 & .743\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-duration-on-physical-activity}{%
+\subsection{The effects of sleep duration on physical activity}\label{the-effects-of-sleep-duration-on-physical-activity}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-duration}Physical activity  by sleep duration controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.37 [0.18, 0.57] & 0.10 & 3.77 & .022\\
+\ \ \ Scale sleep duration lag & 0.00 [-0.03, 0.04] & 0.02 & 0.23 & .825\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -8.82 & < .001\\
+\ \ \ Scale sleep duration lag$^2$ & -0.01 [-0.02, 0.00] & 0.01 & -1.87 & .061\\
+\ \ \ Scale sleep duration lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.54 & .605\\
+\ \ \ Age:scale sleep duration lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.35 & .739\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.90 [0.70, 1.10] & 0.10 & 8.76 & .005\\
+\ \ \ Scale sleep duration lag & 0.01 [-0.02, 0.04] & 0.02 & 0.66 & .544\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -28.60 & < .001\\
+\ \ \ Scale sleep duration lag$^2$ & 0.00 [-0.03, 0.03] & 0.01 & 0.00 & .998\\
+\ \ \ Scale sleep duration lag:age & 0.00 [0.00, 0.00] & 0.00 & 0.38 & .711\\
+\ \ \ Age:scale sleep duration lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.82 & .482\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_duration_lag} \caption{Physical activty by sleep duration}\label{fig:PA-by-sleep-duration-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-efficiency-on-physical-activity}{%
+\subsection{The effects of sleep efficiency on physical activity}\label{the-effects-of-sleep-efficiency-on-physical-activity}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-efficiency}Physical activity by sleep efficiency controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.36 [0.18, 0.55] & 0.09 & 3.82 & .019\\
+\ \ \ Scale sleep efficiency lag & 0.06 [0.00, 0.12] & 0.03 & 2.11 & .114\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -8.37 & .001\\
+\ \ \ Scale sleep efficiency lag$^2$ & 0.01 [0.00, 0.02] & 0.01 & 1.28 & .270\\
+\ \ \ Scale sleep efficiency lag:age & 0.00 [0.00, 0.00] & 0.00 & -1.15 & .293\\
+\ \ \ Age:scale sleep efficiency lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.39 & .720\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.90 [0.73, 1.07] & 0.09 & 10.11 & .003\\
+\ \ \ Scale sleep efficiency lag & 0.05 [0.01, 0.09] & 0.02 & 2.28 & .060\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -22.87 & < .001\\
+\ \ \ Scale sleep efficiency lag$^2$ & 0.01 [0.00, 0.01] & 0.00 & 1.78 & .076\\
+\ \ \ Scale sleep efficiency lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.78 & .451\\
+\ \ \ Age:scale sleep efficiency lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.39 & .712\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_efficiency_lag} \caption{Physical activty by sleep efficiency}\label{fig:PA-by-sleep-efficiency-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-onset-on-physical-activity}{%
+\subsection{The effects of sleep onset on physical activity}\label{the-effects-of-sleep-onset-on-physical-activity}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-onset}Physical activity by sleep onset controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.40 [0.18, 0.61] & 0.11 & 3.64 & .031\\
+\ \ \ Scale sleep onset lag & 0.03 [0.01, 0.06] & 0.01 & 2.39 & .017\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -11.12 & < .001\\
+\ \ \ Scale sleep onset lag$^2$ & -0.03 [-0.06, 0.01] & 0.02 & -1.59 & .218\\
+\ \ \ Scale sleep onset lag:age & 0.00 [0.00, 0.00] & 0.00 & -2.17 & .032\\
+\ \ \ Age:scale sleep onset lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.74 & .508\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.92 [0.74, 1.11] & 0.10 & 9.70 & .003\\
+\ \ \ Scale sleep onset lag & 0.01 [-0.05, 0.08] & 0.03 & 0.44 & .692\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -34.44 & < .001\\
+\ \ \ Scale sleep onset lag$^2$ & -0.01 [-0.02, 0.00] & 0.01 & -1.66 & .098\\
+\ \ \ Scale sleep onset lag:age & 0.00 [0.00, 0.00] & 0.00 & 0.04 & .972\\
+\ \ \ Age:scale sleep onset lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.27 & .791\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_onset_lag} \caption{Physical activty by sleep onset}\label{fig:PA-by-sleep-onset-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-regularity-on-physical-activity}{%
+\subsection{The effects of sleep regularity on physical activity}\label{the-effects-of-sleep-regularity-on-physical-activity}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-regularity}Physical activity by sleep regularity controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.33 [0.13, 0.53] & 0.10 & 3.23 & .041\\
+\ \ \ Scale sleep regularity lag & 0.21 [0.18, 0.23] & 0.01 & 16.87 & < .001\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -10.74 & < .001\\
+\ \ \ Scale sleep regularity lag$^2$ & 0.02 [0.01, 0.04] & 0.01 & 3.02 & .012\\
+\ \ \ Scale sleep regularity lag:age & 0.00 [0.00, 0.00] & 0.00 & -6.68 & < .001\\
+\ \ \ Age:scale sleep regularity lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.62 & .557\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.89 [0.72, 1.07] & 0.09 & 10.05 & .003\\
+\ \ \ Scale sleep regularity lag & 0.11 [0.08, 0.14] & 0.02 & 6.84 & .002\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -30.01 & < .001\\
+\ \ \ Scale sleep regularity lag$^2$ & 0.00 [-0.01, 0.02] & 0.01 & 0.40 & .696\\
+\ \ \ Scale sleep regularity lag:age & 0.00 [0.00, 0.00] & 0.00 & -2.65 & .029\\
+\ \ \ Age:scale sleep regularity lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.03 & .973\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_regularity_lag} \caption{Physical activty by sleep regularity}\label{fig:PA-by-sleep-regularity-fig}
+\end{figure}
+
 \end{document}

### 2023-03-14 doc/manuscript.Rmd
Add placeholder for demo table.
Complete draft results for R1 and R2

@@
 floatsintext      : no
-linenumbers       : yes
+linenumbers       : no
 draft             : no
@@
 The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
-Table \@ref(demo) shows demographic information.
+Table \@ref(demo) [Mike's table to be inserted] shows demographic information.
 A table of study characteristics can be found in supplementary materials.
@@
 
-We explored the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-by-volume) and Figure \@ref(fig:sleep-by-volume-fig).
@@
 
-## The effects of physical activty intensity on sleep
+## The effects of physical activity intensity on sleep
+
+We estimated how physical activity intensity affects sleep across different age groups.
+We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-by-intensity) and Figure \@ref(fig:sleep-by-intensity-fig).
+We found that higher physical activity intensity is directly proportional to longer sleep duration and better sleep efficiency.
+In the case of older participants, physical activity intensity had a U-shaped relationship with sleep onset, meaning that individuals with very low or very high physical activity intensity had longer sleep onset.
+We also found a strong link between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
 
@@
 ## The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-duration) and Figure \@ref(fig:PA-by-sleep-duration-fig).
+As age increases, both physical activity volume and intensity decrease.
+We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.
 
@@
 
+We estimated the effect of sleep efficiency on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-efficiency) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
+We did not find a relationship between physical activity volume and sleep efficiency.
+A subtle U-shaped relationship emerged, indicating that individuals with above-average sleep efficiency engaged in more intense physical activity.
+
 ```{r PA-by-sleep-efficiency}
@@
 ## The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-onset) and Figure \@ref(fig:PA-by-sleep-onset-fig).
+There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
+The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.
 
@@
 
+We estimated the effect of sleep regularity on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-regularity) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
+There was a U-shaped relationship between sleep regularity and physical activity volume.
+Participants with below-average sleep regularity tended to have average physical activity volume.
+Increases in regularity above the average were linked to greater physical activity volume.
+There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
+Greater sleep regularity was associated with greater physical activity the following day.
+
 ```{r PA-by-sleep-regularity}

### 2023-03-14 doc/manuscript.tex
Add placeholder for demo table.
Complete draft results for R1 and R2

--- 2023-03-14 doc/manuscript.tex
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 
-The aggregated data-set describes 316,835 observations of daily physical activity and sleep from 24,935 unique participants.
-Table \ref{demo} shows demographic information.
+The aggregated data-set describes 314,925 observations of daily physical activity and sleep from 24,935 unique participants.
+Table \ref{demo} {[}Mike's table to be inserted{]} shows demographic information.
 A table of study characteristics can be found in supplementary materials.
@@
 
-We explored the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \ref{tab:sleep-by-volume} and Figure \ref{fig:sleep-by-volume-fig}.
@@
 Sleep duration &  &  &  & \\
-\ \ \ (Intercept) & -0.37 [-0.94, 0.20] & 0.29 & -1.28 & .291\\
-\ \ \ Scale  pa  volume & 0.03 [0.00, 0.07] & 0.02 & 1.96 & .050\\
-\ \ \ Age & 0.00 [-0.01, 0.00] & 0.00 & -0.29 & .797\\
-\ \ \ Scale  pa  volume$^2$ & 0.00 [-0.01, 0.01] & 0.00 & 0.11 & .912\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.92 & .359\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.94 & .349\\
+\ \ \ (Intercept) & -0.23 [-0.55, 0.10] & 0.17 & -1.37 & .189\\
+\ \ \ Scale PA volume & 0.02 [-0.04, 0.08] & 0.03 & 0.68 & .528\\
+\ \ \ Age & 0.00 [0.00, 0.00] & 0.00 & -1.20 & .231\\
+\ \ \ Scale PA volume$^2$ & 0.00 [-0.01, 0.02] & 0.01 & 0.55 & .593\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & 1.20 & .249\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.89 & .399\\
 Sleep efficiency &  &  &  & \\
-\ \ \ (Intercept) & -0.90 [-1.29, -0.50] & 0.20 & -4.46 & .001\\
-\ \ \ Scale  pa  volume & 0.23 [0.20, 0.27] & 0.02 & 12.97 & < .001\\
-\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 9.99 & .002\\
-\ \ \ Scale  pa  volume$^2$ & -0.02 [-0.03, -0.01] & 0.00 & -4.77 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -5.16 & < .001\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.50 & .617\\
+\ \ \ (Intercept) & -1.03 [-1.51, -0.54] & 0.25 & -4.15 & .005\\
+\ \ \ Scale PA volume & 0.20 [0.16, 0.24] & 0.02 & 10.34 & < .001\\
+\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 9.72 & .003\\
+\ \ \ Scale PA volume$^2$ & -0.02 [-0.03, -0.01] & 0.01 & -3.04 & .005\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & -3.07 & .005\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.54 & .618\\
 Sleep onset &  &  &  & \\
-\ \ \ (Intercept) & -0.98 [-1.50, -0.47] & 0.26 & -3.77 & .060\\
-\ \ \ Scale  pa  volume & 0.11 [0.09, 0.14] & 0.01 & 8.32 & < .001\\
-\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.81 & .007\\
-\ \ \ Scale  pa  volume$^2$ & -0.01 [-0.02, -0.01] & 0.00 & -4.73 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & -8.70 & < .001\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.34 & .034\\
+\ \ \ (Intercept) & -1.01 [-1.15, -0.87] & 0.07 & -14.16 & < .001\\
+\ \ \ Scale PA volume & 0.13 [0.10, 0.16] & 0.02 & 7.65 & < .001\\
+\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 32.14 & < .001\\
+\ \ \ Scale PA volume$^2$ & -0.02 [-0.03, 0.00] & 0.01 & -2.78 & .048\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & -8.47 & < .001\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & 1.61 & .179\\
 Sleep regularity &  &  &  & \\
-\ \ \ (Intercept) & -0.13 [-0.39, 0.13] & 0.13 & -0.96 & .415\\
-\ \ \ Scale  pa  volume & 0.33 [0.29, 0.36] & 0.02 & 19.10 & < .001\\
-\ \ \ Age & 0.01 [0.00, 0.01] & 0.00 & 5.07 & .019\\
-\ \ \ Scale  pa  volume$^2$ & -0.03 [-0.03, -0.02] & 0.00 & -5.74 & < .001\\
-\ \ \ Scale  pa  volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.64 & .540\\
-\ \ \ Age:scale  pa  volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -3.33 & .006\\
+\ \ \ (Intercept) & -0.05 [-0.29, 0.18] & 0.12 & -0.43 & .697\\
+\ \ \ Scale PA volume & 0.33 [0.29, 0.37] & 0.02 & 17.05 & < .001\\
+\ \ \ Age & 0.01 [0.00, 0.01] & 0.00 & 4.53 & .032\\
+\ \ \ Scale PA volume$^2$ & -0.03 [-0.04, -0.02] & 0.00 & -6.18 & < .001\\
+\ \ \ Scale PA volume:age & 0.00 [0.00, 0.00] & 0.00 & 0.71 & .486\\
+\ \ \ Age:scale PA volume$^2$ & 0.00 [0.00, 0.00] & 0.00 & -3.87 & < .001\\
 \bottomrule
@@
 
+\hypertarget{the-effects-of-physical-activity-intensity-on-sleep}{%
+\subsection{The effects of physical activity intensity on sleep}\label{the-effects-of-physical-activity-intensity-on-sleep}}
+
+We estimated how physical activity intensity affects sleep across different age groups.
+We present the results controlling for sex, SES, and BMI, in Table \ref{tab:sleep-by-intensity} and Figure \ref{fig:sleep-by-intensity-fig}.
+We found that higher physical activity intensity is directly proportional to longer sleep duration and better sleep efficiency.
+In the case of older participants, physical activity intensity had a U-shaped relationship with sleep onset, meaning that individuals with very low or very high physical activity intensity had longer sleep onset.
+We also found a strong link between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sleep-by-intensity}Sleep on physical activity intensity controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+Sleep duration &  &  &  & \\
+\ \ \ (Intercept) & -0.26 [-0.60, 0.09] & 0.18 & -1.46 & .171\\
+\ \ \ Scale PA intensity & 0.07 [0.03, 0.12] & 0.02 & 3.23 & .001\\
+\ \ \ Age & 0.00 [0.00, 0.00] & 0.00 & 0.03 & .978\\
+\ \ \ Scale PA intensity$^2$ & -0.01 [-0.04, 0.02] & 0.02 & -0.53 & .596\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.51 & .130\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.58 & .565\\
+Sleep efficiency &  &  &  & \\
+\ \ \ (Intercept) & -1.09 [-1.61, -0.57] & 0.27 & -4.11 & .007\\
+\ \ \ Scale PA intensity & 0.08 [0.02, 0.14] & 0.03 & 2.55 & .030\\
+\ \ \ Age & 0.01 [0.01, 0.02] & 0.00 & 8.36 & .006\\
+\ \ \ Scale PA intensity$^2$ & 0.00 [-0.03, 0.04] & 0.02 & 0.17 & .863\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.32 & .220\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.00 & .325\\
+Sleep onset &  &  &  & \\
+\ \ \ (Intercept) & -0.98 [-1.15, -0.81] & 0.09 & -11.35 & .001\\
+\ \ \ Scale PA intensity & -0.03 [-0.07, 0.01] & 0.02 & -1.33 & .213\\
+\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 28.96 & < .001\\
+\ \ \ Scale PA intensity$^2$ & -0.01 [-0.04, 0.01] & 0.01 & -1.09 & .293\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -0.49 & .627\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.45 & .032\\
+Sleep regularity &  &  &  & \\
+\ \ \ (Intercept) & -0.15 [-0.31, 0.02] & 0.08 & -1.75 & .126\\
+\ \ \ Scale PA intensity & 0.28 [0.22, 0.34] & 0.03 & 9.38 & < .001\\
+\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 5.33 & .019\\
+\ \ \ Scale PA intensity$^2$ & -0.04 [-0.07, -0.01] & 0.01 & -2.73 & .010\\
+\ \ \ Scale PA intensity:age & 0.00 [0.00, 0.00] & 0.00 & -4.61 & .001\\
+\ \ \ Age:scale PA intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.24 & .810\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-duration-on-physical-activity}{%
+\subsection{The effects of sleep duration on physical activity}\label{the-effects-of-sleep-duration-on-physical-activity}}
+
+We estimated the effect of sleep duration on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \ref{tab:PA-by-sleep-duration} and Figure \ref{fig:PA-by-sleep-duration-fig}.
+As age increases, both physical activity volume and intensity decrease.
+We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-duration}Physical activity  by sleep duration controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.44 [0.06, 0.82] & 0.20 & 2.25 & .133\\
+\ \ \ Scale sleep duration lag & 0.00 [-0.03, 0.03] & 0.01 & 0.00 & .997\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -6.56 & .004\\
+\ \ \ Scale sleep duration lag$^2$ & -0.02 [-0.03, 0.00] & 0.01 & -2.58 & .024\\
+\ \ \ Scale sleep duration lag:age & 0.00 [0.00, 0.00] & 0.00 & -1.21 & .251\\
+\ \ \ Age:scale sleep duration lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.53 & .596\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.99 [0.60, 1.37] & 0.20 & 5.01 & .032\\
+\ \ \ Scale sleep duration lag & 0.02 [-0.01, 0.05] & 0.02 & 1.18 & .292\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -20.12 & .001\\
+\ \ \ Scale sleep duration lag$^2$ & 0.00 [-0.01, 0.01] & 0.01 & -0.64 & .526\\
+\ \ \ Scale sleep duration lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.02 & .987\\
+\ \ \ Age:scale sleep duration lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.13 & .259\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_duration_lag} \caption{Physical activty by sleep duration}\label{fig:PA-by-sleep-duration-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-efficiency-on-physical-activity}{%
+\subsection{The effects of sleep efficiency on physical activity}\label{the-effects-of-sleep-efficiency-on-physical-activity}}
+
+We estimated the effect of sleep efficiency on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \ref{tab:PA-by-sleep-efficiency} and Figure \ref{fig:PA-by-sleep-efficiency-fig}.
+We did not find a relationship between physical activity volume and sleep efficiency.
+A subtle U-shaped relationship emerged, indicating that individuals with above-average sleep efficiency engaged in more intense physical activity.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-efficiency}Physical activity by sleep efficiency controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.42 [0.03, 0.81] & 0.20 & 2.11 & .151\\
+\ \ \ Scale sleep efficiency lag & 0.04 [-0.02, 0.10] & 0.03 & 1.44 & .238\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -6.63 & .004\\
+\ \ \ Scale sleep efficiency lag$^2$ & 0.01 [0.00, 0.02] & 0.01 & 1.23 & .270\\
+\ \ \ Scale sleep efficiency lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.77 & .467\\
+\ \ \ Age:scale sleep efficiency lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.23 & .815\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.99 [0.60, 1.37] & 0.20 & 5.03 & .032\\
+\ \ \ Scale sleep efficiency lag & 0.03 [0.00, 0.07] & 0.02 & 2.05 & .058\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -19.00 & .001\\
+\ \ \ Scale sleep efficiency lag$^2$ & 0.01 [0.00, 0.02] & 0.00 & 2.39 & .019\\
+\ \ \ Scale sleep efficiency lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.62 & .544\\
+\ \ \ Age:scale sleep efficiency lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.87 & .393\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_efficiency_lag} \caption{Physical activty by sleep efficiency}\label{fig:PA-by-sleep-efficiency-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-onset-on-physical-activity}{%
+\subsection{The effects of sleep onset on physical activity}\label{the-effects-of-sleep-onset-on-physical-activity}}
+
+We estimated the effect of sleep onset on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \ref{tab:PA-by-sleep-onset} and Figure \ref{fig:PA-by-sleep-onset-fig}.
+There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
+The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-onset}Physical activity by sleep onset controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.47 [0.08, 0.87] & 0.20 & 2.36 & .124\\
+\ \ \ Scale sleep onset lag & 0.03 [-0.01, 0.06] & 0.02 & 1.63 & .130\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -7.41 & .002\\
+\ \ \ Scale sleep onset lag$^2$ & -0.05 [-0.07, -0.03] & 0.01 & -4.52 & .001\\
+\ \ \ Scale sleep onset lag:age & 0.00 [0.00, 0.00] & 0.00 & -1.62 & .112\\
+\ \ \ Age:scale sleep onset lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & 2.64 & .017\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 1.04 [0.65, 1.43] & 0.20 & 5.20 & .030\\
+\ \ \ Scale sleep onset lag & 0.03 [0.00, 0.06] & 0.01 & 2.10 & .040\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -21.47 & < .001\\
+\ \ \ Scale sleep onset lag$^2$ & -0.02 [-0.04, -0.01] & 0.01 & -2.77 & .010\\
+\ \ \ Scale sleep onset lag:age & 0.00 [0.00, 0.00] & 0.00 & -0.29 & .782\\
+\ \ \ Age:scale sleep onset lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.89 & .396\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_onset_lag} \caption{Physical activty by sleep onset}\label{fig:PA-by-sleep-onset-fig}
+\end{figure}
+
+\hypertarget{the-effects-of-sleep-regularity-on-physical-activity}{%
+\subsection{The effects of sleep regularity on physical activity}\label{the-effects-of-sleep-regularity-on-physical-activity}}
+
+We estimated the effect of sleep regularity on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \ref{tab:PA-by-sleep-regularity} and Figure \ref{fig:PA-by-sleep-regularity-fig}.
+There was a U-shaped relationship between sleep regularity and physical activity volume.
+Participants with below-average sleep regularity tended to have average physical activity volume.
+Increases in regularity above the average were linked to greater physical activity volume.
+There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
+Greater sleep regularity was associated with greater physical activity the following day.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:PA-by-sleep-regularity}Physical activity by sleep regularity controlling for SES, gender and BMI}
+
+\begin{tabular}{lllll}
+\toprule
+Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+PA volume &  &  &  & \\
+\ \ \ (Intercept) & 0.38 [-0.02, 0.79] & 0.21 & 1.84 & .191\\
+\ \ \ Scale sleep regularity lag & 0.20 [0.17, 0.23] & 0.02 & 12.05 & < .001\\
+\ \ \ Age & -0.01 [-0.01, -0.01] & 0.00 & -6.06 & .008\\
+\ \ \ Scale sleep regularity lag$^2$ & 0.03 [0.02, 0.04] & 0.01 & 4.32 & < .001\\
+\ \ \ Scale sleep regularity lag:age & 0.00 [0.00, 0.00] & 0.00 & -5.07 & .001\\
+\ \ \ Age:scale sleep regularity lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.31 & .242\\
+PA intensity &  &  &  & \\
+\ \ \ (Intercept) & 0.98 [0.59, 1.38] & 0.20 & 4.87 & .035\\
+\ \ \ Scale sleep regularity lag & 0.11 [0.09, 0.13] & 0.01 & 10.15 & < .001\\
+\ \ \ Age & -0.02 [-0.03, -0.02] & 0.00 & -19.24 & .001\\
+\ \ \ Scale sleep regularity lag$^2$ & 0.01 [-0.01, 0.02] & 0.01 & 0.85 & .421\\
+\ \ \ Scale sleep regularity lag:age & 0.00 [0.00, 0.00] & 0.00 & -4.01 & < .001\\
+\ \ \ Age:scale sleep regularity lag$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.12 & .903\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Adjusted for SES, BMI, and sex. }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=7.08in]{../Figures/Pa on sleep_regularity_lag} \caption{Physical activty by sleep regularity}\label{fig:PA-by-sleep-regularity-fig}
+\end{figure}
+
 \end{document}

### 2023-03-14 doc/manuscript.Rmd
Manuscript updates, and move updated demog table to new target.

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 ---
+
+\renewcommand{\arraystretch}{0.65}
 
@@
 options(warn = -1)
+knitr::opts_chunk$set(out.width = "110%")
 ```
@@
 tar_load(data_clean)
+tar_load(purdy_pictures)
 pretty <- function(x) format(x, big.mark = ",")
@@
 The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
-Table \@ref(demo) [Mike's table to be inserted] shows demographic information.
+Table \@ref(demo-participants) shows demographic information for all participants.
 A table of study characteristics can be found in supplementary materials.
+
+```{r demo-participants}
+tar_load(demog_table)
+tar_load(table_1) # to get participants data
+
+tab <- demog_table |> 
+  dplyr::select(Variable = level, Value = out) |> 
+  split(demog_table$name)
+
+tab <- append(tab["Numeric variables"], tab[!names(tab) %in% "Numeric variables"])
+
+# Reorder socioeconomic status
+tab$`Socioeconomic Status`$Variable <- factor(tab$`Socioeconomic Status`$Variable, levels = c("Low","Medium","High"))
+tab$`Sleep Conditions Reported` <- tab$`Sleep Conditions Reported`[tab$`Sleep Conditions Reported`$Variable == "Yes"]
+tab$`Socioeconomic Status` <- tab$`Socioeconomic Status`[order(tab$`Socioeconomic Status`$Variable),]
+
+papaja::apa_table(tab, caption = "Participant characteristics",
+                  note = glue::glue("For categorical variables the value is the count, and percentage.
+For numeric variables the value is the Mean and SD.
+N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"))
+
+```
 
@@
 There was no meaningful relationship between physical activity volume and sleep duration.
-However, a positive curvilinear relationship was observed between physical activity volume and sleep efficiency, onset, and regularity, which interacted with age.
+However, we observed a curvilinear relationships between physical activity volume and sleep efficiency, onset, and regularity, all of which interacted with age.
 Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
@@
 For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.
-
-\renewcommand{\arraystretch}{0.7}
 
@@
 We did not find a relationship between physical activity volume and sleep efficiency.
-A subtle U-shaped relationship emerged, indicating that individuals with above-average sleep efficiency engaged in more intense physical activity.
+However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.
 

### 2023-03-14 doc/manuscript.tex
Manuscript updates, and move updated demog table to new target.

@@
 
+\renewcommand{\arraystretch}{0.65}
+
 \hypertarget{results}{%
@@
 The aggregated data-set describes 314,925 observations of daily physical activity and sleep from 24,935 unique participants.
-Table \ref{demo} {[}Mike's table to be inserted{]} shows demographic information.
+Table \ref{demo-participants} shows demographic information for all participants.
 A table of study characteristics can be found in supplementary materials.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demo-participants}Participant characteristics}
+
+\begin{tabular}{ll}
+\toprule
+Variable & \multicolumn{1}{c}{Value}\\
+\midrule
+Numeric variables & \\
+\ \ \ Valid weartime hours & 18.01 (5.41)\\
+\ \ \ PA volume & 39.39 (19.84)\\
+\ \ \ PA intensity & -2.34 (0.31)\\
+\ \ \ Sleep duration & 387.49 (110.41)\\
+\ \ \ Sleep efficiency & 0.77 (0.14)\\
+\ \ \ Sleep onset & 22.55 (2.11)\\
+\ \ \ Sleep wakeup & 31.11 (1.46)\\
+\ \ \ Sleep regularity & 55.03 (12.77)\\
+\ \ \ Age & 35.28 (28.33)\\
+\ \ \ BMI & 21.74 (5.92)\\
+Accelerometer Wear Location & \\
+\ \ \ Hip & 8,830 (35.41\%)\\
+\ \ \ Wrist & 16,105 (64.59\%)\\
+Region & \\
+\ \ \ Africa & 1,090 (4.37\%)\\
+\ \ \ Asia & \ \  731 (2.93\%)\\
+\ \ \ Europe & 14,840 (59.51\%)\\
+\ \ \ North america & 1,449 (5.81\%)\\
+\ \ \ Oceania & 3,183 (12.77\%)\\
+\ \ \ South america & 3,642 (14.61\%)\\
+Season & \\
+\ \ \ Autumn & 6,644 (26.65\%)\\
+\ \ \ Spring & 7,874 (31.58\%)\\
+\ \ \ Summer & 4,137 (16.59\%)\\
+\ \ \ Winter & 6,280 (25.19\%)\\
+Sex & \\
+\ \ \ Female & 12,393 (49.70\%)\\
+\ \ \ Male & 12,542 (50.30\%)\\
+Sleep Conditions Reported & \\
+\ \ \ Yes & 1,009 (4.05\%)\\
+Socioeconomic Status & \\
+\ \ \ Low & 8,375 (33.59\%)\\
+\ \ \ Medium & 8,510 (34.13\%)\\
+\ \ \ High & 8,050 (32.28\%)\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = 24,935}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/sleep on pa_volume} \caption{Sleep metrics on Physical activity volume}\label{fig:sleep-by-volume-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/sleep on pa_volume} \caption{Sleep metrics on Physical activity volume}\label{fig:sleep-by-volume-fig}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/Pa on sleep_duration_lag} \caption{Physical activty by sleep duration}\label{fig:PA-by-sleep-duration-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/Pa on sleep_duration_lag} \caption{Physical activty by sleep duration}\label{fig:PA-by-sleep-duration-fig}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/Pa on sleep_efficiency_lag} \caption{Physical activty by sleep efficiency}\label{fig:PA-by-sleep-efficiency-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/Pa on sleep_efficiency_lag} \caption{Physical activty by sleep efficiency}\label{fig:PA-by-sleep-efficiency-fig}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/Pa on sleep_onset_lag} \caption{Physical activty by sleep onset}\label{fig:PA-by-sleep-onset-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/Pa on sleep_onset_lag} \caption{Physical activty by sleep onset}\label{fig:PA-by-sleep-onset-fig}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=7.08in]{../Figures/Pa on sleep_regularity_lag} \caption{Physical activty by sleep regularity}\label{fig:PA-by-sleep-regularity-fig}
+\includegraphics[width=1.1\linewidth]{../Figures/Pa on sleep_regularity_lag} \caption{Physical activty by sleep regularity}\label{fig:PA-by-sleep-regularity-fig}
 \end{figure}

### 2023-03-14 R/make_demog_table.R

@@ -1,0 +1,72 @@
+#' demographic_table
+#'
+#' Create a demographic table based on Mike's data
+#' @description I've added in this next segment in order to have a data.frame version of the participant table
+#' Which we can use with papaja. The gtsummary version does not allow for rowspans and was probably
+#' too long to include in the paper.
+
+make_demog_table <- function(table_1, region_lookup){
+
+participants <- table_1$participants
+# First I select all eligible participants
+participants <- dplyr::filter(participants, elible = TRUE) |>
+  # I simplify country to region
+  dplyr::left_join(region_lookup, by = "country") |>
+  # I remove variables we don't want in the table
+  dplyr::select(
+    -c(waist_circumference, screen_time, daylight_hours, city, studyid, country, eligible, pa_sleep_cat,
+       height, weight))
+
+# I store the variable labels for use in the table and add region
+participant_labels <- var_label(participants)
+participant_labels$region <- "Region"
+
+# I select all character variables and create a long from dataset
+participants_character <- dplyr::select(participants, where(is.character) | where(is.factor)) |>
+  tidyr::pivot_longer(-participant_id) |>
+  data.table()
+# I select all numeric variables and create a long form dataset
+participants_numeric <- dplyr::select(participants, where(is.numeric), participant_id) |>
+  tidyr::pivot_longer(-participant_id) |>
+  data.table()
+
+# For the numeric variables I calculate means and SDs
+participants_numeric <- participants_numeric[, {
+  m = papaja::print_num(mean(value, na.rm = TRUE))
+  sd = papaja::print_num(sd(value, na.rm = TRUE))
+  .(out = glue::glue("{m} ({sd})"), variable = "Numeric variables")}, by = "name"]
+
+# For the character variables I get counts and percents
+participants_character <- participants_character[,
+                                                 {
+                                                   num <- table(value) |>
+                                                     data.frame()
+                                                   percent <- table(value) |>
+                                                     prop.table() |>
+                                                     data.frame()
+
+                                                   list(
+                                                     level = as.character(num$value),
+                                                     out = glue::glue(
+                                                       "{format(num$Freq, big.mark = ',')} ({papaja::print_num(percent$Freq*100)}%)"
+                                                     )
+                                                     , variable = "Categorical variables")
+
+                                                 },
[…]

### 2023-03-15 doc/manuscript.Rmd
Add age categories to demog table

@@
 
-tab <- demog_table |> 
-  dplyr::select(Variable = level, Value = out) |> 
-  split(demog_table$name)
+tar_load(demog_table)
 
-tab <- append(tab["Numeric variables"], tab[!names(tab) %in% "Numeric variables"])
-
-# Reorder socioeconomic status
-tab$`Socioeconomic Status`$Variable <- factor(tab$`Socioeconomic Status`$Variable, levels = c("Low","Medium","High"))
-tab$`Sleep Conditions Reported` <- tab$`Sleep Conditions Reported`[tab$`Sleep Conditions Reported`$Variable == "Yes"]
-tab$`Socioeconomic Status` <- tab$`Socioeconomic Status`[order(tab$`Socioeconomic Status`$Variable),]
-
-papaja::apa_table(tab, caption = "Participant characteristics",
+papaja::apa_table(demog_table, caption = "Participant characteristics",
                   note = glue::glue("For categorical variables the value is the count, and percentage.
 For numeric variables the value is the Mean and SD.
-N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"))
+N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
+                  landscape = TRUE,
+                  col_spanners = list("Age group" = c(2,6)))
 

### 2023-03-15 R/make_demog_table.R

@@ -17,24 +17,47 @@ participants <- dplyr::filter(participants, elible = TRUE) |>
     -c(waist_circumference, screen_time, daylight_hours, city, studyid, country, eligible, pa_sleep_cat,
        height, weight, sleep_wakeup))
 
+# Create age bins with specified age points
+age_breaks <- c(0, 11, 18, 35, 65, Inf)
+age_labels <- c("0-11 years", "12-18 years", "19-35 years", "36-65 years", "66+ years")
+
+# Assign age categories to the 'age_cat' column in the 'participants' data frame
+participants$age_cat <-
+  cut(
+    participants$age,
+    breaks = age_breaks,
+    labels = age_labels,
+    include.lowest = TRUE,
+    right = FALSE
+  )
+
 # I store the variable labels for use in the table and add region
 participant_labels <- var_label(participants)
 participant_labels$region <- "Region"
 
 # I select all character variables and create a long from dataset
 participants_character <- dplyr::select(participants, where(is.character) | where(is.factor)) |>
-  tidyr::pivot_longer(-participant_id) |>
+  tidyr::pivot_longer(-c(participant_id, age_cat)) |>
   data.table()
 # I select all numeric variables and create a long form dataset
-participants_numeric <- dplyr::select(participants, where(is.numeric), participant_id) |>
-  tidyr::pivot_longer(-participant_id) |>
+participants_numeric <- dplyr::select(participants, where(is.numeric), participant_id, age_cat) |>
+  tidyr::pivot_longer(-c(participant_id, age_cat)) |>
   data.table()
 
 # For the numeric variables I calculate means and SDs
 participants_numeric <- participants_numeric[, {
   m = papaja::print_num(mean(value, na.rm = TRUE))
   sd = papaja::print_num(sd(value, na.rm = TRUE))
-  .(out = glue::glue("{m} ({sd})"), variable = "Numeric variables")}, by = "name"]
+  .(out = glue::glue("{m} ({sd})"), variable = "Numeric variables")}, by = c("name", "age_cat")]
+
+
+Ns <-
+  data.table::data.table(participants)[, .(
+    out = glue::as_glue(format(length(unique(participant_id)), big.mark = ",")),
+      level = "N",
+      variable = "Numeric variables"
+    ),
+    by = "age_cat"]
 
 # For the character variables I get counts and percents
 participants_character <- participants_character[,
[…]

### 2023-03-15 doc/manuscript.Rmd
Fix demographic table reference
One sentence per line.
Abstract model_list to include other moderators. Add sex.

@@
 ```{r load-targets, include=FALSE}
-tar_load(model_list)
+tar_load(model_list_by_age)
 tar_load(data_clean)
@@
 The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
-Table \@ref(demo-participants) shows demographic information for all participants.
+Table \@ref(tab:demo-participants) shows demographic information for all participants.
 A table of study characteristics can be found in supplementary materials.
@@
 
-sleep_outcomes_by_PA_volume <- lapply(model_list[sleep_names], function(x){
+sleep_outcomes_by_PA_volume <- lapply(model_list_by_age[sleep_names], function(x){
 tab <- format_table(x$table)  
@@
 
-sleep_outcomes_by_PA_intens <- lapply(model_list[sleep_names], function(x){
+sleep_outcomes_by_PA_intens <- lapply(model_list_by_age[sleep_names], function(x){
 tab <- format_table(x$table)  
@@
 
-PA_by_sleep_duration <- lapply(model_list[var_names], function(x){
+PA_by_sleep_duration <- lapply(model_list_by_age[var_names], function(x){
 tab <- format_table(x$table)  
@@
 
-PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x){
+PA_by_sleep_efficiency <- lapply(model_list_by_age[var_names], function(x){
 tab <- format_table(x$table)  
@@
 
-PA_by_sleep_onset <- lapply(model_list[var_names], function(x){
+PA_by_sleep_onset <- lapply(model_list_by_age[var_names], function(x){
 tab <- format_table(x$table)  
@@
 
-PA_by_sleep_regularity <- lapply(model_list[var_names], function(x){
+PA_by_sleep_regularity <- lapply(model_list_by_age[var_names], function(x){
 tab <- format_table(x$table)  

### 2023-03-15 _targets.R

@@ -29,12 +29,35 @@ list(
 
   # Modelling targets
 
-  tar_target(model_list, make_model_list(data_imp)),
-  tar_target(model_diagnostics, make_model_diagnostics(model_list)),
+  # Moderated by age
+  tar_target(
+    model_list_by_age,
+    make_model_list(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65")
+  ),
+  tar_target(
+    model_list_by_sex,
+    make_model_list(
+      data_imp,
+      moderator = "sex",
+      moderator_term = "all",
+      control_vars = c("ses", "age", "bmi"))
+    ),
+
+
+  tar_target(model_diagnostics, make_model_diagnostics(model_list_by_age)),
 
   # Figures
   tar_target(explore_img, make_explore_img_list(data_holdout)),
-  tar_target(purdy_pictures, produce_purdy_pictures(model_list)),
+  tar_target(
+    purdy_pictures_by_age,
+    produce_purdy_pictures(model_list_by_age,
+                           paste_facet_labels = " years")
+  ),
+  tar_target(
+    purdy_pictures_by_sex,
+    produce_purdy_pictures(model_list_by_sex)
+  ),
+
 
   # Output manuscript
   tar_render(manuscript, "doc/manuscript.Rmd", output_format = c("papaja::apa6_docx",

### 2023-03-15 doc/manuscript.Rmd
Abstract model_list to include other moderators. Add sex.

@@
 ```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
 ```
@@
 ```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
 ```

### 2023-03-15 R/clean_data.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author
 #' @export
-clean_data <- function(data_joined) {
+clean_data <- function(data_joined, region_lookup) {
   data_gsheet <- "https://docs.google.com/spreadsheets/d/1A75Qk8mNXygxcsCxLQ4maspZsQxZXJ5K-12X338CQ2s/edit#gid=1960479274" # nolint
   d <- data_joined %>%
     clean_names() %>%
@@ -220,11 +220,14 @@ clean_data <- function(data_joined) {
     location = paste(city, country, sep = ", ")
   )
 
+  d <- dplyr::left_join(d, region_lookup, by = "country")
+
   locations <- unique(d$location)
   locations <- locations[!is.na(locations)]
   update_latlong(locations)
   latlong <- read.csv("latlong.csv") %>% select(-X)
   d <- d %>% left_join(latlong, by = "location")
+
 
   # use suncalc to find sunrise and sunset times
   sunlight <- d %>%

### 2023-03-15 R/make_data_imp.R

@@ -17,7 +17,7 @@ make_data_imp <- function(data, n_imps = 3) {
   m0 <- mice(data, maxit = 0)
 
   # Don't do imputation based on these vars:
-  dont_imp <- c("age_cat", "filename", "calendar_date")
+  dont_imp <- c("age_cat", "filename", "calendar_date", "region")
   meth <- m0$method
   pred <- m0$predictorMatrix
   meth[names(meth) %in% dont_imp] <- ""

### 2023-03-15 R/make_demog_table.R

@@ -5,16 +5,14 @@
 #' Which we can use with papaja. The gtsummary version does not allow for rowspans and was probably
 #' too long to include in the paper.
 
-make_demog_table <- function(table_1, region_lookup){
+make_demog_table <- function(participant_summary){
 
-participants <- table_1$participants
+participants <- participant_summary
 # First I select all eligible participants
 participants <- dplyr::filter(participants, elible = TRUE) |>
-  # I simplify country to region
-  dplyr::left_join(region_lookup, by = "country") |>
   # I remove variables we don't want in the table
   dplyr::select(
-    -c(waist_circumference, screen_time, daylight_hours, city, studyid, country, eligible, pa_sleep_cat,
+    -c(waist_circumference, screen_time, daylight_hours, city, studyid, eligible,
        height, weight, sleep_wakeup))
 
 # Create age bins with specified age points
@@ -34,7 +32,6 @@ participants$age_cat <-
 
 # I store the variable labels for use in the table and add region
 participant_labels <- var_label(participants)
-participant_labels$region <- "Region"
 
 # I select all character variables and create a long from dataset
 participants_character <- dplyr::select(participants, where(is.character) | where(is.factor)) |>

### 2023-03-15 R/make_model_list.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author conig
 #' @export
-make_model_list <- function(data_imp) {
+make_model_list <- function(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65", control_vars = c("ses", "sex", "bmi")) {
 
   sleep_vars <- c("scale_sleep_duration",
                     "scale_sleep_efficiency",
@@ -18,9 +18,7 @@ make_model_list <- function(data_imp) {
 
   PA_vars <- c("scale_pa_volume", "scale_pa_intensity")
 
-  control_vars <- c("ses", "sex", "bmi")
-
-  make_quadratic <- function(x) glue::glue("{x} * age + I({x}^2) * age")
+  make_quadratic <- function(x) glue::glue("{x} * {moderator} + I({x}^2) * {moderator}")
 
   instructions.rq1 <-
     expand.grid(
@@ -53,8 +51,9 @@ make_model_list <- function(data_imp) {
         table_only = FALSE
       )
 
-    attr(model, "terms") <- c(paste0(gsub(" .*", "" ,instructions[i, "predictors"]), "[-4:4 by = 0.1]"), "age [11, 18, 35, 65]")
+    attr(model, "terms") <- c(paste0(gsub(" .*", "" ,instructions[i, "predictors"]), "[-4:4 by = 0.1]"), glue::glue("{moderator} [{moderator_term}]"))
     attr(model, "RQ") <- instructions[i , "RQ"]
+    attr(model, "moderator") <- moderator
     model
 
     }

### 2023-03-15 R/make_table1.R

@@ -5,53 +5,24 @@
 #' @title
 #' @param data_holdout
 #' @return gt object with table1
-#' @author noetel
+#' @author noetel & conigrave
 #' @export
-make_table1 <- function(data_clean) {
+make_participant_summary <- function(data_clean) {
 
-  # targets::tar_make()
-  # targets::tar_load(data_clean)
-  # d <- data_clean
   d <- data_clean %>%
     select(n_valid_hours, accelerometer_wear_location,
     pa_volume, pa_intensity,
     sleep_duration, sleep_efficiency,
     sleep_onset, sleep_wakeup,
-    sleep_regularity,# sleep_onset_time, sleep_wakeup_time,
+    sleep_regularity, # sleep_onset_time, sleep_wakeup_time,
     sleep_duration, sleep_efficiency,
     sex, age, height, weight, bmi, waist_circumference,
     ses, screen_time, daylight_hours, city, eligible,
-    sleep_conditions, country, season, studyid, participant_id) %>%
+    sleep_conditions, country, season, region, studyid, participant_id) %>%
     mutate(studyid = as.factor(studyid),
             city = as.factor(city),
             season = as.factor(season))
-  # Label everything nicely
-  var_label(d) <- c("Valid Weartime Hours",
-    "Accelerometer Wear Location",
-    "PA Volume",
-    "PA Intensity",
-    "Sleep Duration",
-    "Sleep Efficiency",
-    "Sleep Onset",
-    "Sleep Wakeup", "Sleep Regularity",
-    "Sex", "Age", "Height", "Weight", "BMI", "Waist Circumference",
-    "Socioeconomic Status", "Screen Time", "Daylight Hours", "City", "Met Weartime Criteria",
-    "Sleep Conditions Reported", "Country", "Season", "Study ID", "Participant ID")
 
-  # Tabulate the number of observations
-  observations_table1 <- d %>% select(-studyid, -participant_id) %>%
-  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})",
-                                all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    missing = "no")
-    as_gt(observations_table1) %>%
-
-    gtsave("tables/observations_table_one.png")
-
-  # Now across each participant_id, summarise all variables.
-  # For factor variables, pick the most common.
-  # For numeric variables, take the mean.
-  find_max  <- function(x) {names(which.max(table(x)))}
   participants <- d %>%
[…]

### 2023-03-15 R/model_builder.R

@@ -27,9 +27,8 @@ model_builder <-
       )
 
     formula <- gsub("\\+  \\+", "+", formula)
-    # formula <- gsub("\\#.*", "", formula)
 
-    fit_model <- function(..., data){
+    fit_model <- function(..., data, max_iter = 1e6){
       require(optimx)
       require(lme4)
       require(dfoptim)
@@ -38,8 +37,9 @@ model_builder <-
       exhausted <- FALSE
       i <- 1
       meth.tab <- lme4:::meth.tab.0
-      meth.tab[!duplicated(meth.tab[,1]),]
+      meth.tab <- cbind(meth.tab, maxit_name = c("maxfun", "maxfun", "maxit", "maxfeval", "maxit", "maxeval","maxeval"))
       meth.tab <- meth.tab[sample(seq_len(nrow(meth.tab)), nrow(meth.tab), replace = FALSE), ]
+
       while(!conv & i <= nrow(meth.tab)) {
 
         if(meth.tab[i , 2] != ""){
@@ -47,6 +47,8 @@ model_builder <-
         }else{
           optCtrl <- list()
         }
+
+        optCtrl[[meth.tab[i , 3]]] <- max_iter
 
         mod <- lme4::lmer(
           ...,

### 2023-03-15 R/produce_purdy_pictures.R

@@ -1,7 +1,8 @@
 #' produce_purdy_pictures
 #' @param model_list list of RQ1 models
+#' @example  model_list <- model_list_by_age
 
-produce_purdy_pictures <- function(model_list){
+produce_purdy_pictures <- function(model_list, paste_facet_labels = ""){
 
   dat_list <- lapply(seq_len(length(model_list)), function(i){
 
@@ -13,6 +14,7 @@ produce_purdy_pictures <- function(model_list){
     dt$group_name = terms[2]
     dt$outcome = gsub(" .*","",names(model_list)[[i]])
     dt$RQ <- attr(m, "RQ")
+    dt$moderator <- attr(m, "moderator")
     dt
 
   })
@@ -23,7 +25,7 @@ produce_purdy_pictures <- function(model_list){
     gsub("_", " ", x = _) |>
     stringr::str_to_title() |>
     paste("(z)")
-  plot_dat$group <- paste(plot_dat$group, "years")
+  plot_dat$group <- paste0(plot_dat$group, paste_facet_labels)
   plot_dat$x_name <- gsub("\\[.*","", plot_dat$x_name)
 
 
@@ -37,14 +39,14 @@ produce_purdy_pictures <- function(model_list){
     geom_ribbon(alpha = .5) +
     facet_grid(rows = vars(outcome), cols = vars(group)) +
       labs(x = x_lab,
-           fill = "Age") +
+           fill = stringr::str_to_sentence(unique(plot_dat$moderator))) +
       figure_theme() +
     theme(legend.position = "none")
 
     outcome <- unique(gsub(" .*","", pdat$outcome))
     if(length(outcome) > 1) stop("Outcome length is greater than 1")
 
-    filename <- "Figures/{outcome} on {x_var}.jpg" |>
+    filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}.jpg" |>
       glue::glue()
 
     if(outcome == "Sleep"){
@@ -53,7 +55,7 @@ produce_purdy_pictures <- function(model_list){
       height = 9
     }
 
-    ggsave(filename, plot = fig, height = height, width = 18, units = "cm", dpi = 300)
+    ggsave(filename, plot = fig, height = height, width = 3.25 * length(unique(pdat$group)) + 5, units = "cm", dpi = 300)
 
   }
 

### 2023-03-15 R/utils.R

@@ -88,3 +88,4 @@ get_season <- function(date, lat){
   }
 }
 
+find_max  <- function(x) {names(which.max(table(x)))}

### 2023-03-15 _targets.R

@@ -19,22 +19,44 @@ list(
 
   # Data targets
   tar_target(data_joined, bind_rows(data_raw), pattern = map(data_raw)),
-  tar_target(data_clean, clean_data(data_joined)),
+  tar_target(data_clean, clean_data(data_joined, region_lookup)),
   tar_target(data_holdout, make_data_holdout(data_clean)),
 
-  tar_target(table_1, make_table1(data_clean)),
+  tar_target(participant_summary, make_participant_summary(data_clean)),
   tar_target(region_lookup, make_region_lookup()),
-  tar_target(demog_table, make_demog_table(table_1, region_lookup)),
+  tar_target(demog_table, make_demog_table(participant_summary)),
   tar_target(data_imp, make_data_imp(data_holdout, n_imps = 3)),
 
   # Modelling targets
 
-  tar_target(model_list, make_model_list(data_imp)),
-  tar_target(model_diagnostics, make_model_diagnostics(model_list)),
+  # Moderated by age
+  tar_target(
+    model_list_by_age,
+    make_model_list(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65")
+  ),
+  tar_target(
+    model_list_by_sex,
+    make_model_list(
+      data_imp,
+      moderator = "sex",
+      moderator_term = "all",
+      control_vars = c("ses", "age", "bmi"))
+    ),
+
+
+  tar_target(model_diagnostics, make_model_diagnostics(model_list_by_age)),
 
   # Figures
   tar_target(explore_img, make_explore_img_list(data_holdout)),
-  tar_target(purdy_pictures, produce_purdy_pictures(model_list)),
+  tar_target(
+    purdy_pictures_by_age,
+    produce_purdy_pictures(model_list_by_age,
+                           paste_facet_labels = " years")
+  ),
+  tar_target(
+    purdy_pictures_by_sex,
+    produce_purdy_pictures(model_list_by_sex)
+  ),
 
   # Output manuscript
   tar_render(manuscript, "doc/manuscript.Rmd", output_format = c("papaja::apa6_docx",

### 2023-03-15 doc/manuscript.Rmd
WIP: collapse model tables

--- 2023-03-15 doc/manuscript.Rmd
@@
 ```{r load-targets, include=FALSE}
-tar_load(model_list_by_age)
 tar_load(data_clean)
 tar_load(purdy_pictures)
+tar_load(model_tables)
 pretty <- function(x) format(x, big.mark = ",")
@@
 
-papaja::apa_table(demog_table, caption = "Participant characteristics",
+papaja::apa_table(demog_table,
+  caption = "Participant characteristics",
   note = glue::glue("For categorical variables the value is the count, and percentage.
@@
   landscape = TRUE,
-                  col_spanners = list("Age group" = c(2,6)))
-
+  col_spanners = list("Age group" = c(2, 6))
+)
 ```
@@
 We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-by-volume) and Figure \@ref(fig:sleep-by-volume-fig).
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig).
 There was no meaningful relationship between physical activity volume and sleep duration.
@@
 
-```{r sleep-by-volume}
-note <- "Adjusted for SES, BMI, and sex. "
-
-format_table <- function(tab) {
-  tab$term <- gsub("I\\(", "", tab$term) |>
-    gsub("_", " ", x = _) |>
-    gsub("\\^2\\)", "$^2$", x = _ )
-  tab <- tab[!grepl("^ses", tab$term), ]
-  tab <- tab[!grepl("^sex", tab$term), ]
-  tab <- tab[!grepl("^bmi", tab$term), ]
-  tab$term <- stringr::str_to_sentence(tab$term)
-  tab$term <- gsub(" pa ", " PA ", tab$term)
-  names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
-  tab
-}
-
-fix_model_names <- function(x){
-  x <- stringr::str_to_sentence(x)
-  x <- gsub("Pa", "PA", x)
-  x
-}
-
-sleep_names <- c("scale_sleep_duration by scale_pa_volume", "scale_sleep_efficiency by scale_pa_volume", 
-"scale_sleep_onset by scale_pa_volume", "scale_sleep_regularity by scale_pa_volume")
-
-sleep_outcomes_by_PA_volume <- lapply(model_list_by_age[sleep_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
-
-names(sleep_outcomes_by_PA_volume) <- gsub("scale_", "", names(sleep_outcomes_by_PA_volume)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
-
-  papaja::apa_table(sleep_outcomes_by_PA_volume,
-                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
+```{r sleep-outcomes}
+papaja::apa_table(
+  model_tables$sleep$data,
+  caption = model_tables$sleep$caption,
+  note = model_tables$sleep$note,
+  col_spanners = model_tables$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
 ```
@@
 We estimated how physical activity intensity affects sleep across different age groups.
-We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-by-intensity) and Figure \@ref(fig:sleep-by-intensity-fig).
+We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
 We found that higher physical activity intensity is directly proportional to longer sleep duration and better sleep efficiency.
@@
 We also found a strong link between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
-
-```{r sleep-by-intensity}
-sleep_names <- c("scale_sleep_duration by scale_pa_intensity", "scale_sleep_efficiency by scale_pa_intensity", 
-"scale_sleep_onset by scale_pa_intensity", "scale_sleep_regularity by scale_pa_intensity")
-
-sleep_outcomes_by_PA_intens <- lapply(model_list_by_age[sleep_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
-
-names(sleep_outcomes_by_PA_intens) <- gsub("scale_", "", names(sleep_outcomes_by_PA_intens)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
-
-  papaja::apa_table(sleep_outcomes_by_PA_intens,
-                    caption = "Sleep on physical activity intensity controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
-```
 
@@
 ```{r PA-by-sleep-duration}
-var_names <- c(
-  "scale_pa_volume by scale_sleep_duration_lag",
-  "scale_pa_intensity by scale_sleep_duration_lag"
-)
+# var_names <- c(
+#   "scale_pa_volume by scale_sleep_duration_lag",
+#   "scale_pa_intensity by scale_sleep_duration_lag"
+# )
 
-PA_by_sleep_duration <- lapply(model_list_by_age[var_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
+# PA_by_sleep_duration <- lapply(model_list[var_names], function(x) {
+#   tab <- format_table(x$table)
+#   tab
+# })
 
-names(PA_by_sleep_duration) <- gsub("scale_", "", names(PA_by_sleep_duration)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
+# names(PA_by_sleep_duration) <- gsub("scale_", "", names(PA_by_sleep_duration)) |>
+#   gsub("\\sby.*", "", x = _) |>
+#   gsub("_", " ", x = _) |>
+#   fix_model_names()
 
-  papaja::apa_table(PA_by_sleep_duration,
-                    caption = "Physical activity  by sleep duration controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
+# papaja::apa_table(PA_by_sleep_duration,
+#   caption = "Physical activity  by sleep duration controlling for SES, gender and BMI",
+#   note = note,
+#   escape = FALSE
+# )
 ```
@@
 ```{r PA-by-sleep-efficiency}
-var_names <- c(
-  "scale_pa_volume by scale_sleep_efficiency_lag",
-  "scale_pa_intensity by scale_sleep_efficiency_lag"
-)
+# var_names <- c(
+#   "scale_pa_volume by scale_sleep_efficiency_lag",
+#   "scale_pa_intensity by scale_sleep_efficiency_lag"
+# )
 
-PA_by_sleep_efficiency <- lapply(model_list_by_age[var_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
+# PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x) {
+#   tab <- format_table(x$table)
+#   tab
+# })
 
-names(PA_by_sleep_efficiency) <- gsub("scale_", "", names(PA_by_sleep_efficiency)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
+# names(PA_by_sleep_efficiency) <- gsub("scale_", "", names(PA_by_sleep_efficiency)) |>
+#   gsub("\\sby.*", "", x = _) |>
+#   gsub("_", " ", x = _) |>
+#   fix_model_names()
 
-  papaja::apa_table(PA_by_sleep_efficiency,
-                    caption = "Physical activity by sleep efficiency controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
+# papaja::apa_table(PA_by_sleep_efficiency,
+#   caption = "Physical activity by sleep efficiency controlling for SES, gender and BMI",
+#   note = note,
+#   escape = FALSE
+# )
 ```
@@
 ```{r PA-by-sleep-onset}
-var_names <- c(
-  "scale_pa_volume by scale_sleep_onset_lag",
-  "scale_pa_intensity by scale_sleep_onset_lag"
-)
+# var_names <- c(
+#   "scale_pa_volume by scale_sleep_onset_lag",
+#   "scale_pa_intensity by scale_sleep_onset_lag"
+# )
 
-PA_by_sleep_onset <- lapply(model_list_by_age[var_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
+# PA_by_sleep_onset <- lapply(model_list[var_names], function(x) {
+#   tab <- format_table(x$table)
+#   tab
+# })
 
-names(PA_by_sleep_onset) <- gsub("scale_", "", names(PA_by_sleep_onset)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
+# names(PA_by_sleep_onset) <- gsub("scale_", "", names(PA_by_sleep_onset)) |>
+#   gsub("\\sby.*", "", x = _) |>
+#   gsub("_", " ", x = _) |>
+#   fix_model_names()
 
-  papaja::apa_table(PA_by_sleep_onset,
-                    caption = "Physical activity by sleep onset controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
+# papaja::apa_table(PA_by_sleep_onset,
+#   caption = "Physical activity by sleep onset controlling for SES, gender and BMI",
+#   note = note,
+#   escape = FALSE
+# )
 ```
@@
 ```{r PA-by-sleep-regularity}
-var_names <- c(
-  "scale_pa_volume by scale_sleep_regularity_lag",
-  "scale_pa_intensity by scale_sleep_regularity_lag"
-)
+# var_names <- c(
+#   "scale_pa_volume by scale_sleep_regularity_lag",
+#   "scale_pa_intensity by scale_sleep_regularity_lag"
+# )
 
-PA_by_sleep_regularity <- lapply(model_list_by_age[var_names], function(x){
-tab <- format_table(x$table)  
-tab
-})
+# PA_by_sleep_regularity <- lapply(model_list[var_names], function(x) {
+#   tab <- format_table(x$table)
+#   tab
+# })
 
-names(PA_by_sleep_regularity) <- gsub("scale_", "", names(PA_by_sleep_regularity)) |> 
-  gsub("\\sby.*", "", x = _ ) |> 
-  gsub("_", " ", x = _ ) |> 
-  fix_model_names()
+# names(PA_by_sleep_regularity) <- gsub("scale_", "", names(PA_by_sleep_regularity)) |>
+#   gsub("\\sby.*", "", x = _) |>
+#   gsub("_", " ", x = _) |>
+#   fix_model_names()
 
-  papaja::apa_table(PA_by_sleep_regularity,
-                    caption = "Physical activity by sleep regularity controlling for SES, gender and BMI",
-                    note = note,
-                    escape = FALSE)
+# papaja::apa_table(PA_by_sleep_regularity,
+#   caption = "Physical activity by sleep regularity controlling for SES, gender and BMI",
+#   note = note,
+#   escape = FALSE
+# )
 ```

### 2023-03-15 R/make_model_tables.R

@@ -1,0 +1,58 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param model_list
+#' @return list of tables
+#' @author Taren Sanders
+#' @export
+make_model_tables <- function(model_list) {
+  note <- "Adjusted for SES, BMI, and sex."
+
+  sleep_vars <- list(
+    `Sleep duration` = "scale_sleep_duration",
+    `Sleep efficency` = "scale_sleep_efficiency",
+    `Sleep onset` = "scale_sleep_onset",
+    `Sleep regularity` = "scale_sleep_regularity"
+  )
+  pa_vars <- c("scale_pa_volume", "scale_pa_intensity")
+
+  sleep_table <- list()
+
+  sleep_table$data <- lapply(sleep_vars, function(sleep) {
+    model1_name <- paste(sleep, "by", pa_vars[[1]], collapse = " ")
+    model2_name <- paste(sleep, "by", pa_vars[[2]], collapse = " ")
+
+    tab <- cbind(
+      format_table(model_list[[model1_name]]$table),
+      format_table(model_list[[model2_name]]$table)
+    )
+    tab[, c(1:5, 7:10)]
+  })
+
+  sleep_table$caption <-
+    "Sleep on physical activity volume controlling for SES, gender and BMI"
+  sleep_table$note <- note
+  sleep_table$col_spanners <- list(
+    "Physical Activity Volume" = c(2, 5),
+    "Physical Activity Intensity" = c(6, 9)
+  )
+
+  return(list(sleep = sleep_table))
+}
+
+format_table <- function(tab) {
+  tab$term <- gsub("I\\(", "", tab$term) |>
+    gsub("_", " ", x = _) |>
+    gsub("\\^2\\)", "$^2$", x = _)
+  tab <- tab[!grepl("^ses", tab$term), ]
+  tab <- tab[!grepl("^sex", tab$term), ]
+  tab <- tab[!grepl("^bmi", tab$term), ]
+  tab$term <- stringr::str_to_sentence(tab$term)
+  tab$term <- gsub(
+    "(S|s)cale pa (intensity|volume)", "Physical Activity", tab$term
+  )
+  names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
+  tab
+}

### 2023-03-15 _targets.R

@@ -35,6 +35,7 @@ list(
   tar_target(table_1, make_table1(data_clean)),
   tar_target(region_lookup, make_region_lookup()),
   tar_target(demog_table, make_demog_table(table_1, region_lookup)),
+  tar_target(model_tables, make_model_tables(model_list)),
 
   # Output manuscript
   tar_render(manuscript, "doc/manuscript.Rmd", output_format = c(

### 2023-03-15 doc/manuscript.Rmd
Add PA tables and tidy Rmd

@@
 tar_load(model_tables)
+tar_load(demog_table)
+tar_load(table_1)
 pretty <- function(x) format(x, big.mark = ",")
@@
 ```{r demo-participants}
-tar_load(demog_table)
-tar_load(table_1) # to get participants data
-
-tar_load(demog_table)
-
 papaja::apa_table(demog_table,
@@
 We estimated the effect of sleep duration on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-duration) and Figure \@ref(fig:PA-by-sleep-duration-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
 As age increases, both physical activity volume and intensity decrease.
@@
 
-```{r PA-by-sleep-duration}
-# var_names <- c(
-#   "scale_pa_volume by scale_sleep_duration_lag",
-#   "scale_pa_intensity by scale_sleep_duration_lag"
-# )
-
-# PA_by_sleep_duration <- lapply(model_list[var_names], function(x) {
-#   tab <- format_table(x$table)
-#   tab
-# })
-
-# names(PA_by_sleep_duration) <- gsub("scale_", "", names(PA_by_sleep_duration)) |>
-#   gsub("\\sby.*", "", x = _) |>
-#   gsub("_", " ", x = _) |>
-#   fix_model_names()
-
-# papaja::apa_table(PA_by_sleep_duration,
-#   caption = "Physical activity  by sleep duration controlling for SES, gender and BMI",
-#   note = note,
-#   escape = FALSE
-# )
+```{r pa-outcomes}
+papaja::apa_table(
+  model_tables$physical_activity$data,
+  caption = model_tables$physical_activity$caption,
+  note = model_tables$physical_activity$note,
+  col_spanners = model_tables$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
 ```
@@
 We estimated the effect of sleep efficiency on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-efficiency) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
 We did not find a relationship between physical activity volume and sleep efficiency.
 However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.
-
-```{r PA-by-sleep-efficiency}
-# var_names <- c(
-#   "scale_pa_volume by scale_sleep_efficiency_lag",
-#   "scale_pa_intensity by scale_sleep_efficiency_lag"
-# )
-
-# PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x) {
-#   tab <- format_table(x$table)
-#   tab
-# })
-
-# names(PA_by_sleep_efficiency) <- gsub("scale_", "", names(PA_by_sleep_efficiency)) |>
-#   gsub("\\sby.*", "", x = _) |>
-#   gsub("_", " ", x = _) |>
-#   fix_model_names()
-
-# papaja::apa_table(PA_by_sleep_efficiency,
-#   caption = "Physical activity by sleep efficiency controlling for SES, gender and BMI",
-#   note = note,
-#   escape = FALSE
-# )
-```
 
@@
 We estimated the effect of sleep onset on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-onset) and Figure \@ref(fig:PA-by-sleep-onset-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
 There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
 The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.
-
-```{r PA-by-sleep-onset}
-# var_names <- c(
-#   "scale_pa_volume by scale_sleep_onset_lag",
-#   "scale_pa_intensity by scale_sleep_onset_lag"
-# )
-
-# PA_by_sleep_onset <- lapply(model_list[var_names], function(x) {
-#   tab <- format_table(x$table)
-#   tab
-# })
-
-# names(PA_by_sleep_onset) <- gsub("scale_", "", names(PA_by_sleep_onset)) |>
-#   gsub("\\sby.*", "", x = _) |>
-#   gsub("_", " ", x = _) |>
-#   fix_model_names()
-
-# papaja::apa_table(PA_by_sleep_onset,
-#   caption = "Physical activity by sleep onset controlling for SES, gender and BMI",
-#   note = note,
-#   escape = FALSE
-# )
-```
 
@@
 We estimated the effect of sleep regularity on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-regularity) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
 There was a U-shaped relationship between sleep regularity and physical activity volume.
@@
 
-```{r PA-by-sleep-regularity}
-# var_names <- c(
-#   "scale_pa_volume by scale_sleep_regularity_lag",
-#   "scale_pa_intensity by scale_sleep_regularity_lag"
-# )
-
-# PA_by_sleep_regularity <- lapply(model_list[var_names], function(x) {
-#   tab <- format_table(x$table)
-#   tab
-# })
-
-# names(PA_by_sleep_regularity) <- gsub("scale_", "", names(PA_by_sleep_regularity)) |>
-#   gsub("\\sby.*", "", x = _) |>
-#   gsub("_", " ", x = _) |>
-#   fix_model_names()
-
-# papaja::apa_table(PA_by_sleep_regularity,
-#   caption = "Physical activity by sleep regularity controlling for SES, gender and BMI",
-#   note = note,
-#   escape = FALSE
-# )
-```
-
 ```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}

### 2023-03-15 R/make_model_tables.R

@@ -16,13 +16,23 @@ make_model_tables <- function(model_list) {
     `Sleep onset` = "scale_sleep_onset",
     `Sleep regularity` = "scale_sleep_regularity"
   )
-  pa_vars <- c("scale_pa_volume", "scale_pa_intensity")
+
+  pa_vars <- list(
+    `Physical activity volume` = "scale_pa_volume",
+    `Physical activity intensity` = "scale_pa_intensity"
+  )
 
   sleep_table <- list()
 
   sleep_table$data <- lapply(sleep_vars, function(sleep) {
-    model1_name <- paste(sleep, "by", pa_vars[[1]], collapse = " ")
-    model2_name <- paste(sleep, "by", pa_vars[[2]], collapse = " ")
+    model1_name <- paste(
+      sleep, "by", pa_vars["Physical activity volume"],
+      collapse = " "
+    )
+    model2_name <- paste(
+      sleep, "by", pa_vars[["Physical activity intensity"]],
+      collapse = " "
+    )
 
     tab <- cbind(
       format_table(model_list[[model1_name]]$table),
@@ -32,14 +42,40 @@ make_model_tables <- function(model_list) {
   })
 
   sleep_table$caption <-
-    "Sleep on physical activity volume controlling for SES, gender and BMI"
+    "Physical activity on sleep controlling for SES, gender and BMI"
   sleep_table$note <- note
   sleep_table$col_spanners <- list(
     "Physical Activity Volume" = c(2, 5),
     "Physical Activity Intensity" = c(6, 9)
   )
 
-  return(list(sleep = sleep_table))
+  pa_table <- list()
+  pa_table$data <- lapply(sleep_vars, function(sleep) {
+    model1_name <- paste(
+      pa_vars["Physical activity volume"], "by", paste0(sleep, "_lag"),
+      collapse = " "
+    )
+    model2_name <- paste(
+      pa_vars[["Physical activity intensity"]], "by", paste0(sleep, "_lag"),
+      collapse = " "
+    )
+
+    tab <- cbind(
+      format_table(model_list[[model1_name]]$table),
+      format_table(model_list[[model2_name]]$table)
+    )
+    tab[, c(1:5, 7:10)]
+  })
+
+  pa_table$caption <-
+    "Sleep on physical activity controlling for SES, gender and BMI"
+  pa_table$note <- note
[…]

### 2023-03-15 doc/manuscript.Rmd
Make model tables (#50)
* Restructure _targets file

* WIP: collapse model tables

* Add PA tables and tidy Rmd

* Small tidy of Rmd

@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig).
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
 There was no meaningful relationship between physical activity volume and sleep duration.
@@
 
-We estimated how physical activity intensity affects sleep across different age groups.
+We estimated how physical activity intensity affects sleep across different age groups
 We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
@@
 
-We estimated the effect of sleep duration on physical activity by age.
+We estimated the effect of sleep duration on physical activity by age
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
@@
 
-We estimated the effect of sleep onset on physical activity by age.
+We estimated the effect of sleep onset on physical activity by age
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).

### 2023-03-15 _targets.R

@@ -10,25 +10,20 @@ load_packages()
 list(
   tar_files_input(datasets, list.files("data", full.names = TRUE)),
   tar_target(data_raw,
-             read_csv(datasets,
-                      col_types = list(.default = "c"),
-                      id = "studyid"
-             ),
-             pattern = map(datasets), iteration = "list"
+    read_csv(datasets,
+      col_types = list(.default = "c"),
+      id = "studyid"
+    ),
+    pattern = map(datasets), iteration = "list"
   ),
 
   # Data targets
   tar_target(data_joined, bind_rows(data_raw), pattern = map(data_raw)),
   tar_target(data_clean, clean_data(data_joined)),
   tar_target(data_holdout, make_data_holdout(data_clean)),
-
-  tar_target(table_1, make_table1(data_clean)),
-  tar_target(region_lookup, make_region_lookup()),
-  tar_target(demog_table, make_demog_table(table_1, region_lookup)),
   tar_target(data_imp, make_data_imp(data_holdout, n_imps = 3)),
 
   # Modelling targets
-
   tar_target(model_list, make_model_list(data_imp)),
   tar_target(model_diagnostics, make_model_diagnostics(model_list)),
 
@@ -36,7 +31,15 @@ list(
   tar_target(explore_img, make_explore_img_list(data_holdout)),
   tar_target(purdy_pictures, produce_purdy_pictures(model_list)),
 
+  # Tables
+  tar_target(table_1, make_table1(data_clean)),
+  tar_target(region_lookup, make_region_lookup()),
+  tar_target(demog_table, make_demog_table(table_1, region_lookup)),
+  tar_target(model_tables, make_model_tables(model_list)),
+
   # Output manuscript
-  tar_render(manuscript, "doc/manuscript.Rmd", output_format = c("papaja::apa6_docx",
-                                                                 "papaja::apa6_pdf"))
+  tar_render(manuscript, "doc/manuscript.Rmd", output_format = c(
+    "papaja::apa6_docx",
+    "papaja::apa6_pdf"
+  ))
 )

### 2023-03-15 doc/manuscript.Rmd

@@
 ```{r load-targets, include=FALSE}
+tar_load(model_list_by_age)
 tar_load(data_clean)

### 2023-03-17 doc/multiverse.Rmd
Add analysis where study is a fixed effect instead of a random effect. unnest participants from within measurement days. Nest measurement days within studies by use of concatenate. Create rmd for multiverse.

--- 2023-03-15 doc/manuscript.Rmd
@@
 ---
-title             : "The title"
+title             : "Multiverse analysis"
 shorttitle        : "Title"
@@
 ```{r load-targets, include=FALSE}
+model_list_by_age_fixedef <- tar_read(model_list_by_age_fixedef)
 tar_load(data_clean)
-tar_load(purdy_pictures)
-tar_load(model_tables)
-tar_load(demog_table)
-tar_load(table_1)
+tar_load(purdy_pictures_by_age_fixedef)
+model_tables <- tar_read(model_tables_fixedef)
 pretty <- function(x) format(x, big.mark = ",")
@@
 
-The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
-Table \@ref(tab:demo-participants) shows demographic information for all participants.
-A table of study characteristics can be found in supplementary materials.
+```{r}
+n_participants <- length(unique(data_clean$participant_id))
+```
 
-```{r demo-participants}
-papaja::apa_table(demog_table,
-  caption = "Participant characteristics",
-  note = glue::glue("For categorical variables the value is the count, and percentage.
-For numeric variables the value is the Mean and SD.
-N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
-  landscape = TRUE,
-  col_spanners = list("Age group" = c(2, 6))
-)
-```
+## Multiverse
+
+In this document we show the results using another analytic technique. Namely treating study ID as a fixed effect. This is what we wrote in the protocol originally.
 
@@
 We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
-There was no meaningful relationship between physical activity volume and sleep duration.
-However, we observed a curvilinear relationships between physical activity volume and sleep efficiency, onset, and regularity, all of which interacted with age.
-Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
-Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
-There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
-For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.
 
@@
 ```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age_fixedef.jpg"), error = FALSE)
 ```
@@
 We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
-We found that higher physical activity intensity is directly proportional to longer sleep duration and better sleep efficiency.
-In the case of older participants, physical activity intensity had a U-shaped relationship with sleep onset, meaning that individuals with very low or very high physical activity intensity had longer sleep onset.
-We also found a strong link between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
 
 ```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age_fixedef.jpg"), error = FALSE)
 ```
@@
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
-As age increases, both physical activity volume and intensity decrease.
-We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.
 
@@
 ```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
 ```
@@
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
-We did not find a relationship between physical activity volume and sleep efficiency.
-However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.
 
 ```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
 ```
@@
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
-There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
-The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.
 
 ```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
 ```
@@
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
-There was a U-shaped relationship between sleep regularity and physical activity volume.
-Participants with below-average sleep regularity tended to have average physical activity volume.
-Increases in regularity above the average were linked to greater physical activity volume.
-There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
-Greater sleep regularity was associated with greater physical activity the following day.
 
 ```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
 ```

### 2023-03-17 R/clean_data.R

@@ -272,5 +272,11 @@ clean_data <- function(data_joined, region_lookup) {
     )) %>%
     ungroup()
 
+  # Setting up variables for fixed-effects nested analysis
+  # I don't think it's appropriate for participants to be nested within measurement day
+  # As then the same participant on different days will be treated as different people.
+  d$studyid <- as.factor(d$studyid)
+  d$measurement_day <- as.factor(paste0(as.numeric(d$studyid), "_", d$measurement_day))
+
   d
 }

### 2023-03-17 R/make_model_list.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author conig
 #' @export
-make_model_list <- function(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65", control_vars = c("ses", "sex", "bmi")) {
+make_model_list <- function(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65", control_vars = c("ses", "sex", "bmi"), ranef  = "(1|studyid) + (1|measurement_day) + (1|participant_id)") {
 
   sleep_vars <- c("scale_sleep_duration",
                     "scale_sleep_efficiency",
@@ -48,7 +48,8 @@ make_model_list <- function(data_imp, moderator = "age", moderator_term = "11, 1
         outcome = instructions[i, "outcome"],
         predictors = instructions[i, "predictors"],
         control_vars = control_vars,
-        table_only = FALSE
+        table_only = FALSE,
+        ranef = ranef
       )
 
     attr(model, "terms") <- c(paste0(gsub(" .*", "" ,instructions[i, "predictors"]), "[-4:4 by = 0.1]"), glue::glue("{moderator} [{moderator_term}]"))

### 2023-03-17 R/model_builder.R

@@ -15,7 +15,8 @@ model_builder <-
            outcome,
            predictors,
            control_vars = c(),
-           table_only = TRUE) {
+           table_only = TRUE,
+           ranef = "(1|studyid/measurement_day/participant_id)") {
 
     require(broom.mixed)
     require(lme4)
@@ -23,7 +24,7 @@ model_builder <-
 
     formula <-
       glue::glue(
-        "{outcome} ~ {paste(predictors, collapse = ' + ')} + {paste(control_vars, collapse = ' + ')} + (1|participant_id) + (1|measurement_day) + (1|studyid)"
+        "{outcome} ~ {paste(predictors, collapse = ' + ')} + {paste(control_vars, collapse = ' + ')} + {ranef}"
       )
 
     formula <- gsub("\\+  \\+", "+", formula)
@@ -102,74 +103,7 @@ model_builder <-
 
                                       )]
 
-    if (table_only)
-      return(tabby)
-
-    list(model = m,
-         pooled_model = pool(m),
-         table = tabby)
-
-  }
-
-model_builder_fixedef <-
-  function(data_imp,
-           outcome,
-           predictors,
-           control_vars = c(),
-           table_only = TRUE) {
-
-    require(broom.mixed)
-    require(data.table)
-
-    formula <-
-      glue::glue(
-        "{outcome} ~ {paste(predictors, collapse = ' + ')} + {paste(control_vars, collapse = ' + ')} + participant_id + measurement_day"
-      )
-
-    formula <- gsub("\\+  \\+", "+", formula)
-
-    fit_model <- function(..., data){
-        mod <- lm(
-          ...,
-          data,
-          control = lmerControl(
-            optimizer = meth.tab[i, 1],
-            optCtrl = optCtrl
-          ))
-
-    }
-
-    imp_list <- complete(data_imp, "all")
-
-    m <- lapply(imp_list, function(x){
-
-      fit_model(formula = eval(parse(text = formula)), data = x)
-
-    })
-
-
-    m_pooled <- pool(m)
-    pool_summary <- data.table(summary(m_pooled))
-
-    crit.val <- qnorm(1 - 0.05 / 2)
-
-    pool_summary$lower <-
-      print_num(with(pool_summary, estimate - crit.val * std.error))
-    pool_summary$upper <-
-      print_num(with(pool_summary, estimate + crit.val * std.error))
-
-    tabby <- data.table(pool_summary)[,
-                                      list(
-                                        term = term,
[…]

### 2023-03-17 R/produce_purdy_pictures.R

@@ -2,7 +2,7 @@
 #' @param model_list list of RQ1 models
 #' @example  model_list <- model_list_by_age
 
-produce_purdy_pictures <- function(model_list, paste_facet_labels = ""){
+produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_filename = ""){
 
   dat_list <- lapply(seq_len(length(model_list)), function(i){
 
@@ -41,12 +41,14 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = ""){
       labs(x = x_lab,
            fill = stringr::str_to_sentence(unique(plot_dat$moderator))) +
       figure_theme() +
-    theme(legend.position = "none")
+    theme(legend.position = "none") +
+    scale_x_continuous(limits = c(-4,4)) +
+    scale_y_continuous(limits = c(-4,4))
 
     outcome <- unique(gsub(" .*","", pdat$outcome))
     if(length(outcome) > 1) stop("Outcome length is greater than 1")
 
-    filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}.jpg" |>
+    filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}{add_filename}.jpg" |>
       glue::glue()
 
     if(outcome == "Sleep"){

### 2023-03-17 _targets.R

@@ -59,9 +59,29 @@ list(
   # Tables
   tar_target(model_tables, make_model_tables(model_list_by_age)),
 
+  # Multiverse
+  # Using study id as a fixed effect
+  tar_target(
+    model_list_by_age_fixedef,
+    make_model_list(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65",
+                    ranef = "(1 | measurement_day) + (1 | participant_id)",
+                    c("ses", "sex", "bmi", "studyid"))
+  ),
+  tar_target(model_tables_fixedef, make_model_tables(model_list_by_age_fixedef)),
+
+  tar_target(
+    purdy_pictures_by_age_fixedef,
+    produce_purdy_pictures(model_list_by_age_fixedef,
+                           paste_facet_labels = " years",
+                           add_filename = "_fixedef")
+  ),
+
   # Output manuscript
   tar_render(manuscript, "doc/manuscript.Rmd", output_format = c(
     "papaja::apa6_docx",
+    "papaja::apa6_pdf"
+  )),
+  tar_render(multiverse, "doc/multiverse.Rmd", output_format = c(
     "papaja::apa6_pdf"
   ))
 )

### 2023-03-17 doc/manuscript.Rmd
increase table spacing

@@
 
-\renewcommand{\arraystretch}{0.65}
+\renewcommand{\arraystretch}{0.7}
 
@@
 tar_load(data_clean)
-tar_load(purdy_pictures)
+tar_load(purdy_pictures_by_age)
 tar_load(model_tables)
 tar_load(demog_table)
-tar_load(table_1)
 pretty <- function(x) format(x, big.mark = ",")
@@
 
-The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
+```{r}
+n_participants <- length(unique(data_clean$participant_id))
+```
+
+The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r n_participants |> pretty()` unique participants.
 Table \@ref(tab:demo-participants) shows demographic information for all participants.
@@
   caption = "Participant characteristics",
-  note = glue::glue("For categorical variables the value is the count, and percentage.
-For numeric variables the value is the Mean and SD.
-N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
+  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {n_participants |> pretty()}"),
   landscape = TRUE,

### 2023-03-21 doc/multiverse.Rmd
increase table spacing
Add in moderation to supps 🥵

@@
 classoption       : "man"
-output            : papaja::apa6_docx
+
+header-includes:
+ - \usepackage[maxfloats=256]{morefloats}
+
+output            : papaja::apa6_pdf
+
 ---
 
-\renewcommand{\arraystretch}{0.65}
+```{comment}
+I needed to add maxdeadcycles and more floats to support how many figures are in this doc.
+```
+
+\renewcommand{\arraystretch}{0.7}
+\maxdeadcycles=1000
 
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.pos = "!htbp")
 source("R/utils.R")
@@
 ```
+
+# Moderation
+
+In the following section we present models for a range of moderators which were pre-defined in our protocol.
+
+```{r include = FALSE, eval = FALSE}
+pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")
+
+moderator_df <- data.frame(
+  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
+  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
+  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
+)
+moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)
+
+lapply(seq_len(nrow(moderator_df)), function(r){
+
+  moderator <- moderator_df$moderator[r]
+  moderator_fig <- gsub("_","-",moderator)
+  moderator_formal <- moderator_df$moderator_formal[r]
+  moderator_sentence <- moderator_df$moderator_sentence[r]
+  image_path <- moderator_df$image_path[r]
+
+  glue::glue(pattern, .open = "_::", .close = "::_")
+
+}) |> paste(collapse = "\n") |> 
+  clipr::write_clip()
+
+```
+
+\clearpage
+
+## BMI
+
+```{r}
+tar_load(model_tables_bmi)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)
+
+```{r sleep-outcomes-by-bmi}
+papaja::apa_table(
+  model_tables_bmi$sleep$data,
+  caption = model_tables_bmi$sleep$caption,
+  note = model_tables_bmi$sleep$note,
+  col_spanners = model_tables_bmi$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Bmi.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by BMI
+
+We estimated how physical activity intensity affects sleep across BMI
+We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).
+
+```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Bmi.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by BMI
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
+
+```{r pa-outcomes-by-bmi}
+papaja::apa_table(
+  model_tables_bmi$physical_activity$data,
+  caption = model_tables_bmi$physical_activity$caption,
+  note = model_tables_bmi$physical_activity$note,
+  col_spanners = model_tables_bmi$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activty by sleep duration moderated by BMI"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by BMI.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-bmi).
+
+```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activty by sleep efficiency moderated by BMI"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by BMI
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).
+
+```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activty by sleep onset moderated by BMI"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by BMI.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).
+
+```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activty by sleep regularity moderated by BMI"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
+```
+\clearpage
+
+## SES
+
+```{r}
+tar_load(model_tables_ses)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)
+
+```{r sleep-outcomes-by-ses}
+papaja::apa_table(
+  model_tables_ses$sleep$data,
+  caption = model_tables_ses$sleep$caption,
+  note = model_tables_ses$sleep$note,
+  col_spanners = model_tables_ses$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Ses.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by SES
+
+We estimated how physical activity intensity affects sleep across SES
+We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).
+
+```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Ses.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by SES
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
+
+```{r pa-outcomes-by-ses}
+papaja::apa_table(
+  model_tables_ses$physical_activity$data,
+  caption = model_tables_ses$physical_activity$caption,
+  note = model_tables_ses$physical_activity$note,
+  col_spanners = model_tables_ses$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activty by sleep duration moderated by SES"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by SES.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ses).
+
+```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activty by sleep efficiency moderated by SES"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by SES
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).
+
+```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activty by sleep onset moderated by SES"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by SES.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).
+
+```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activty by sleep regularity moderated by SES"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
+```
+\clearpage
+
+## sex
+
+```{r}
+tar_load(model_tables_sex)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)
+
+```{r sleep-outcomes-by-sex}
+papaja::apa_table(
+  model_tables_sex$sleep$data,
+  caption = model_tables_sex$sleep$caption,
+  note = model_tables_sex$sleep$note,
+  col_spanners = model_tables_sex$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Sex.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by sex
+
+We estimated how physical activity intensity affects sleep across sex
+We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).
+
+```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Sex.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by sex
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
+
+```{r pa-outcomes-by-sex}
+papaja::apa_table(
+  model_tables_sex$physical_activity$data,
+  caption = model_tables_sex$physical_activity$caption,
+  note = model_tables_sex$physical_activity$note,
+  col_spanners = model_tables_sex$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activty by sleep duration moderated by sex"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by sex.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-sex).
+
+```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activty by sleep efficiency moderated by sex"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by sex
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).
+
+```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activty by sleep onset moderated by sex"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by sex.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).
+
+```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activty by sleep regularity moderated by sex"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
+```
+\clearpage
+
+## weekday
+
+```{r}
+tar_load(model_tables_weekday)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)
+
+```{r sleep-outcomes-by-weekday}
+papaja::apa_table(
+  model_tables_weekday$sleep$data,
+  caption = model_tables_weekday$sleep$caption,
+  note = model_tables_weekday$sleep$note,
+  col_spanners = model_tables_weekday$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Weekday_x.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by weekday
+
+We estimated how physical activity intensity affects sleep across weekday
+We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).
+
+```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Weekday_x.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by weekday
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
+
+```{r pa-outcomes-by-weekday}
+papaja::apa_table(
+  model_tables_weekday$physical_activity$data,
+  caption = model_tables_weekday$physical_activity$caption,
+  note = model_tables_weekday$physical_activity$note,
+  col_spanners = model_tables_weekday$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activty by sleep duration moderated by weekday"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by weekday.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-weekday).
+
+```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activty by sleep efficiency moderated by weekday"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by weekday
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).
+
+```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activty by sleep onset moderated by weekday"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by weekday.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).
+
+```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activty by sleep regularity moderated by weekday"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
+```
+\clearpage
+
+## season
+
+```{r}
+tar_load(model_tables_season)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by season, and the results are presented in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-volume-fig-by-season)
+
+```{r sleep-outcomes-by-season}
+papaja::apa_table(
+  model_tables_season$sleep$data,
+  caption = model_tables_season$sleep$caption,
+  note = model_tables_season$sleep$note,
+  col_spanners = model_tables_season$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-season, fig.cap = "Sleep metrics on Physical activity volume by season"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Season.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by season
+
+We estimated how physical activity intensity affects sleep across season
+We present the results in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-intensity-fig-by-season).
+
+```{r sleep-by-intensity-fig-by-season, fig.cap = "Sleep metrics on Physical activity intensity moderated by season"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Season.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by season
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
+
+```{r pa-outcomes-by-season}
+papaja::apa_table(
+  model_tables_season$physical_activity$data,
+  caption = model_tables_season$physical_activity$caption,
+  note = model_tables_season$physical_activity$note,
+  col_spanners = model_tables_season$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activty by sleep duration moderated by season"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by season.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-season).
+
+```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activty by sleep efficiency moderated by season"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by season
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).
+
+```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activty by sleep onset moderated by season"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by season.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).
+
+```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activty by sleep regularity moderated by season"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
+```
+\clearpage
+
+## region
+
+```{r}
+tar_load(model_tables_region)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by region, and the results are presented in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-volume-fig-by-region)
+
+```{r sleep-outcomes-by-region}
+papaja::apa_table(
+  model_tables_region$sleep$data,
+  caption = model_tables_region$sleep$caption,
+  note = model_tables_region$sleep$note,
+  col_spanners = model_tables_region$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-region, fig.cap = "Sleep metrics on Physical activity volume by region"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Region.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by region
+
+We estimated how physical activity intensity affects sleep across region
+We present the results in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-intensity-fig-by-region).
+
+```{r sleep-by-intensity-fig-by-region, fig.cap = "Sleep metrics on Physical activity intensity moderated by region"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Region.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by region
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
+
+```{r pa-outcomes-by-region}
+papaja::apa_table(
+  model_tables_region$physical_activity$data,
+  caption = model_tables_region$physical_activity$caption,
+  note = model_tables_region$physical_activity$note,
+  col_spanners = model_tables_region$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activty by sleep duration moderated by region"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by region.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-region).
+
+```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activty by sleep efficiency moderated by region"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by region
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).
+
+```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activty by sleep onset moderated by region"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by region.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).
+
+```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activty by sleep regularity moderated by region"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
+```
+\clearpage
+
+## daylight hours
+
+```{r}
+tar_load(model_tables_daylight)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight)
+
+```{r sleep-outcomes-by-daylight}
+papaja::apa_table(
+  model_tables_daylight$sleep$data,
+  caption = model_tables_daylight$sleep$caption,
+  note = model_tables_daylight$sleep$note,
+  col_spanners = model_tables_daylight$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Daylight_hours.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by daylight hours
+
+We estimated how physical activity intensity affects sleep across daylight hours
+We present the results in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight).
+
+```{r sleep-by-intensity-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Daylight_hours.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by daylight hours
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).
+
+```{r pa-outcomes-by-daylight}
+papaja::apa_table(
+  model_tables_daylight$physical_activity$data,
+  caption = model_tables_daylight$physical_activity$caption,
+  note = model_tables_daylight$physical_activity$note,
+  col_spanners = model_tables_daylight$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activty by sleep duration moderated by daylight hours"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by daylight hours.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight).
+
+```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activty by sleep efficiency moderated by daylight hours"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by daylight hours
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight).
+
+```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activty by sleep onset moderated by daylight hours"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by daylight hours.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).
+
+```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activty by sleep regularity moderated by daylight hours"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
+```
+\clearpage
+
+## wear location
+
+```{r}
+tar_load(model_tables_wear_location)
+```
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)
+
+```{r sleep-outcomes-by-wear_location}
+papaja::apa_table(
+  model_tables_wear_location$sleep$data,
+  caption = model_tables_wear_location$sleep$caption,
+  note = model_tables_wear_location$sleep$note,
+  col_spanners = model_tables_wear_location$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Accelerometer_wear_location.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by wear location
+
+We estimated how physical activity intensity affects sleep across wear location
+We present the results in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).
+
+```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Accelerometer_wear_location.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by wear location
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).
+
+```{r pa-outcomes-by-wear_location}
+papaja::apa_table(
+  model_tables_wear_location$physical_activity$data,
+  caption = model_tables_wear_location$physical_activity$caption,
+  note = model_tables_wear_location$physical_activity$note,
+  col_spanners = model_tables_wear_location$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+\clearpage
+
+```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activty by sleep duration moderated by wear location"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by wear location.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear_location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).
+
+```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activty by sleep efficiency moderated by wear location"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by wear location
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-wear-location).
+
+```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activty by sleep onset moderated by wear location"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by wear location.
+Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
+
+```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activty by sleep regularity moderated by wear location"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+```

### 2023-03-21 R/make_data_imp.R

@@ -11,7 +11,7 @@
 
 make_data_imp <- function(data, n_imps = 3) {
   data <- data %>%
-    select(-n_valid_hours, -n_hours, -weekday_x, -day_zero)
+    select(-n_valid_hours, -n_hours, -day_zero)
 
   # Empty imputation to change defaults:
   m0 <- mice(data, maxit = 0)

### 2023-03-21 R/make_model_tables.R

@@ -6,6 +6,7 @@
 #' @param model_list
 #' @return list of tables
 #' @author Taren Sanders
+#' @test model_list <- model_list_by_wear_location
 #' @export
 make_model_tables <- function(model_list) {
   note <- "Adjusted for SES, BMI, and sex."
@@ -81,7 +82,8 @@ make_model_tables <- function(model_list) {
 format_table <- function(tab) {
   tab$term <- gsub("I\\(", "", tab$term) |>
     gsub("_", " ", x = _) |>
-    gsub("\\^2\\)", "$^2$", x = _)
+    gsub("\\^2\\)", "$^2$", x = _) |>
+    gsub("accelerometer wear location", "", x = _ )
   tab <- tab[!grepl("^ses", tab$term), ]
   tab <- tab[!grepl("^sex", tab$term), ]
   tab <- tab[!grepl("^bmi", tab$term), ]

### 2023-03-21 R/model_builder.R

@@ -1,3 +1,55 @@
+is_conv <- function(x) performance::check_convergence(x) & !performance::check_singularity(x)
+
+#' fit_model
+#'
+#' A function to fit a model with a range of optimizers
+#' @param ... arguments passed to lmer
+#' @param data data object
+
+fit_model <- function(..., data, max_iter = 1e6){
+  require(optimx)
+  require(lme4)
+  require(dfoptim)
+
+  conv <- FALSE
+  exhausted <- FALSE
+  i <- 1
+  meth.tab <- lme4:::meth.tab.0
+  meth.tab <- cbind(meth.tab, maxit_name = c("maxfun", "maxfun", "maxit", "maxfeval", "maxit", "maxeval","maxeval"))
+  meth.tab <- meth.tab[sample(seq_len(nrow(meth.tab)), nrow(meth.tab), replace = FALSE), ]
+
+  while(!conv & i <= nrow(meth.tab)) {
+    if(meth.tab[i , 2] != ""){
+      optCtrl <- list(method = unname(meth.tab[i , 2]))
+    }else{
+      optCtrl <- list()
+    }
+
+    optCtrl[[meth.tab[i , 3]]] <- max_iter
+
+    mod <- lme4::lmer(
+      ...,
+      data = data,
+      control = lmerControl(
+        optimizer = meth.tab[i, 1],
+        optCtrl = optCtrl
+      ))
+    mod@call$control$optimizer <- unname(meth.tab[i, 1])
+    mod@call$control$optCtrl <- unlist(optCtrl)
+
+    if (is_conv(mod)){
+      conv <- TRUE
+      attr(mod, "conv") <- TRUE
+      return(mod)
+    }
+    i = i + 1
+  }
+  warning("No convergence with any optimizer:" , ...)
+  attr(mod, "conv") <- FALSE
+  mod
+}
+
+
 
 #' model_builder
 #'
@@ -30,62 +82,21 @@ model_builder <-
 
     formula <- gsub("\\+  \\+", "+", formula)
 
-    fit_model <- function(..., data, max_iter = 1e6){
-      require(optimx)
-      require(lme4)
-      require(dfoptim)
-
-      conv <- FALSE
-      exhausted <- FALSE
-      i <- 1
-      meth.tab <- lme4:::meth.tab.0
[…]

### 2023-03-21 R/produce_purdy_pictures.R

@@ -1,6 +1,8 @@
 #' produce_purdy_pictures
 #' @param model_list list of RQ1 models
-#' @example  model_list <- model_list_by_age
+#' @example  model_list <- model_list_by_daylight
+#' @details I check the proporiton of models that converged. If less then 75% of models converged
+#' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge
 
 produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_filename = ""){
 
@@ -8,6 +10,8 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
 
     m <- model_list[[i]]
     terms <- attr(m, "terms")
+    conv <- attr(m$pooled_model, "conv")
+    conv_print <- paste0( papaja::print_num((1 -conv) * 100), "%")
 
     dt <- data.table(get_effects(m, terms = terms))
     dt$x_name = terms[1]
@@ -15,6 +19,14 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     dt$outcome = gsub(" .*","",names(model_list)[[i]])
     dt$RQ <- attr(m, "RQ")
     dt$moderator <- attr(m, "moderator")
+    dt$conv_p <- conv
+    if(conv < .75){
+      # dt[,c("predicted","conf.low","conf.high")] <- NA
+      dt$message <- as.character(glue::glue("DID NOT CONVERGE ({conv_print})"))
+    }else{
+      dt$message <- " "
+    }
+    attr(dt, "conv") <- conv
     dt
 
   })
@@ -25,7 +37,7 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     gsub("_", " ", x = _) |>
     stringr::str_to_title() |>
     paste("(z)")
-  plot_dat$group <- paste0(plot_dat$group, paste_facet_labels)
+  levels(plot_dat$group) <- paste0(levels(plot_dat$group), paste_facet_labels)
   plot_dat$x_name <- gsub("\\[.*","", plot_dat$x_name)
 
 
@@ -33,6 +45,8 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
 
   p <- function(x_var, x_lab, rq){
     pdat <- plot_dat[x_name == x_var & RQ == rq]
+
+  conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
 
[…]

### 2023-03-21 R/utils.R

@@ -89,3 +89,4 @@ get_season <- function(date, lat){
 }
 
 find_max  <- function(x) {names(which.max(table(x)))}
+

### 2023-03-21 _targets.R

@@ -39,13 +39,69 @@ list(
     make_model_list(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65")
   ),
   tar_target(
+    model_list_by_bmi,
+    make_model_list(
+      data_imp,
+      moderator = "bmi",
+      moderator_term = "18, 22, 25, 30",
+      control_vars = c("ses", "age", "sex"))
+  ),
+  tar_target(
+    model_list_by_ses,
+    make_model_list(
+      data_imp,
+      moderator = "ses",
+      moderator_term = "all",
+      control_vars = c("bmi", "age", "sex"))
+  ),
+  tar_target(
     model_list_by_sex,
     make_model_list(
       data_imp,
       moderator = "sex",
       moderator_term = "all",
       control_vars = c("ses", "age", "bmi"))
-    ),
+  ),
+  tar_target(
+    model_list_by_weekday,
+    make_model_list(
+      data_imp,
+      moderator = "weekday_x",
+      moderator_term = "all",
+      control_vars = c("bmi", "age", "sex"))
+  ),
+  tar_target(
+    model_list_by_season,
+    make_model_list(
+      data_imp,
+      moderator = "season",
+      moderator_term = "all",
+      control_vars = c("bmi", "age", "sex"))
+  ),
+  tar_target(
+    model_list_by_region,
+    make_model_list(
+      data_imp,
+      moderator = "region",
+      moderator_term = "all",
+      control_vars = c("ses", "age", "sex"))
+  ),
+  tar_target(
+    model_list_by_daylight,
+    make_model_list(
+      data_imp,
+      moderator = "daylight_hours",
+      moderator_term = "8, 10, 12, 14",
+      control_vars = c("bmi", "age", "sex"))
+  ),
+  tar_target(
+    model_list_by_wear_location,
+    make_model_list(
+      data_imp,
+      moderator = "accelerometer_wear_location",
+      moderator_term = "all",
+      control_vars = c("bmi", "age", "sex"))
+  ),
 
   tar_target(model_diagnostics, make_model_diagnostics(model_list_by_age)),
 
@@ -60,12 +116,48 @@ list(
                            paste_facet_labels = " years")
   ),
   tar_target(
+    purdy_pictures_by_bmi,
+    produce_purdy_pictures(model_list_by_bmi)
+  ),
+  tar_target(
+    purdy_pictures_by_ses,
+    produce_purdy_pictures(model_list_by_ses)
+  ),
[…]

### 2023-03-21 doc/manuscript.Rmd
Spelling errors fixed

@@
 
-```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
+```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
 knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
+```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
 knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
+```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
 knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
+```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
 knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)

### 2023-03-21 doc/multiverse.Rmd
Spelling errors fixed

@@
 
-```{r PA-by-sleep-duration-fig, fig.cap = "Physical activty by sleep duration"}
+```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
 knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activty by sleep efficiency"}
+```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
 knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig, fig.cap = "Physical activty by sleep onset"}
+```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
 knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activty by sleep regularity"}
+```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
 knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
@@
 
-```{r include = FALSE, eval = FALSE}
+```{r eval = FALSE}
 pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")
@@
 
-}) |> paste(collapse = "\n") |> 
-  clipr::write_clip()
+}) |> paste(collapse = "\n") |> clipr::write_clip()
 
 ```
+
+<!------------------------------------>
+<!-- Auto-generated chunks go here: -->
+<!------------------------------------>
 
@@
 ```
-
-\clearpage
 
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activty by sleep duration moderated by BMI"}
+```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activty by sleep efficiency moderated by BMI"}
+```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activty by sleep onset moderated by BMI"}
+```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activty by sleep regularity moderated by BMI"}
+```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activty by sleep duration moderated by SES"}
+```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activty by sleep efficiency moderated by SES"}
+```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activty by sleep onset moderated by SES"}
+```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activty by sleep regularity moderated by SES"}
+```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activty by sleep duration moderated by sex"}
+```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activty by sleep efficiency moderated by sex"}
+```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activty by sleep onset moderated by sex"}
+```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activty by sleep regularity moderated by sex"}
+```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activty by sleep duration moderated by weekday"}
+```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activty by sleep efficiency moderated by weekday"}
+```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activty by sleep onset moderated by weekday"}
+```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activty by sleep regularity moderated by weekday"}
+```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activty by sleep duration moderated by season"}
+```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activty by sleep efficiency moderated by season"}
+```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activty by sleep onset moderated by season"}
+```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activty by sleep regularity moderated by season"}
+```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activty by sleep duration moderated by region"}
+```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activty by sleep efficiency moderated by region"}
+```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activty by sleep onset moderated by region"}
+```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activty by sleep regularity moderated by region"}
+```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activty by sleep duration moderated by daylight hours"}
+```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activty by sleep efficiency moderated by daylight hours"}
+```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activty by sleep onset moderated by daylight hours"}
+```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activty by sleep regularity moderated by daylight hours"}
+```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
@@
 
-\clearpage
-
-```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activty by sleep duration moderated by wear location"}
+```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activty by sleep efficiency moderated by wear location"}
+```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activty by sleep onset moderated by wear location"}
+```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activty by sleep regularity moderated by wear location"}
+```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
 knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
 ```
+
+<!-- Finish auto-generated chunks go here: -->

### 2023-03-21 R/produce_purdy_pictures.R

@@ -59,7 +59,7 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     scale_x_continuous(limits = c(-4,4)) +
     scale_y_continuous(limits = c(-4,4)) +
     geom_text(data = conv_message_dat, aes(x = 0, y = 0, label = message, ),
-              hjust = .5, vjust = .5, size = 3, color = "black", family = "serif",
+              hjust = .5, vjust = .5, size = 2, color = "black", family = "serif",
               fontface = "bold",
               show.legend = FALSE, inherit.aes = FALSE)
 

### 2023-03-21 doc/multiverse.Rmd
Line removal
Update headers in results chunk

@@
 <!------------------------------------>
-
 \clearpage
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by BMI
 
@@
 We estimated the effect of sleep duration on physical activity by BMI
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
 
@@
 We estimated the effect of sleep regularity on physical activity by BMI.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).
+Results are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by SES
 
@@
 We estimated the effect of sleep duration on physical activity by SES
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
 
@@
 We estimated the effect of sleep regularity on physical activity by SES.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).
+Results are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by sex
 
@@
 We estimated the effect of sleep duration on physical activity by sex
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
 
@@
 We estimated the effect of sleep regularity on physical activity by sex.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).
+Results are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by weekday
 
@@
 We estimated the effect of sleep duration on physical activity by weekday
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
 
@@
 We estimated the effect of sleep regularity on physical activity by weekday.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).
+Results are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by season
 
@@
 We estimated the effect of sleep duration on physical activity by season
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
 
@@
 We estimated the effect of sleep regularity on physical activity by season.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).
+Results are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by region
 
@@
 We estimated the effect of sleep duration on physical activity by region
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
 
@@
 We estimated the effect of sleep regularity on physical activity by region.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).
+Results are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by daylight hours
 
@@
 We estimated the effect of sleep duration on physical activity by daylight hours
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).
 
@@
 We estimated the effect of sleep regularity on physical activity by daylight hours.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).
+Results are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).
 
@@
 
-### The effects of physical activity volume on sleep
+### The effects of physical activity volume on sleep by wear location
 
 We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)
+We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)
 
-```{r sleep-outcomes-by-wear_location}
+```{r sleep-outcomes-by-wear-location}
 papaja::apa_table(
@@
 We estimated how physical activity intensity affects sleep across wear location
-We present the results in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).
+We present the results in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).
 
@@
 We estimated the effect of sleep duration on physical activity by wear location
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).
 
-```{r pa-outcomes-by-wear_location}
+```{r pa-outcomes-by-wear-location}
 papaja::apa_table(
@@
 We estimated the effect of sleep efficiency on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear_location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).
 
@@
 We estimated the effect of sleep regularity on physical activity by wear location.
-Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
+Results are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
 

### 2023-03-22 doc/manuscript.Rmd
Made table captions easier to understand. Also fixed capitalisation of PA in figures. Make manuscript use model_tables_age, not model_tables.

@@
 tar_load(purdy_pictures_by_age)
-tar_load(model_tables)
+tar_load(model_tables_age)
 tar_load(demog_table)
 pretty <- function(x) format(x, big.mark = ",")
+
 ```
@@
 papaja::apa_table(
-  model_tables$sleep$data,
-  caption = model_tables$sleep$caption,
-  note = model_tables$sleep$note,
-  col_spanners = model_tables$sleep$col_spanners,
+  model_tables_age$sleep$data,
+  caption = model_tables_age$sleep$caption,
+  note = model_tables_age$sleep$note,
+  col_spanners = model_tables_age$sleep$col_spanners,
   escape = FALSE,
@@
 papaja::apa_table(
-  model_tables$physical_activity$data,
-  caption = model_tables$physical_activity$caption,
-  note = model_tables$physical_activity$note,
-  col_spanners = model_tables$physical_activity$col_spanners,
+  model_tables_age$physical_activity$data,
+  caption = model_tables_age$physical_activity$caption,
+  note = model_tables_age$physical_activity$note,
+  col_spanners = model_tables_age$physical_activity$col_spanners,
   escape = FALSE,

### 2023-03-22 R/make_model_tables.R

@@ -51,8 +51,8 @@ make_model_tables <- function(model_list) {
   })
 
   sleep_table$caption <-
-    glue::glue("Physical activity on sleep controlling for {control_vars}")
-  sleep_table$note <- note
+    glue::glue("Physical activity predicting sleep controlling for {control_vars}.")
+  sleep_table$note <- paste0(note, ". Outcomes variables are listed in the column headers.")
 
   sleep_conv_issue <- any(sapply(sleep_table$data, function(x) any(grepl("\\\\dagger", x$"$\\beta$ [95\\% CI]"))))
 
@@ -84,8 +84,8 @@ make_model_tables <- function(model_list) {
   })
 
   pa_table$caption <-
-    glue::glue("Sleep on physical activity controlling for {control_vars}")
-  pa_table$note <- note
+    glue::glue("Sleep predicting physical activity controlling for {control_vars}")
+  pa_table$note <- paste0(note, ". Outcomes variables are listed in the row headers.")
 
   pa_conv_issue <- any(sapply(pa_table$data, function(x) any(grepl("\\\\dagger", x$"$\\beta$ [95\\% CI]"))))
 

### 2023-03-22 R/produce_purdy_pictures.R

@@ -37,6 +37,8 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     gsub("_", " ", x = _) |>
     stringr::str_to_title() |>
     paste("(z)")
+  plot_dat$outcome <- gsub("Pa", "PA", plot_dat$outcome)
+
   levels(plot_dat$group) <- paste0(levels(plot_dat$group), paste_facet_labels)
   plot_dat$x_name <- gsub("\\[.*","", plot_dat$x_name)
 

### 2023-03-22 doc/manuscript.Rmd
Add weekday description.

@@
 n_participants <- length(unique(data_clean$participant_id))
+weekday_table <- (data_clean$weekday_x) |> table()
+weekday <- chisq.test(weekday_table)
+weekday_res <-glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")
+
 ```
@@
 Table \@ref(tab:demo-participants) shows demographic information for all participants.
+Observations were not uniform across the days of the week `r weekday_res`.
+There were fewer observations on Monday (z = `r weekday$stdres["Monday"]`) and Sunday  (z = `r weekday$stdres["Sunday"]`); and more on Wednesday (z = `r weekday$stdres["Wednesday"]`).
 A table of study characteristics can be found in supplementary materials.

### 2023-03-28 doc/multiverse.Rmd
merge
update assets

@@
 n_participants <- length(unique(data_clean$participant_id))
+```
+
+## Model diagnostics
+
+The model diagnostics for the main analysis, and for all models presented in this document are in Table \@ref(tab:model-diagnostics)
+
+```{r model-diagnostics}
+tar_read(model_diagnostics) |> 
+  papaja::apa_table(caption = "Model diagnostics", escape = FALSE,
+                    longtable = TRUE)
 ```
@@
 )
-moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)
 
@@
   moderator_formal <- moderator_df$moderator_formal[r]
-  moderator_sentence <- moderator_df$moderator_sentence[r]
   image_path <- moderator_df$image_path[r]
@@
 <!------------------------------------>
+
 \clearpage

### 2023-03-28 doc/multiverse.Rmd
Add in time of day relating to most active periods for moderation
Fixes #71

--- 2023-03-21 doc/multiverse.Rmd
@@
 moderator_df <- data.frame(
-  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
-  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
-  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
+  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
+  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
+  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
 )
@@
 ```
+\clearpage
+
+## most active hour
+
+```{r}
+tar_load(model_tables_pa_mostactivehr)
+```
+
+### The effects of physical activity volume on sleep by most active hour
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effect of physical activity volume on sleep by most active hour, and the results are presented in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-volume-fig-by-pa-mostactivehr)
+
+```{r sleep-outcomes-by-pa-mostactivehr}
+papaja::apa_table(
+  model_tables_pa_mostactivehr$sleep$data,
+  caption = model_tables_pa_mostactivehr$sleep$caption,
+  note = model_tables_pa_mostactivehr$sleep$note,
+  col_spanners = model_tables_pa_mostactivehr$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r sleep-by-volume-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity volume by most active hour"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Pa_mostactivehr.jpg"), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by most active hour
+
+We estimated how physical activity intensity affects sleep across most active hour
+We present the results in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-intensity-fig-by-pa-mostactivehr).
+
+```{r sleep-by-intensity-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity intensity moderated by most active hour"}
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Pa_mostactivehr.jpg"), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by most active hour
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-pa-mostactivehr).
+
+```{r pa-outcomes-by-pa-mostactivehr}
+papaja::apa_table(
+  model_tables_pa_mostactivehr$physical_activity$data,
+  caption = model_tables_pa_mostactivehr$physical_activity$caption,
+  note = model_tables_pa_mostactivehr$physical_activity$note,
+  col_spanners = model_tables_pa_mostactivehr$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r PA-by-sleep-duration-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep duration moderated by most active hour"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Pa_mostactivehr.jpg"), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by most active hour.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-pa-mostactivehr).
+
+```{r PA-by-sleep-efficiency-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep efficiency moderated by most active hour"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Pa_mostactivehr.jpg"), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by most active hour
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).
+
+```{r PA-by-sleep-onset-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep onset moderated by most active hour"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Pa_mostactivehr.jpg"), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by most active hour.
+Results are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-pa-mostactivehr).
+
+```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Pa_mostactivehr.jpg"), error = FALSE)
+```
 

### 2023-03-28 R/clean_data.R

@@ -16,6 +16,7 @@ clean_data <- function(data_joined, region_lookup) {
       pa_volume = acc_day_mg,
       pa_intensity = ig_gradient,
       pa_intensity_m16 = m16_ig_gradient_enmo_mg_0_24hr,
+      pa_mostactivehr = m1time,
       sleep_duration = dur_spt_sleep_min,
       sleep_efficiency = sleep_efficiency,
       sleep_onset = sleeponset_p5,
@@ -27,9 +28,9 @@ clean_data <- function(data_joined, region_lookup) {
     # remove all the ggir data execpt the columns that we're using
     select(
       -ig_gradient_enmo_0_24hr:-thresh_wear_loc, -contains("guider_"), -id,
-      measurementday, pa_volume, pa_intensity, pa_intensity_m16, sleep_duration,
-      sleep_efficiency, sleep_onset, sleep_wakeup, sleep_onset_time,
-      sleep_wakeup_time, sleep_regularity
+      measurementday, pa_volume, pa_intensity, pa_intensity_m16,
+      pa_mostactivehr, sleep_duration, sleep_efficiency, sleep_onset,
+      sleep_wakeup, sleep_onset_time, sleep_wakeup_time, sleep_regularity
     ) %>%
     # convert numeric variables to numeric
     mutate(across(c(
@@ -96,7 +97,13 @@ clean_data <- function(data_joined, region_lookup) {
       sleep_onset_time = chron(times = sleep_onset_time),
       sleep_wakeup_time = chron(times = sleep_wakeup_time)
     ) %>%
-    select(-measurementday)
+    select(-measurementday)  %>% 
+    # Fix up the most active time
+    mutate(
+      pa_mostactivehr = 
+        hour(lubridate::ymd_hms(pa_mostactivehr)) + 
+        minute(lubridate::ymd_hms(pa_mostactivehr)) / 60
+    )
   # read in sleep conditions harmonisation data
 
   sleep_refactors <-

### 2023-03-28 R/make_data_imp.R

@@ -21,9 +21,11 @@ make_data_imp <- function(data, n_imps = 3) {
   # Don't do imputation based on these vars:
 
   dont_imp <- c("filename", "calendar_date")
-  dont_use <- c("age_cat", "studyid", "participant_id", "country" , "region",
-                "accelerometer_wear_location", "accelerometer_model", "pa_intensity_m16",
-                "weekday_x")
+  dont_use <- c(
+    "age_cat", "studyid", "participant_id", "country", "region",
+    "accelerometer_wear_location", "accelerometer_model", "pa_intensity_m16", 
+    "pa_mostactivehr", "weekday_x"
+  )
   # Don't imp some vars, and disable some as predictors
   meth <- m0$method
   pred <- m0$predictorMatrix
@@ -36,6 +38,7 @@ make_data_imp <- function(data, n_imps = 3) {
     c("pa_volume",
       "pa_intensity",
       "pa_intensity_m16",
+      "pa_mostactivehr",
       "sleep_duration",
       "sleep_efficiency",
       "sleep_onset",

### 2023-03-28 _targets.R

@@ -102,6 +102,14 @@ list(
       moderator_term = "all",
       control_vars = c("bmi", "age", "sex"))
   ),
+    tar_target(
+    model_list_by_pa_mostactivehr,
+    make_model_list(
+      data_imp,
+      moderator = "pa_mostactivehr",
+      moderator_term = "5, 9, 14, 19",
+      control_vars = c("bmi", "age", "sex"))
+  ),
 
   tar_target(model_diagnostics, make_model_diagnostics(model_list_by_age)),
 
@@ -147,6 +155,10 @@ list(
     purdy_pictures_by_wear_location,
     produce_purdy_pictures(model_list_by_wear_location)
   ),
+    tar_target(
+    purdy_pictures_by_mostactivehr,
+    produce_purdy_pictures(model_list_by_pa_mostactivehr)
+  ),
 
   # Tables
   tar_target(model_tables_age, make_model_tables(model_list_by_age)),
@@ -158,6 +170,7 @@ list(
   tar_target(model_tables_region, make_model_tables(model_list_by_region)),
   tar_target(model_tables_daylight, make_model_tables(model_list_by_daylight)),
   tar_target(model_tables_wear_location, make_model_tables(model_list_by_wear_location)),
+  tar_target(model_tables_pa_mostactivehr, make_model_tables(model_list_by_pa_mostactivehr)),
 
   # Output results section
   tar_render(manuscript, "doc/manuscript.Rmd", output_format = c(

### 2023-03-30 doc/manuscript.Rmd
Integrate new figures into pipeline

@@
 
-```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
+```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume.
+The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column.
+The panels on the right shows the same relationships but by age continuously.
+These plots demonstrate exact turning points where the effects of PA volume change by age."}
 knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)

### 2023-03-30 R/produce_purdy_pictures.R

@@ -11,25 +11,33 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     model_list[[i]]$model_assets$effects
   })
 
-  tile_dat <- lapply(seq_len(length(model_list)), function(i){
-    model_list[[i]]$model_assets$pred_matrix
-  }) |> rbindlist()
-  tile_dat$group <- as.numeric(tile_dat$group)
-  tile_dat$includes_zero <- tile_dat$conf.low <= 0 & tile_dat$conf.high >= 0
-  # hide non-sig predictions
-  tile_dat$predicted[tile_dat$includes_zero == TRUE] <- 0
-  tile_dat$predicted[tile_dat$predicted >= 2] <- 2
-  tile_dat$predicted[tile_dat$predicted <= -2] <- -2
-  tile_dat <- tile_dat |> prepare_plot_data(paste_facet_labels)
-
   plot_dat <- data.table::rbindlist(dat_list) |>
     prepare_plot_data(paste_facet_labels)
 
+  moderator <- attr(model_list[[1]], "moderator")
+
+  # Im the moderator is age, then, retrieve granular age predictions
+
+  if(moderator == "age"){
+
+    tile_dat <- lapply(seq_len(length(model_list)), function(i){
+      model_list[[i]]$model_assets$pred_matrix
+    }) |> rbindlist()
+    tile_dat$group <- as.numeric(tile_dat$group)
+    tile_dat$includes_zero <- tile_dat$conf.low <= 0 & tile_dat$conf.high >= 0
+    # hide non-sig predictions
+    tile_dat$predicted[tile_dat$includes_zero == TRUE] <- 0
+    tile_dat$predicted[tile_dat$predicted >= 2] <- 2
+    tile_dat$predicted[tile_dat$predicted <= -2] <- -2
+    tile_dat <- tile_dat |> prepare_plot_data(paste_facet_labels)
+
+  }
+
+  # Plotting function
   require(ggplot2)
 
   p <- function(x_var, x_lab, rq){
     pdat <- plot_dat[x_name == x_var & RQ == rq]
-    tdat <- tile_dat[x_name == x_var & RQ == rq]
 
   conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
   fig <- ggplot(pdat, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
@@ -47,30 +55,43 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
[…]

### 2023-03-30 doc/manuscript.Rmd
Update figure labels

@@
 The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column.
-The panels on the right shows the same relationships but by age continuously.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero.
 These plots demonstrate exact turning points where the effects of PA volume change by age."}
@@
 
-```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
+```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity.
+The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero."}
 knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
+```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration.
+The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero."}
 knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
+```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency.
+The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero."}
 knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
+```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset.
+The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero."}
 knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
@@
 
-```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
+```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity.
+The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column.
+The panels on the right show the same relationships but by age continuously.
+The white band indicates predictions which were not significantly different from zero."}
 knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)

### 2023-04-04 doc/manuscript_data_imp.Rmd
Abstract the pipeline.

--- 2023-03-30 doc/manuscript.Rmd
@@
 ```{r load-targets, include=FALSE}
-tar_load(model_list_by_age)
+tar_load(model_list_by_age_data_imp)
 tar_load(data_clean)
 tar_load(purdy_pictures_by_age)
-tar_load(model_tables_age)
+tar_load(model_tables_age_data_imp)
 tar_load(demog_table)
@@
 papaja::apa_table(
-  model_tables_age$sleep$data,
-  caption = model_tables_age$sleep$caption,
-  note = model_tables_age$sleep$note,
-  col_spanners = model_tables_age$sleep$col_spanners,
+  model_tables_age_data_imp$sleep$data,
+  caption = model_tables_age_data_imp$sleep$caption,
+  note = model_tables_age_data_imp$sleep$note,
+  col_spanners = model_tables_age_data_imp$sleep$col_spanners,
   escape = FALSE,
@@
 papaja::apa_table(
-  model_tables_age$physical_activity$data,
-  caption = model_tables_age$physical_activity$caption,
-  note = model_tables_age$physical_activity$note,
-  col_spanners = model_tables_age$physical_activity$col_spanners,
+  model_tables_age_data_imp$physical_activity$data,
+  caption = model_tables_age_data_imp$physical_activity$caption,
+  note = model_tables_age_data_imp$physical_activity$note,
+  col_spanners = model_tables_age_data_imp$physical_activity$col_spanners,
   escape = FALSE,

### 2023-04-04 R/make_model_list.R

@@ -12,7 +12,8 @@ make_model_list <- function(
     moderator = "age",
     moderator_term = "11, 18, 35, 65",
     control_vars = c("ses", "sex", "bmi"),
-    ranef = "(1|studyid) + (1|participant_id)") {
+    ranef = "(1|studyid) + (1|participant_id)",
+    use_log = FALSE) {
   sleep_vars <- c(
     "scale_sleep_duration",
     "scale_sleep_efficiency",
@@ -23,9 +24,12 @@ make_model_list <- function(
   sleep_lag_vars <- paste0(sleep_vars, "_lag")
 
   pa_vars <- c(
-    "scale_pa_volume", "scale_pa_intensity",
-    "log_pa_volume"
+    "scale_pa_volume", "scale_pa_intensity"
   )
+
+  if (use_log) {
+    pa_vars[pa_vars == "scale_pa_volume"] <- "log_pa_volume"
+  }
 
   quadratic_pattern <- "{x} * {moderator} + I({x}^2) * {moderator}"
   make_quadratic <- function(x) glue::glue(quadratic_pattern)
@@ -66,7 +70,8 @@ make_model_list <- function(
         ranef = ranef,
         terms = c(
           paste0(
-            gsub(" .*", "", instructions[i, "predictors"]), "[-4:4 by = 0.1]"),
+            gsub(" .*", "", instructions[i, "predictors"]), "[-4:4 by = 0.1]"
+          ),
           glue::glue("{moderator} [{moderator_term}]")
         ),
         RQ = instructions[i, "RQ"]
@@ -80,5 +85,6 @@ make_model_list <- function(
   )
 
   names(out) <- instructions[, "model_name"]
+  attr(out, "use_log") <- use_log
   out
 }

### 2023-04-04 R/make_model_tables.R

@@ -6,7 +6,7 @@
 #' @param model_list
 #' @return list of tables
 #' @author Taren Sanders
-#' @test model_list <- model_list_by_wear_location
+#' @test model_list <- model_list_by_age_log
 #' @export
 make_model_tables <- function(model_list) {
   recode_var <- c("ses"= "SES" ,"bmi" = "BMI", "studyid" = "the fixed effects of study IDs")
@@ -30,6 +30,10 @@ make_model_tables <- function(model_list) {
     `Physical activity volume` = "scale_pa_volume",
     `Physical activity intensity` = "scale_pa_intensity"
   )
+
+  if(attr(model_list, "use_log")) {
+    pa_vars$`Physical activity volume` <- "log_pa_volume"
+  }
 
   sleep_table <- list()
 
@@ -91,6 +95,10 @@ make_model_tables <- function(model_list) {
 
   if(pa_conv_issue){
     pa_table$note <- paste0(pa_table$note, ". $^\\dagger$ value came from a pooled model where fewer than 75\\% of models converged.")
+  }
+
+  if(attr(model_list, "use_log")) {
+  pa_table$note <- paste0(pa_table$note, "PA volume was log-transformed.")
   }
 
   pa_table$col_spanners <- list(

### 2023-04-04 R/model_builder.R

@@ -44,7 +44,7 @@ fit_model <- function(..., data, max_iter = 1e6) {
       )
     )
     mod@call$control$optimizer <- unname(meth_tab[i, 1])
-    mod@call$control$optCtrl <- unlist(optCtrl)
+    mod@call$control$optCtrl <- unlist(opt_ctrl)
 
     if (is_conv(mod)) {
       conv <- TRUE

### 2023-04-04 R/produce_purdy_pictures.R

@@ -2,7 +2,7 @@
 #' @param model_list model_list
 #' @param paste_facet_labels character. String to paste to facet labels
 #' @param add_filename character. String to add to end of filenames
-#' @example  model_list <- model_list_by_age
+#' @example  model_list <- model_list_by_age_fixedef
 #' @details I check the proporiton of models that converged. If less then 75% of models converged
 #' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge # nolint
 
@@ -37,11 +37,19 @@ produce_purdy_pictures <- function(
   # Plotting function
   require(ggplot2)
 
-  p <- function(x_var, x_lab, rq) {
+  p <- function(x_var, x_lab, rq, debug = FALSE) {
+    if(debug) browser()
     pdat <- plot_dat[x_name == x_var & RQ == rq]
 
     conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
-    fig <- ggplot(pdat, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
+    fig <- ggplot(
+      pdat,
+      aes(
+        x = x, y = predicted,
+        ymin = conf.low, ymax = conf.high,
+        group = group, fill = group
+      )
+    ) +
       geom_line() +
       geom_ribbon(alpha = .5) +
       facet_grid(rows = vars(outcome), cols = vars(group)) +
@@ -103,8 +111,12 @@ produce_purdy_pictures <- function(
     outcome <- unique(gsub(" .*", "", pdat$outcome))
     if (length(outcome) > 1) stop("Outcome length is greater than 1")
 
-    filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}{add_filename}.jpg" |>
+    filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}{add_filename}.jpg" |> # nolint: line_length_linter.
       glue::glue()
+
+    if(attr(model_list, "use_log")) {
+      filename <- gsub("\\.jpg","_log.jpg", filename)
+    }
 
     if (outcome == "Sleep") {
       height <- 15
@@ -115,15 +127,30 @@ produce_purdy_pictures <- function(
[…]

### 2023-04-04 R/target_utils.R

@@ -1,0 +1,132 @@
+# ),
+# tar_target(
+#   purdy_pictures_by_daylight,
+#   produce_purdy_pictures(model_list_by_daylight, paste_facet_labels = " hours")
+# ),
+
+
+target_factory <-
+  function(moderators = c("age", "bmi"),
+           data = "data_imp") {
+    out <-
+      lapply(moderators, function(x)
+        create_analytic_targets(x, data = data))
+    # Generate model_names based on data object
+    model_names <- paste0("model_list_by_", moderators)
+    model_names_data <- paste0(model_names,"_", data)
+
+    # model_tables
+    model_table_names <- paste0("model_tables_", moderators)
+    model_table_names_data <-  paste0(model_table_names,"_", data)
+
+
+    # Create a manuscript using those names
+    manuscript_path <- "doc/manuscript.Rmd"
+    skeleton_manuscript <- readLines(manuscript_path)
+
+    names_to_change <- c(model_names, model_table_names)
+    new_names <- c(model_names_data, model_table_names_data)
+
+    for(i in seq_along(names_to_change)){
+    skeleton_manuscript <- gsub(names_to_change[i], new_names[i], skeleton_manuscript)
+    }
+
+    manuscript_path_new <- gsub("\\.Rmd",glue::glue("_{data}.Rmd"),manuscript_path)
+    write(skeleton_manuscript, manuscript_path_new)
+
+    append(out,
+           list(
+             tar_target_raw(
+               name = glue::glue("model_diagnostics_{data}"),
+               command = parse(
+                 text = glue::glue(
+                   "make_model_diagnostics({paste(model_names_data, collapse = ',')})"
+                 )
+               ),
+               deployment = "main"
+             ),
+             tar_render_raw(
+               name = glue::glue("manuscript_{data}"),
+               manuscript_path_new,
+               render_arguments = quote(list(
+                 output_format = c("papaja::apa6_docx",
+                                   "papaja::apa6_pdf")
+               ))
+             )
+           ))
+
+  }
+
+create_analytic_targets <- function(moderator = "age", data = "data_imp"){
+  # Detine control vars
+  control_vars <- c("ses", "age", "sex", "bmi")
+  control_vars <- control_vars[!control_vars == moderator]
+
+  # Define moderator term
+  i_df <-
+    data.frame(
[…]

### 2023-04-04 _targets.R

@@ -46,9 +46,10 @@ list(
   tar_target(region_lookup, make_region_lookup()),
   tar_target(demog_table, make_demog_table(participant_summary)),
   tar_target(
-    data_imp_raw, make_data_imp(data_holdout, n_imps = 3), deployment = "main",
+    data_imp_raw, make_data_imp(data_holdout, n_imps = 3),
+    deployment = "main",
     format = format, repository = repository
-    ),
+  ),
   tar_target(data_imp, format_imp_vars(data_imp_raw)),
   tar_target(imputation_checks, check_imps(data_imp),
     format = "file",
@@ -59,203 +60,19 @@ list(
   ##                          MODELLING                          ##
   #################################################################
 
-  tar_target(
-    model_list_by_age,
-    make_model_list(data_imp, moderator = "age",
-    moderator_term = "11, 18, 35, 65")
-  ),
-  tar_target(
-    model_list_by_bmi,
-    make_model_list(
-      data_imp,
-      moderator = "bmi",
-      moderator_term = "18, 22, 25, 30",
-      control_vars = c("ses", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_ses,
-    make_model_list(
-      data_imp,
-      moderator = "ses",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_sex,
-    make_model_list(
-      data_imp,
-      moderator = "sex",
-      moderator_term = "all",
-      control_vars = c("ses", "age", "bmi")
-    )
-  ),
-  tar_target(
-    model_list_by_weekday,
-    make_model_list(
-      data_imp,
-      moderator = "weekday_x",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_season,
-    make_model_list(
-      data_imp,
-      moderator = "season",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_region,
-    make_model_list(
-      data_imp,
-      moderator = "region",
-      moderator_term = "all",
-      control_vars = c("ses", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_daylight,
-    make_model_list(
-      data_imp,
-      moderator = "daylight_hours",
[…]

### 2023-04-04 doc/manuscript.Rmd
Abstract figure names in manuscript

@@
 These plots demonstrate exact turning points where the effects of PA volume change by age."}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_pa_volume), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_pa_intensity), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age)$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-04 doc/manuscript_data_imp.Rmd
Abstract figure names in manuscript

@@
 tar_load(data_clean)
-tar_load(purdy_pictures_by_age)
+tar_load(purdy_pictures_by_age_data_imp)
 tar_load(model_tables_age_data_imp)
@@
 These plots demonstrate exact turning points where the effects of PA volume change by age."}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_pa_volume), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_pa_intensity), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-04 R/produce_purdy_pictures.R

@@ -2,7 +2,7 @@
 #' @param model_list model_list
 #' @param paste_facet_labels character. String to paste to facet labels
 #' @param add_filename character. String to add to end of filenames
-#' @example  model_list <- model_list_by_age_fixedef
+#' @example  model_list <- model_list_by_age_data_imp
 #' @details I check the proporiton of models that converged. If less then 75% of models converged
 #' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge # nolint
 
@@ -125,6 +125,7 @@ produce_purdy_pictures <- function(
     }
 
     ggsave(filename, plot = fig, height = height, width = width + 5, units = "cm", dpi = dpi)
+    return(filename)
   }
 
   # Create an input data.frame
@@ -147,12 +148,15 @@ produce_purdy_pictures <- function(
     df$y[row] <- "PA volume (log)"
   }
 
-  # Produce the plots
-  for (row in seq_len(nrow(df))) {
-    p(df$x[row], df$y[row], df$RQ[row])
-  }
 
-  NULL
+  # produce the plots
+  out <- lapply(seq_len(nrow(df)), function(row){
+    p(df$x[row], df$y[row], df$RQ[row])
+  })
+
+  names(out) <- paste0("predictor_", df$x)
+  out
+
 }
 
 prepare_plot_data <- function(plot_dat, paste_facet_labels) {

### 2023-04-04 R/target_utils.R

@@ -19,13 +19,16 @@ target_factory <-
     model_table_names <- paste0("model_tables_", moderators)
     model_table_names_data <-  paste0(model_table_names,"_", data)
 
+    # model_figures
+    model_figure_names <- paste0("purdy_pictures_by_", moderators)
+    model_figure_names_data <- paste0(model_figure_names, "_", data)
 
     # Create a manuscript using those names
     manuscript_path <- "doc/manuscript.Rmd"
     skeleton_manuscript <- readLines(manuscript_path)
 
-    names_to_change <- c(model_names, model_table_names)
-    new_names <- c(model_names_data, model_table_names_data)
+    names_to_change <- c(model_names, model_table_names, model_figure_names)
+    new_names <- c(model_names_data, model_table_names_data, model_figure_names_data)
 
     for(i in seq_along(names_to_change)){
     skeleton_manuscript <- gsub(names_to_change[i], new_names[i], skeleton_manuscript)
@@ -110,7 +113,8 @@ create_analytic_targets <- function(moderator = "age", data = "data_imp"){
       command = parse(
         text =
           glue::glue(
-            "produce_purdy_pictures(model_list_by_{moderator}_{data}, paste_facet_labels = \"{facet_label}\")
+            "produce_purdy_pictures(model_list_by_{moderator}_{data}, paste_facet_labels = \"{facet_label}\",
+            add_filename = \"_{data}\")
 # )"
           )
       )

### 2023-04-04 doc/manuscript_data_imp_log.Rmd
Abstract tables and figures

--- 2023-03-30 doc/manuscript.Rmd
@@
 ```{r load-targets, include=FALSE}
-tar_load(model_list_by_age)
+tar_load(model_list_by_age_data_imp_log)
 tar_load(data_clean)
-tar_load(purdy_pictures_by_age)
-tar_load(model_tables_age)
+tar_load(purdy_pictures_by_age_data_imp_log)
+tar_load(model_tables_age_data_imp_log)
 tar_load(demog_table)
@@
 papaja::apa_table(
-  model_tables_age$sleep$data,
-  caption = model_tables_age$sleep$caption,
-  note = model_tables_age$sleep$note,
-  col_spanners = model_tables_age$sleep$col_spanners,
+  model_tables_age_data_imp_log$sleep$data,
+  caption = model_tables_age_data_imp_log$sleep$caption,
+  note = model_tables_age_data_imp_log$sleep$note,
+  col_spanners = model_tables_age_data_imp_log$sleep$col_spanners,
   escape = FALSE,
@@
 These plots demonstrate exact turning points where the effects of PA volume change by age."}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_pa_volume), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_pa_intensity), error = FALSE)
 ```
@@
 papaja::apa_table(
-  model_tables_age$physical_activity$data,
-  caption = model_tables_age$physical_activity$caption,
-  note = model_tables_age$physical_activity$note,
-  col_spanners = model_tables_age$physical_activity$col_spanners,
+  model_tables_age_data_imp_log$physical_activity$data,
+  caption = model_tables_age_data_imp_log$physical_activity$caption,
+  note = model_tables_age_data_imp_log$physical_activity$note,
+  col_spanners = model_tables_age_data_imp_log$physical_activity$col_spanners,
   escape = FALSE,
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-04 doc/multiverse_data_imp_log.Rmd
Abstract tables and figures

--- 2023-03-28 doc/multiverse.Rmd
@@
 ```{r load-targets, include=FALSE}
-model_list_by_age_fixedef <- tar_read(model_list_by_age_fixedef)
 tar_load(data_clean)
-tar_load(purdy_pictures_by_age_fixedef)
-model_tables <- tar_read(model_tables_fixedef)
 pretty <- function(x) format(x, big.mark = ",")
@@
 
-In this document we show the results using another analytic technique. Namely treating study ID as a fixed effect. This is what we wrote in the protocol originally.
-
-## The effects of physical activity volume on sleep
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
-
-```{r sleep-outcomes}
-papaja::apa_table(
-  model_tables$sleep$data,
-  caption = model_tables$sleep$caption,
-  note = model_tables$sleep$note,
-  col_spanners = model_tables$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age_fixedef.jpg"), error = FALSE)
-```
-
-## The effects of physical activity intensity on sleep
-
-We estimated how physical activity intensity affects sleep across different age groups
-We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
-
-```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age_fixedef.jpg"), error = FALSE)
-```
-
-## The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by age
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
-
-```{r pa-outcomes}
-papaja::apa_table(
-  model_tables$physical_activity$data,
-  caption = model_tables$physical_activity$caption,
-  note = model_tables$physical_activity$note,
-  col_spanners = model_tables$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
-```
-
-## The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
-
-```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
-```
-
-## The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by age
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
-
-```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
-```
-
-## The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
-
-```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
-```
+In this document we show the relationship between sleep and physical activity by the moderators that were pre-registered in our protocol.
 
@@
 moderator_df <- data.frame(
-  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
-  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
-  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
+  moderator = c("bmi", "ses", "sex", "weekday_x", "season", "region", "daylight_hours", "accelerometer_wear_location", "pa_mostactivehr"),
+  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
+  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
 )
@@
 
-\clearpage
-
-## BMI
-
-```{r}
-tar_load(model_tables_bmi)
-```
-
-### The effects of physical activity volume on sleep by BMI
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)
-
-```{r sleep-outcomes-by-bmi}
-papaja::apa_table(
-  model_tables_bmi$sleep$data,
-  caption = model_tables_bmi$sleep$caption,
-  note = model_tables_bmi$sleep$note,
-  col_spanners = model_tables_bmi$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Bmi.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by BMI
-
-We estimated how physical activity intensity affects sleep across BMI
-We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).
-
-```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Bmi.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by BMI
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
-
-```{r pa-outcomes-by-bmi}
-papaja::apa_table(
-  model_tables_bmi$physical_activity$data,
-  caption = model_tables_bmi$physical_activity$caption,
-  note = model_tables_bmi$physical_activity$note,
-  col_spanners = model_tables_bmi$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by BMI.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-bmi).
-
-```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by BMI
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).
-
-```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by BMI.
-Results are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).
-
-```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
-```
-\clearpage
-
-## SES
-
-```{r}
-tar_load(model_tables_ses)
-```
-
-### The effects of physical activity volume on sleep by SES
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)
-
-```{r sleep-outcomes-by-ses}
-papaja::apa_table(
-  model_tables_ses$sleep$data,
-  caption = model_tables_ses$sleep$caption,
-  note = model_tables_ses$sleep$note,
-  col_spanners = model_tables_ses$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Ses.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by SES
-
-We estimated how physical activity intensity affects sleep across SES
-We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).
-
-```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Ses.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by SES
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
-
-```{r pa-outcomes-by-ses}
-papaja::apa_table(
-  model_tables_ses$physical_activity$data,
-  caption = model_tables_ses$physical_activity$caption,
-  note = model_tables_ses$physical_activity$note,
-  col_spanners = model_tables_ses$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by SES.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ses).
-
-```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by SES
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).
-
-```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by SES.
-Results are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).
-
-```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
-```
-\clearpage
-
-## sex
-
-```{r}
-tar_load(model_tables_sex)
-```
-
-### The effects of physical activity volume on sleep by sex
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)
-
-```{r sleep-outcomes-by-sex}
-papaja::apa_table(
-  model_tables_sex$sleep$data,
-  caption = model_tables_sex$sleep$caption,
-  note = model_tables_sex$sleep$note,
-  col_spanners = model_tables_sex$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Sex.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by sex
-
-We estimated how physical activity intensity affects sleep across sex
-We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).
-
-```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Sex.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by sex
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
-
-```{r pa-outcomes-by-sex}
-papaja::apa_table(
-  model_tables_sex$physical_activity$data,
-  caption = model_tables_sex$physical_activity$caption,
-  note = model_tables_sex$physical_activity$note,
-  col_spanners = model_tables_sex$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by sex.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-sex).
-
-```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by sex
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).
-
-```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by sex.
-Results are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).
-
-```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
-```
-\clearpage
-
-## weekday
-
-```{r}
-tar_load(model_tables_weekday)
-```
-
-### The effects of physical activity volume on sleep by weekday
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)
-
-```{r sleep-outcomes-by-weekday}
-papaja::apa_table(
-  model_tables_weekday$sleep$data,
-  caption = model_tables_weekday$sleep$caption,
-  note = model_tables_weekday$sleep$note,
-  col_spanners = model_tables_weekday$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Weekday_x.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by weekday
-
-We estimated how physical activity intensity affects sleep across weekday
-We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).
-
-```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Weekday_x.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by weekday
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
-
-```{r pa-outcomes-by-weekday}
-papaja::apa_table(
-  model_tables_weekday$physical_activity$data,
-  caption = model_tables_weekday$physical_activity$caption,
-  note = model_tables_weekday$physical_activity$note,
-  col_spanners = model_tables_weekday$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by weekday.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-weekday).
-
-```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by weekday
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).
-
-```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by weekday.
-Results are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).
-
-```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
-```
-\clearpage
-
-## season
-
-```{r}
-tar_load(model_tables_season)
-```
-
-### The effects of physical activity volume on sleep by season
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by season, and the results are presented in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-volume-fig-by-season)
-
-```{r sleep-outcomes-by-season}
-papaja::apa_table(
-  model_tables_season$sleep$data,
-  caption = model_tables_season$sleep$caption,
-  note = model_tables_season$sleep$note,
-  col_spanners = model_tables_season$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-season, fig.cap = "Sleep metrics on Physical activity volume by season"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Season.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by season
-
-We estimated how physical activity intensity affects sleep across season
-We present the results in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-intensity-fig-by-season).
-
-```{r sleep-by-intensity-fig-by-season, fig.cap = "Sleep metrics on Physical activity intensity moderated by season"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Season.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by season
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
-
-```{r pa-outcomes-by-season}
-papaja::apa_table(
-  model_tables_season$physical_activity$data,
-  caption = model_tables_season$physical_activity$caption,
-  note = model_tables_season$physical_activity$note,
-  col_spanners = model_tables_season$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by season.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-season).
-
-```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by season
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).
-
-```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by season.
-Results are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).
-
-```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
-```
-\clearpage
-
-## region
-
-```{r}
-tar_load(model_tables_region)
-```
-
-### The effects of physical activity volume on sleep by region
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by region, and the results are presented in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-volume-fig-by-region)
-
-```{r sleep-outcomes-by-region}
-papaja::apa_table(
-  model_tables_region$sleep$data,
-  caption = model_tables_region$sleep$caption,
-  note = model_tables_region$sleep$note,
-  col_spanners = model_tables_region$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-region, fig.cap = "Sleep metrics on Physical activity volume by region"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Region.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by region
-
-We estimated how physical activity intensity affects sleep across region
-We present the results in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-intensity-fig-by-region).
-
-```{r sleep-by-intensity-fig-by-region, fig.cap = "Sleep metrics on Physical activity intensity moderated by region"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Region.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by region
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
-
-```{r pa-outcomes-by-region}
-papaja::apa_table(
-  model_tables_region$physical_activity$data,
-  caption = model_tables_region$physical_activity$caption,
-  note = model_tables_region$physical_activity$note,
-  col_spanners = model_tables_region$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by region.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-region).
-
-```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by region
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).
-
-```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by region.
-Results are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).
-
-```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
-```
-\clearpage
-
-## daylight hours
-
-```{r}
-tar_load(model_tables_daylight)
-```
-
-### The effects of physical activity volume on sleep by daylight hours
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight)
-
-```{r sleep-outcomes-by-daylight}
-papaja::apa_table(
-  model_tables_daylight$sleep$data,
-  caption = model_tables_daylight$sleep$caption,
-  note = model_tables_daylight$sleep$note,
-  col_spanners = model_tables_daylight$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Daylight_hours.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by daylight hours
-
-We estimated how physical activity intensity affects sleep across daylight hours
-We present the results in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight).
-
-```{r sleep-by-intensity-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Daylight_hours.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by daylight hours
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).
-
-```{r pa-outcomes-by-daylight}
-papaja::apa_table(
-  model_tables_daylight$physical_activity$data,
-  caption = model_tables_daylight$physical_activity$caption,
-  note = model_tables_daylight$physical_activity$note,
-  col_spanners = model_tables_daylight$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by daylight hours.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight).
-
-```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by daylight hours
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight).
-
-```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by daylight hours.
-Results are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).
-
-```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
-```
-\clearpage
-
-## wear location
-
-```{r}
-tar_load(model_tables_wear_location)
-```
-
-### The effects of physical activity volume on sleep by wear location
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)
-
-```{r sleep-outcomes-by-wear-location}
-papaja::apa_table(
-  model_tables_wear_location$sleep$data,
-  caption = model_tables_wear_location$sleep$caption,
-  note = model_tables_wear_location$sleep$note,
-  col_spanners = model_tables_wear_location$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by wear location
-
-We estimated how physical activity intensity affects sleep across wear location
-We present the results in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).
-
-```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by wear location
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).
-
-```{r pa-outcomes-by-wear-location}
-papaja::apa_table(
-  model_tables_wear_location$physical_activity$data,
-  caption = model_tables_wear_location$physical_activity$caption,
-  note = model_tables_wear_location$physical_activity$note,
-  col_spanners = model_tables_wear_location$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).
-
-```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by wear location
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-wear-location).
-
-```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by wear location.
-Results are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
-
-```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
-```
-
 <!-- Finish auto-generated chunks go here: -->

### 2023-04-04 R/make_model_list.R

@@ -3,33 +3,46 @@
 #' .. content for \details{} ..
 #'
 #' @title
-#' @param data_imp
+#' @param imp_data <- tar_read(data_imp_log)
 #' @return
 #' @author conig
+#' @test data
 #' @export
+#'
 make_model_list <- function(
-    data_imp,
+    imp_data,
     moderator = "age",
     moderator_term = "11, 18, 35, 65",
     control_vars = c("ses", "sex", "bmi"),
-    ranef = "(1|studyid) + (1|participant_id)",
-    use_log = FALSE) {
-  sleep_vars <- c(
-    "scale_sleep_duration",
-    "scale_sleep_efficiency",
-    "scale_sleep_onset",
-    "scale_sleep_regularity"
-  )
+    ranef = "(1|studyid) + (1|participant_id)") {
 
-  sleep_lag_vars <- paste0(sleep_vars, "_lag")
+  # Declare base variables to analyse
+  sleep_vars <- c(
+    "sleep_duration",
+    "sleep_efficiency",
+    "sleep_onset",
+    "sleep_regularity"
+  )
 
   pa_vars <- c(
-    "scale_pa_volume", "scale_pa_intensity"
+    "pa_volume", "pa_intensity"
   )
 
-  if (use_log) {
-    pa_vars[pa_vars == "scale_pa_volume"] <- "log_pa_volume"
-  }
+  # Find transformed variables for use (log or scaled)
+  data_names <- names(imp_data$data)
+
+  sleep_vars <- sapply(sleep_vars, function(x){
+    grep(glue::glue("(scale|log)_{x}$"), data_names, value = TRUE)
+  })
+  names(sleep_vars) <- display_names(sleep_vars)
+
+  pa_vars <- sapply(pa_vars, function(x){
+    grep(glue::glue("(scale|log)_{x}$"), data_names, value = TRUE)
+  })
+  names(pa_vars) <- display_names(pa_vars)
+
+
+  sleep_lag_vars <- paste0(sleep_vars, "_lag")
 
   quadratic_pattern <- "{x} * {moderator} + I({x}^2) * {moderator}"
   make_quadratic <- function(x) glue::glue(quadratic_pattern)
@@ -61,7 +74,7 @@ make_model_list <- function(
     seq_len(length(instructions[, 1])),
     FUN = function(i) {
       model <- model_builder(
-        data_imp,
+        imp_data,
         outcome = instructions[i, "outcome"],
[…]

### 2023-04-04 R/make_model_tables.R

@@ -6,7 +6,7 @@
 #' @param model_list
 #' @return list of tables
 #' @author Taren Sanders
-#' @test model_list <- model_list_by_age_log
+#' @test model_list <- model_list_by_bmi_data_imp_log
 #' @export
 make_model_tables <- function(model_list) {
   recode_var <- c("ses"= "SES" ,"bmi" = "BMI", "studyid" = "the fixed effects of study IDs")
@@ -19,31 +19,20 @@ make_model_tables <- function(model_list) {
 
   note <- paste("Adjusted for", control_vars)
 
-  sleep_vars <- list(
-    `Sleep duration` = "scale_sleep_duration",
-    `Sleep efficency` = "scale_sleep_efficiency",
-    `Sleep onset` = "scale_sleep_onset",
-    `Sleep regularity` = "scale_sleep_regularity"
-  )
+  vars <- attr(model_list, "vars")
 
-  pa_vars <- list(
-    `Physical activity volume` = "scale_pa_volume",
-    `Physical activity intensity` = "scale_pa_intensity"
-  )
-
-  if(attr(model_list, "use_log")) {
-    pa_vars$`Physical activity volume` <- "log_pa_volume"
-  }
+  sleep_vars <- vars$sleep_vars
+  pa_vars <- vars$pa_vars
 
   sleep_table <- list()
 
   sleep_table$data <- lapply(sleep_vars, function(sleep) {
     model1_name <- paste(
-      sleep, "by", pa_vars["Physical activity volume"],
+      sleep, "by", pa_vars[[1]],
       collapse = " "
     )
     model2_name <- paste(
-      sleep, "by", pa_vars[["Physical activity intensity"]],
+      sleep, "by", pa_vars[[2]],
       collapse = " "
     )
 
@@ -65,18 +54,19 @@ make_model_tables <- function(model_list) {
   }
 
   sleep_table$col_spanners <- list(
-    "Physical Activity Volume" = c(2, 5),
-    "Physical Activity Intensity" = c(6, 9)
+    c(2, 5),
+    c(6, 9)
   )
+  names(sleep_table$col_spanners) <- names(pa_vars)
 
   pa_table <- list()
   pa_table$data <- lapply(sleep_vars, function(sleep) {
     model1_name <- paste(
-      pa_vars["Physical activity volume"], "by", paste0(sleep, "_lag"),
+      pa_vars[[1]], "by", paste0(sleep, "_lag"),
       collapse = " "
     )
[…]

### 2023-04-04 R/make_data_imp.R
Abstract tables and figures

@@ -107,9 +107,16 @@ make_data_imp <- function(data, n_imps = 3) {
 
 }
 
-format_imp_vars <- function(data_imp_raw){
+format_imp_vars <- function(data_imp_raw, use_log = FALSE){
 require(mice)
    # include data transformations
+
+ log_df <- data.frame(
+    var = c("pa_volume"),
+    new_name = c("log_pa_volume"),
+    method = "log"
+  )
+
   sleep_vars <- c(
     "sleep_duration",
     "sleep_efficiency",
@@ -118,17 +125,22 @@ require(mice)
   )
 
   var_to_transf <-
-    c(
-      "pa_volume", # For log transform
-      sleep_vars,
+    c(sleep_vars,
       "pa_volume",
       "pa_intensity",
       "pa_intensity_m16",
       paste0(sleep_vars, "_lag")
     )
 
-  new_name <- c("log_pa_volume", paste0("scale_", var_to_transf[-1]))
+  new_name <- c(paste0("scale_", var_to_transf))
   transf_fn <- gsub("_.*", "", new_name)
+
+  if(use_log) {
+    for(i in seq_len(nrow(log_df))) {
+      new_name[var_to_transf == log_df$var[i]] <- log_df$new_name[i]
+      transf_fn[var_to_transf == log_df$var[i]] <- log_df$method[i]
+    }
+  }
 
   imp_list <- data.table(complete(data_imp_raw, action = "long",
    include = TRUE))
@@ -141,3 +153,4 @@ require(mice)
   as.mids(imp_list)
 
 }
+

### 2023-04-04 R/model_builder.R

@@ -198,6 +198,7 @@ model_builder <-
 #' @example model = rq1_example_model, terms = c("pa_intensity", "pa_volume")
 
 get_effects <- function(model, moderator, terms, outcome, conv, RQ, ...) {
+
   effects <-
     lapply(seq_len(length(model)), function(i) {
       suppressMessages(ggeffects::ggpredict(model[[i]], terms = terms, ...))

### 2023-04-04 R/produce_purdy_pictures.R

@@ -2,13 +2,14 @@
 #' @param model_list model_list
 #' @param paste_facet_labels character. String to paste to facet labels
 #' @param add_filename character. String to add to end of filenames
-#' @example  model_list <- model_list_by_age_data_imp
+#' @example  model_list <- model_list_by_age_data_imp_log
 #' @details I check the proporiton of models that converged. If less then 75% of models converged
 #' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge # nolint
 
 produce_purdy_pictures <- function(
     model_list,
     paste_facet_labels = "", add_filename = "") {
+
 
   dat_list <- lapply(seq_len(length(model_list)), function(i) {
     model_list[[i]]$model_assets$effects
@@ -37,8 +38,8 @@ produce_purdy_pictures <- function(
   # Plotting function
   require(ggplot2)
 
-  p <- function(x_var, x_lab, rq, debug = FALSE) {
-    if(debug) browser()
+  p <- function(x_var, x_lab, rq) {
+
     pdat <- plot_dat[x_name == x_var & RQ == rq]
 
     conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
@@ -78,10 +79,6 @@ produce_purdy_pictures <- function(
         gsub("_", " ", x = _) |>
         stringr::str_to_sentence() |>
         gsub("Pa", "PA", x = _)
-      gsub("\\[.*", "", unique(tile_dat$x_name)) |>
-        gsub("_", " ", x = _) |>
-        stringr::str_to_sentence() |>
-        gsub("Pa", "PA", x = _)
 
       fig <- fig + theme(strip.text.y = element_blank())
       tdat$facet_label <- "Age continuous"
@@ -109,14 +106,11 @@ produce_purdy_pictures <- function(
     }
 
     outcome <- unique(gsub(" .*", "", pdat$outcome))
+    outcome <- outcome[outcome != "Log"]
     if (length(outcome) > 1) stop("Outcome length is greater than 1")
 
     filename <- "Figures/{outcome} on {x_var} by {stringr::str_to_sentence(unique(plot_dat$moderator))}{add_filename}.jpg" |> # nolint: line_length_linter.
       glue::glue()
-
[…]

### 2023-04-04 R/utils.R

@@ -90,3 +90,18 @@ get_season <- function(date, lat){
 
 find_max  <- function(x) {names(which.max(table(x)))}
 
+display_names <- function(x){
+
+  is_scale <- grepl("^scale",x)
+  is_log <- grepl("^log",x)
+
+  out <- gsub("(scale_|log_)", "", x) |>
+    gsub("_", " ", x = _) |>
+    gsub("pa","physical activity", x = _) |>
+    stringr::str_to_sentence()
+
+  out[is_scale] <- paste(out[is_scale], "(z)")
+  out[is_log] <- paste(out[is_log], "(ln)")
+  out
+
+}

### 2023-04-04 _targets.R

@@ -24,6 +24,19 @@ if (Sys.getenv("GCS_AUTH_FILE") != "") {
   repository <- targets::tar_option_get("repository")
 }
 
+moderator_variables <- c(
+  "age",
+  "bmi",
+  "ses",
+  "sex",
+  "weekday_x",
+  "season",
+  "region",
+  "daylight_hours",
+  "accelerometer_wear_location",
+  "pa_mostactivehr"
+)
+
 # Pipeline
 list(
   ##################################################################
@@ -51,23 +64,25 @@ list(
     format = format, repository = repository
   ),
   tar_target(data_imp, format_imp_vars(data_imp_raw)),
+  tar_target(data_imp_log, format_imp_vars(data_imp_raw, use_log = TRUE)),
+
   tar_target(imputation_checks, check_imps(data_imp),
     format = "file",
     priority = 1
   ),
 
-  #################################################################
-  ##                          MODELLING                          ##
-  #################################################################
-
-  target_factory(moderator = c("age", "bmi", "ses",
-                               "sex", "weekday_x","season",
-                               "region", "daylight_hours", "accelerometer_wear_location",
-                               "pa_mostactivehr"), data = "data_imp"),
-
   ##################################################################
   ##                        ASSET CREATION                        ##
   ##################################################################
 
-  tar_target(explore_img, make_explore_img_list(data_holdout))
+  tar_target(explore_img, make_explore_img_list(data_holdout)),
+
+  #################################################################
+  ##                          MODELLING                          ##
+  #################################################################
+
+  target_factory(moderators = c(moderator_variables), data = "data_imp"),
+  target_factory(moderators = moderator_variables, data = "data_imp_log")
+
+
 )

### 2023-04-12 doc/multiverse.Rmd
WIP: use tar_map
Could facet_labels, filename go in model_assets instead?

@@
 tar_read(model_diagnostics) |>
-  papaja::apa_table(caption = "Model diagnostics", escape = FALSE,
-                    longtable = TRUE)
+  papaja::apa_table(
+    caption = "Model diagnostics", escape = FALSE,
+    longtable = TRUE
+  )
 ```
@@
   moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
-  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
+  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Acc_wear_loc", "Pa_mostactivehr")
 )
 
-lapply(seq_len(nrow(moderator_df)), function(r){
-
+lapply(seq_len(nrow(moderator_df)), function(r) {
   moderator <- moderator_df$moderator[r]
-  moderator_fig <- gsub("_","-",moderator)
+  moderator_fig <- gsub("_", "-", moderator)
   moderator_formal <- moderator_df$moderator_formal[r]
@@
   glue::glue(pattern, .open = "_::", .close = "::_")
-
-}) |> paste(collapse = "\n") |> clipr::write_clip()
-
+}) |>
+  paste(collapse = "\n") |>
+  clipr::write_clip()
 ```
@@
 ```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Acc_wear_loc.jpg"), error = FALSE)
 ```
@@
 ```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Acc_wear_loc.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Acc_wear_loc.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Acc_wear_loc.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Acc_wear_loc.jpg"), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
+knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Acc_wear_loc.jpg"), error = FALSE)
 ```

### 2023-04-12 R/clean_data.R

@@ -27,7 +27,8 @@ clean_data <- function(data_joined, region_lookup) {
       sleep_wakeup = wakeup_p5,
       sleep_onset_time = sleeponset_ts_p5,
       sleep_wakeup_time = wakeup_ts_p5,
-      sleep_regularity = sleep_regularity_index
+      sleep_regularity = sleep_regularity_index,
+      acc_wear_loc = accelerometer_wear_location
     ) %>%
     # remove all the ggir data execpt the columns that we're using
     select(
@@ -48,7 +49,7 @@ clean_data <- function(data_joined, region_lookup) {
     mutate(across(c(
       studyid, sex, ethnicity,
       ses, sleep_medications, sleep_conditions,
-      country, season, accelerometer_wear_location,
+      country, season, acc_wear_loc,
       weekday_x, accelerometer_model
     ), as.factor)) %>%
     # convert calendar_date to date

### 2023-04-12 R/make_data_imp.R

@@ -24,7 +24,7 @@ make_data_imp <- function(data, n_imps = 3) {
   dont_imp <- c("filename", "calendar_date")
   dont_use <- c(
     "age_cat", "studyid", "participant_id", "country", "region",
-    "accelerometer_wear_location", "accelerometer_model", "pa_intensity_m16",
+    "acc_wear_loc", "accelerometer_model", "pa_intensity_m16",
     "pa_mostactivehr", "weekday_x"
   )
   # Don't imp some vars, and disable some as predictors

### 2023-04-12 _targets.R

@@ -24,6 +24,31 @@ if (Sys.getenv("GCS_AUTH_FILE") != "") {
   repository <- targets::tar_option_get("repository")
 }
 
+# Model parameters
+default_pa <- c("log_pa_volume", "scale_pa_intensity")
+default_sleep <- c(
+  "scale_sleep_duration", "scale_sleep_efficiency", "scale_sleep_onset",
+  "scale_sleep_regularity"
+)
+default_ranef <- "(1|studyid) + (1|participant_id)"
+
+# nolint start styler: off
+models <- dplyr::tribble(
+  ~model_name,          ~moderator,        ~moderator_term,  ~pa_vars,          ~sleep_vars,   ~labels,  ~ranef,
+  "by_age",             "age",             "11, 18, 35, 65", default_pa,        default_sleep, " years", default_ranef,
+  "by_bmi",             "bmi",             "18, 22, 25, 30", default_pa,        default_sleep, "",       default_ranef,
+  "by_ses",             "ses",             "all",            default_pa,        default_sleep, "",       default_ranef,
+  "by_weekday",         "weekday_x",       "all",            default_pa,        default_sleep, "",       default_ranef,
+  "by_season",          "season",          "all",            default_pa,        default_sleep, "",       default_ranef,
+  "by_region",          "region",          "all",            default_pa,        default_sleep, "",       default_ranef,
+  "by_daylight",        "daylight_hours",  "8, 10, 12, 14",  default_pa,        default_sleep, " hours", default_ranef,
+  "by_wear_location",   "acc_wear_loc",    "all",            default_pa,        default_sleep, "",       default_ranef,
+  "by_pa_mostactivehr", "pa_mostactivehr", "5, 9, 14, 19",   default_pa,        default_sleep, "",       default_ranef,
+  "by_age_fixedef",     "age",             "11, 18, 35, 65", default_pa,        default_sleep, " years", "(1 | measurement_day) + (1 | participant_id)",
+  "by_age_nolog",       "age",             "11, 18, 35, 65", "scale_pa_volume", default_sleep, "",       default_ranef
+)
+# nolint end styler: on
+
 # Pipeline
 list(
   ##################################################################
@@ -46,9 +71,10 @@ list(
   tar_target(region_lookup, make_region_lookup()),
   tar_target(demog_table, make_demog_table(participant_summary)),
   tar_target(
-    data_imp, make_data_imp(data_holdout, n_imps = 3), deployment = "main",
+    data_imp, make_data_imp(data_holdout, n_imps = 3),
[…]

### 2023-04-13 doc/manuscript.Rmd
Automate docs
Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

Should prevent the cases where the images are being renamed
and not matching the files.

--- 2023-03-30 doc/manuscript.Rmd
@@
 ```{r load-targets, include=FALSE}
-tar_load(model_list_by_age)
 tar_load(data_clean)
 tar_load(purdy_pictures_by_age)
-tar_load(model_tables_age)
+tar_load(model_tables_by_age)
 tar_load(demog_table)
@@
 n_participants <- length(unique(data_clean$participant_id))
-weekday_table <- (data_clean$weekday_x) |> table()
+weekday_table <- (data_clean$weekday) |> table()
 weekday <- chisq.test(weekday_table)
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
@@
 papaja::apa_table(
-  model_tables_age$sleep$data,
-  caption = model_tables_age$sleep$caption,
-  note = model_tables_age$sleep$note,
-  col_spanners = model_tables_age$sleep$col_spanners,
+  model_tables_by_age$sleep$data,
+  caption = model_tables_by_age$sleep$caption,
+  note = model_tables_by_age$sleep$note,
+  col_spanners = model_tables_by_age$sleep$col_spanners,
   escape = FALSE,
@@
 These plots demonstrate exact turning points where the effects of PA volume change by age."}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_volume), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_intensity), error = FALSE)
 ```
@@
 papaja::apa_table(
-  model_tables_age$physical_activity$data,
-  caption = model_tables_age$physical_activity$caption,
-  note = model_tables_age$physical_activity$note,
-  col_spanners = model_tables_age$physical_activity$col_spanners,
+  model_tables_by_age$physical_activity$data,
+  caption = model_tables_by_age$physical_activity$caption,
+  note = model_tables_by_age$physical_activity$note,
+  col_spanners = model_tables_by_age$physical_activity$col_spanners,
   escape = FALSE,
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 The white band indicates predictions which were not significantly different from zero."}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-13 doc/multiverse.Rmd
Automate docs
Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

Should prevent the cases where the images are being renamed
and not matching the files.

@@
 ```{r load-targets, include=FALSE}
-model_list_by_age_fixedef <- tar_read(model_list_by_age_fixedef)
-tar_load(data_clean)
-tar_load(purdy_pictures_by_age_fixedef)
-model_tables <- tar_read(model_tables_fixedef)
+tar_load(multiverse_file)
 pretty <- function(x) format(x, big.mark = ",")
@@
 # Results
-
-```{r}
-n_participants <- length(unique(data_clean$participant_id))
-```
 
@@
 
-## Multiverse
+## Fixed Effect Model
 
-In this document we show the results using another analytic technique. Namely treating study ID as a fixed effect. This is what we wrote in the protocol originally.
+```{r}
+tar_load(model_tables_by_age_fixedef)
+tar_load(purdy_pictures_by_age_fixedef)
+```
 
-## The effects of physical activity volume on sleep
+In this document we show the results using another analytic technique. 
+Namely treating study ID as a fixed effect. 
+This is what we wrote in the protocol originally.
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
+### The effects of physical activity volume on sleep
 
-```{r sleep-outcomes}
+We estimated the effects of physical activity on sleep (RQ1) using fixed-effects models.
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-fixedef) and Figure \@ref(fig:sleep-by-volume-fig-fixedef).
+
+```{r sleep-outcomes-fixedef}
 papaja::apa_table(
-  model_tables$sleep$data,
-  caption = model_tables$sleep$caption,
-  note = model_tables$sleep$note,
-  col_spanners = model_tables$sleep$col_spanners,
+  model_tables_by_age_fixedef$sleep$data,
+  caption = model_tables_by_age_fixedef$sleep$caption,
+  note = model_tables_by_age_fixedef$sleep$note,
+  col_spanners = model_tables_by_age_fixedef$sleep$col_spanners,
   escape = FALSE,
@@
 
-```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age_fixedef.jpg"), error = FALSE)
+```{r sleep-by-volume-fig-fixedef, fig.cap = "Sleep metrics on Physical activity volume"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_pa_volume), error = FALSE)
 ```
 
-## The effects of physical activity intensity on sleep
+### The effects of physical activity intensity on sleep
 
-We estimated how physical activity intensity affects sleep across different age groups
-We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
+We estimated how physical activity intensity affects sleep across different age groups.
+We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes-fixedef) and Figure \@ref(fig:sleep-by-intensity-fig-fixedef).
 
-```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
-knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age_fixedef.jpg"), error = FALSE)
+```{r sleep-by-intensity-fig-fixedef, fig.cap = "Sleep metrics on Physical activity intensity"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_pa_intensity), error = FALSE)
 ```
 
-## The effects of sleep duration on physical activity
+### The effects of sleep duration on physical activity
 
-We estimated the effect of sleep duration on physical activity by age
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
+We estimated the effect of sleep duration on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-duration-fig-fixedef).
 
-```{r pa-outcomes}
+```{r pa-outcomes-fixedef}
 papaja::apa_table(
-  model_tables$physical_activity$data,
-  caption = model_tables$physical_activity$caption,
-  note = model_tables$physical_activity$note,
-  col_spanners = model_tables$physical_activity$col_spanners,
+  model_tables_by_age_fixedef$physical_activity$data,
+  caption = model_tables_by_age_fixedef$physical_activity$caption,
+  note = model_tables_by_age_fixedef$physical_activity$note,
+  col_spanners = model_tables_by_age_fixedef$physical_activity$col_spanners,
   escape = FALSE,
@@
 
-```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
-knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
+```{r PA-by-sleep-duration-fig-fixedef, fig.cap = "Physical activity by sleep duration"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_duration_lag), error = FALSE)
 ```
 
-## The effects of sleep efficiency on physical activity
+### The effects of sleep efficiency on physical activity
 
 We estimated the effect of sleep efficiency on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-fixedef).
 
-```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
-knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
+```{r PA-by-sleep-efficiency-fig-fixedef, fig.cap = "Physical activity by sleep efficiency"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_efficiency_lag), error = FALSE)
 ```
 
-## The effects of sleep onset on physical activity
+### The effects of sleep onset on physical activity
 
-We estimated the effect of sleep onset on physical activity by age
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
+We estimated the effect of sleep onset on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-onset-fig-fixedef).
 
-```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
-knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
+```{r PA-by-sleep-onset-fig-fixedef, fig.cap = "Physical activity by sleep onset"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_onset_lag), error = FALSE)
 ```
 
-## The effects of sleep regularity on physical activity
+### The effects of sleep regularity on physical activity
 
 We estimated the effect of sleep regularity on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-regularity-fig-fixedef).
 
-```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
-knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
+```{r PA-by-sleep-regularity-fig-fixedef, fig.cap = "Physical activity by sleep regularity"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_regularity_lag), error = FALSE)
+```
+
+## Without Log Transforming PA Volume
+
+```{r}
+tar_load(model_tables_by_age_nolog)
+tar_load(purdy_pictures_by_age_nolog)
+```
+
+Based on preliminary modelling on a subset of the data, we chose to log transform the physical activity volume variable.
+Below, we present the results had we not made this decision.
+These results are all moderated by age, as this was our primary analysis.
+
+### The effects of physical activity volume on sleep
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-nolog) and Figure \@ref(fig:sleep-by-volume-fig-nolog).
+
+```{r sleep-outcomes-nolog}
+papaja::apa_table(
+  model_tables_by_age_nolog$sleep$data,
+  caption = model_tables_by_age_nolog$sleep$caption,
+  note = model_tables_by_age_nolog$sleep$note,
+  col_spanners = model_tables_by_age_nolog$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r sleep-by-volume-fig-nolog, fig.cap = "Sleep metrics on Physical activity volume"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_pa_volume), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-duration-fig-nolog).
+
+```{r pa-outcomes-nolog}
+papaja::apa_table(
+  model_tables_by_age_nolog$physical_activity$data,
+  caption = model_tables_by_age_nolog$physical_activity$caption,
+  note = model_tables_by_age_nolog$physical_activity$note,
+  col_spanners = model_tables_by_age_nolog$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r PA-by-sleep-duration-fig-nolog, fig.cap = "Physical activity by sleep duration"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_duration_lag), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-nolog).
+
+```{r PA-by-sleep-efficiency-fig-nolog, fig.cap = "Physical activity by sleep efficiency"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_efficiency_lag), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-onset-fig-nolog).
+
+```{r PA-by-sleep-onset-fig-nolog, fig.cap = "Physical activity by sleep onset"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_onset_lag), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by age.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-regularity-fig-nolog).
+
+```{r PA-by-sleep-regularity-fig-nolog, fig.cap = "Physical activity by sleep regularity"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 In the following section we present models for a range of moderators which were pre-defined in our protocol.
-
-```{r eval = FALSE}
-pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")
-
-moderator_df <- data.frame(
-  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
-  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
-  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Acc_wear_loc", "Pa_mostactivehr")
-)
-
-lapply(seq_len(nrow(moderator_df)), function(r) {
-  moderator <- moderator_df$moderator[r]
-  moderator_fig <- gsub("_", "-", moderator)
-  moderator_formal <- moderator_df$moderator_formal[r]
-  image_path <- moderator_df$image_path[r]
-
-  glue::glue(pattern, .open = "_::", .close = "::_")
-}) |>
-  paste(collapse = "\n") |>
-  clipr::write_clip()
-```
-
-<!------------------------------------>
-<!-- Auto-generated chunks go here: -->
-<!------------------------------------>
-
 \clearpage
@@
 ```{r}
-tar_load(model_tables_bmi)
+tar_load(model_tables_by_bmi)
+tar_load(purdy_pictures_by_bmi)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)
@@
 papaja::apa_table(
-  model_tables_bmi$sleep$data,
-  caption = model_tables_bmi$sleep$caption,
-  note = model_tables_bmi$sleep$note,
-  col_spanners = model_tables_bmi$sleep$col_spanners,
+  model_tables_by_bmi$sleep$data,
+  caption = model_tables_by_bmi$sleep$caption,
+  note = model_tables_by_bmi$sleep$note,
+  col_spanners = model_tables_by_bmi$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across BMI
+We estimated how physical activity intensity affects sleep across BMI.
 We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).
@@
 ```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by BMI
+We estimated the effect of sleep duration on physical activity by BMI.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
@@
 papaja::apa_table(
-  model_tables_bmi$physical_activity$data,
-  caption = model_tables_bmi$physical_activity$caption,
-  note = model_tables_bmi$physical_activity$note,
-  col_spanners = model_tables_bmi$physical_activity$col_spanners,
+  model_tables_by_bmi$physical_activity$data,
+  caption = model_tables_by_bmi$physical_activity$caption,
+  note = model_tables_by_bmi$physical_activity$note,
+  col_spanners = model_tables_by_bmi$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by BMI
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).
+We estimated the effect of sleep onset on physical activity by BMI.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).
 
 ```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_ses)
+tar_load(model_tables_by_ses)
+tar_load(purdy_pictures_by_ses)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)
@@
 papaja::apa_table(
-  model_tables_ses$sleep$data,
-  caption = model_tables_ses$sleep$caption,
-  note = model_tables_ses$sleep$note,
-  col_spanners = model_tables_ses$sleep$col_spanners,
+  model_tables_by_ses$sleep$data,
+  caption = model_tables_by_ses$sleep$caption,
+  note = model_tables_by_ses$sleep$note,
+  col_spanners = model_tables_by_ses$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across SES
+We estimated how physical activity intensity affects sleep across SES.
 We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).
@@
 ```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by SES
+We estimated the effect of sleep duration on physical activity by SES.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
@@
 papaja::apa_table(
-  model_tables_ses$physical_activity$data,
-  caption = model_tables_ses$physical_activity$caption,
-  note = model_tables_ses$physical_activity$note,
-  col_spanners = model_tables_ses$physical_activity$col_spanners,
+  model_tables_by_ses$physical_activity$data,
+  caption = model_tables_by_ses$physical_activity$caption,
+  note = model_tables_by_ses$physical_activity$note,
+  col_spanners = model_tables_by_ses$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by SES
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).
+We estimated the effect of sleep onset on physical activity by SES.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).
 
 ```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_sex)
+tar_load(model_tables_by_sex)
+tar_load(purdy_pictures_by_sex)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)
@@
 papaja::apa_table(
-  model_tables_sex$sleep$data,
-  caption = model_tables_sex$sleep$caption,
-  note = model_tables_sex$sleep$note,
-  col_spanners = model_tables_sex$sleep$col_spanners,
+  model_tables_by_sex$sleep$data,
+  caption = model_tables_by_sex$sleep$caption,
+  note = model_tables_by_sex$sleep$note,
+  col_spanners = model_tables_by_sex$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across sex
+We estimated how physical activity intensity affects sleep across sex.
 We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).
@@
 ```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by sex
+We estimated the effect of sleep duration on physical activity by sex.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
@@
 papaja::apa_table(
-  model_tables_sex$physical_activity$data,
-  caption = model_tables_sex$physical_activity$caption,
-  note = model_tables_sex$physical_activity$note,
-  col_spanners = model_tables_sex$physical_activity$col_spanners,
+  model_tables_by_sex$physical_activity$data,
+  caption = model_tables_by_sex$physical_activity$caption,
+  note = model_tables_by_sex$physical_activity$note,
+  col_spanners = model_tables_by_sex$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by sex
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).
+We estimated the effect of sleep onset on physical activity by sex.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).
 
 ```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_weekday)
+tar_load(model_tables_by_weekday)
+tar_load(purdy_pictures_by_weekday)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)
@@
 papaja::apa_table(
-  model_tables_weekday$sleep$data,
-  caption = model_tables_weekday$sleep$caption,
-  note = model_tables_weekday$sleep$note,
-  col_spanners = model_tables_weekday$sleep$col_spanners,
+  model_tables_by_weekday$sleep$data,
+  caption = model_tables_by_weekday$sleep$caption,
+  note = model_tables_by_weekday$sleep$note,
+  col_spanners = model_tables_by_weekday$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across weekday
+We estimated how physical activity intensity affects sleep across weekday.
 We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).
@@
 ```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by weekday
+We estimated the effect of sleep duration on physical activity by weekday.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
@@
 papaja::apa_table(
-  model_tables_weekday$physical_activity$data,
-  caption = model_tables_weekday$physical_activity$caption,
-  note = model_tables_weekday$physical_activity$note,
-  col_spanners = model_tables_weekday$physical_activity$col_spanners,
+  model_tables_by_weekday$physical_activity$data,
+  caption = model_tables_by_weekday$physical_activity$caption,
+  note = model_tables_by_weekday$physical_activity$note,
+  col_spanners = model_tables_by_weekday$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by weekday
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).
+We estimated the effect of sleep onset on physical activity by weekday.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).
 
 ```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Weekday_x.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_season)
+tar_load(model_tables_by_season)
+tar_load(purdy_pictures_by_season)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by season, and the results are presented in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-volume-fig-by-season)
@@
 papaja::apa_table(
-  model_tables_season$sleep$data,
-  caption = model_tables_season$sleep$caption,
-  note = model_tables_season$sleep$note,
-  col_spanners = model_tables_season$sleep$col_spanners,
+  model_tables_by_season$sleep$data,
+  caption = model_tables_by_season$sleep$caption,
+  note = model_tables_by_season$sleep$note,
+  col_spanners = model_tables_by_season$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-season, fig.cap = "Sleep metrics on Physical activity volume by season"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across season
+We estimated how physical activity intensity affects sleep across season.
 We present the results in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-intensity-fig-by-season).
@@
 ```{r sleep-by-intensity-fig-by-season, fig.cap = "Sleep metrics on Physical activity intensity moderated by season"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by season
+We estimated the effect of sleep duration on physical activity by season.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
@@
 papaja::apa_table(
-  model_tables_season$physical_activity$data,
-  caption = model_tables_season$physical_activity$caption,
-  note = model_tables_season$physical_activity$note,
-  col_spanners = model_tables_season$physical_activity$col_spanners,
+  model_tables_by_season$physical_activity$data,
+  caption = model_tables_by_season$physical_activity$caption,
+  note = model_tables_by_season$physical_activity$note,
+  col_spanners = model_tables_by_season$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by season
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).
+We estimated the effect of sleep onset on physical activity by season.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).
 
 ```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Season.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_region)
+tar_load(model_tables_by_region)
+tar_load(purdy_pictures_by_region)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by region, and the results are presented in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-volume-fig-by-region)
@@
 papaja::apa_table(
-  model_tables_region$sleep$data,
-  caption = model_tables_region$sleep$caption,
-  note = model_tables_region$sleep$note,
-  col_spanners = model_tables_region$sleep$col_spanners,
+  model_tables_by_region$sleep$data,
+  caption = model_tables_by_region$sleep$caption,
+  note = model_tables_by_region$sleep$note,
+  col_spanners = model_tables_by_region$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-region, fig.cap = "Sleep metrics on Physical activity volume by region"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across region
+We estimated how physical activity intensity affects sleep across region.
 We present the results in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-intensity-fig-by-region).
@@
 ```{r sleep-by-intensity-fig-by-region, fig.cap = "Sleep metrics on Physical activity intensity moderated by region"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by region
+We estimated the effect of sleep duration on physical activity by region.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
@@
 papaja::apa_table(
-  model_tables_region$physical_activity$data,
-  caption = model_tables_region$physical_activity$caption,
-  note = model_tables_region$physical_activity$note,
-  col_spanners = model_tables_region$physical_activity$col_spanners,
+  model_tables_by_region$physical_activity$data,
+  caption = model_tables_by_region$physical_activity$caption,
+  note = model_tables_by_region$physical_activity$note,
+  col_spanners = model_tables_by_region$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by region
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).
+We estimated the effect of sleep onset on physical activity by region.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).
 
 ```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Region.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_daylight)
+tar_load(model_tables_by_daylight)
+tar_load(purdy_pictures_by_daylight)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight)
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight-hours)
 
-```{r sleep-outcomes-by-daylight}
+```{r sleep-outcomes-by-daylight-hours}
 papaja::apa_table(
-  model_tables_daylight$sleep$data,
-  caption = model_tables_daylight$sleep$caption,
-  note = model_tables_daylight$sleep$note,
-  col_spanners = model_tables_daylight$sleep$col_spanners,
+  model_tables_by_daylight$sleep$data,
+  caption = model_tables_by_daylight$sleep$caption,
+  note = model_tables_by_daylight$sleep$note,
+  col_spanners = model_tables_by_daylight$sleep$col_spanners,
   escape = FALSE,
@@
 
-```{r sleep-by-volume-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Daylight_hours.jpg"), error = FALSE)
+```{r sleep-by-volume-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across daylight hours
-We present the results in Table \@ref(tab:sleep-outcomes-by-daylight) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight).
+We estimated how physical activity intensity affects sleep across daylight hours.
+We present the results in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight-hours).
 
-```{r sleep-by-intensity-fig-by-daylight, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Daylight_hours.jpg"), error = FALSE)
+```{r sleep-by-intensity-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by daylight hours
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).
+We estimated the effect of sleep duration on physical activity by daylight hours.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight-hours).
 
-```{r pa-outcomes-by-daylight}
+```{r pa-outcomes-by-daylight-hours}
 papaja::apa_table(
-  model_tables_daylight$physical_activity$data,
-  caption = model_tables_daylight$physical_activity$caption,
-  note = model_tables_daylight$physical_activity$note,
-  col_spanners = model_tables_daylight$physical_activity$col_spanners,
+  model_tables_by_daylight$physical_activity$data,
+  caption = model_tables_by_daylight$physical_activity$caption,
+  note = model_tables_by_daylight$physical_activity$note,
+  col_spanners = model_tables_by_daylight$physical_activity$col_spanners,
   escape = FALSE,
@@
 
-```{r PA-by-sleep-duration-fig-by-daylight, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Daylight_hours.jpg"), error = FALSE)
+```{r PA-by-sleep-duration-fig-by-daylight-hours, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep efficiency on physical activity by daylight hours.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight-hours).
 
-```{r PA-by-sleep-efficiency-fig-by-daylight, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Daylight_hours.jpg"), error = FALSE)
+```{r PA-by-sleep-efficiency-fig-by-daylight-hours, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by daylight hours
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight).
+We estimated the effect of sleep onset on physical activity by daylight hours.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight-hours).
 
-```{r PA-by-sleep-onset-fig-by-daylight, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Daylight_hours.jpg"), error = FALSE)
+```{r PA-by-sleep-onset-fig-by-daylight-hours, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep regularity on physical activity by daylight hours.
-Results are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).
+Results are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight-hours).
 
-```{r PA-by-sleep-regularity-fig-by-daylight, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Daylight_hours.jpg"), error = FALSE)
+```{r PA-by-sleep-regularity-fig-by-daylight-hours, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
+knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_wear_location)
+tar_load(model_tables_by_wear_location)
+tar_load(purdy_pictures_by_wear_location)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
-We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-volume-fig-by-acc-wear-loc)
 
-```{r sleep-outcomes-by-wear-location}
+```{r sleep-outcomes-by-acc-wear-loc}
 papaja::apa_table(
-  model_tables_wear_location$sleep$data,
-  caption = model_tables_wear_location$sleep$caption,
-  note = model_tables_wear_location$sleep$note,
-  col_spanners = model_tables_wear_location$sleep$col_spanners,
+  model_tables_by_wear_location$sleep$data,
+  caption = model_tables_by_wear_location$sleep$caption,
+  note = model_tables_by_wear_location$sleep$note,
+  col_spanners = model_tables_by_wear_location$sleep$col_spanners,
   escape = FALSE,
@@
 
-```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Acc_wear_loc.jpg"), error = FALSE)
+```{r sleep-by-volume-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across wear location
-We present the results in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).
+We estimated how physical activity intensity affects sleep across wear location.
+We present the results in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-intensity-fig-by-acc-wear-loc).
 
-```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Acc_wear_loc.jpg"), error = FALSE)
+```{r sleep-by-intensity-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by wear location
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).
+We estimated the effect of sleep duration on physical activity by wear location.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-acc-wear-loc).
 
-```{r pa-outcomes-by-wear-location}
+```{r pa-outcomes-by-acc-wear-loc}
 papaja::apa_table(
-  model_tables_wear_location$physical_activity$data,
-  caption = model_tables_wear_location$physical_activity$caption,
-  note = model_tables_wear_location$physical_activity$note,
-  col_spanners = model_tables_wear_location$physical_activity$col_spanners,
+  model_tables_by_wear_location$physical_activity$data,
+  caption = model_tables_by_wear_location$physical_activity$caption,
+  note = model_tables_by_wear_location$physical_activity$note,
+  col_spanners = model_tables_by_wear_location$physical_activity$col_spanners,
   escape = FALSE,
@@
 
-```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Acc_wear_loc.jpg"), error = FALSE)
+```{r PA-by-sleep-duration-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep duration moderated by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep efficiency on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-acc-wear-loc).
 
-```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Acc_wear_loc.jpg"), error = FALSE)
+```{r PA-by-sleep-efficiency-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by wear location
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-wear-location).
+We estimated the effect of sleep onset on physical activity by wear location.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-acc-wear-loc).
 
-```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Acc_wear_loc.jpg"), error = FALSE)
+```{r PA-by-sleep-onset-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep onset moderated by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep regularity on physical activity by wear location.
-Results are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
+Results are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-acc-wear-loc).
 
-```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Acc_wear_loc.jpg"), error = FALSE)
+```{r PA-by-sleep-regularity-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
+knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_regularity_lag), error = FALSE)
 ```
@@
 ```{r}
-tar_load(model_tables_pa_mostactivehr)
+tar_load(model_tables_by_pa_mostactivehr)
+tar_load(purdy_pictures_by_pa_mostactivehr)
 ```
@@
 
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
 We estimated the effect of physical activity volume on sleep by most active hour, and the results are presented in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-volume-fig-by-pa-mostactivehr)
@@
 papaja::apa_table(
-  model_tables_pa_mostactivehr$sleep$data,
-  caption = model_tables_pa_mostactivehr$sleep$caption,
-  note = model_tables_pa_mostactivehr$sleep$note,
-  col_spanners = model_tables_pa_mostactivehr$sleep$col_spanners,
+  model_tables_by_pa_mostactivehr$sleep$data,
+  caption = model_tables_by_pa_mostactivehr$sleep$caption,
+  note = model_tables_by_pa_mostactivehr$sleep$note,
+  col_spanners = model_tables_by_pa_mostactivehr$sleep$col_spanners,
   escape = FALSE,
@@
 ```{r sleep-by-volume-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity volume by most active hour"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_volume), error = FALSE)
 ```
@@
 
-We estimated how physical activity intensity affects sleep across most active hour
+We estimated how physical activity intensity affects sleep across most active hour.
 We present the results in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-intensity-fig-by-pa-mostactivehr).
@@
 ```{r sleep-by-intensity-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity intensity moderated by most active hour"}
-knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_intensity), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep duration on physical activity by most active hour
+We estimated the effect of sleep duration on physical activity by most active hour.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-pa-mostactivehr).
@@
 papaja::apa_table(
-  model_tables_pa_mostactivehr$physical_activity$data,
-  caption = model_tables_pa_mostactivehr$physical_activity$caption,
-  note = model_tables_pa_mostactivehr$physical_activity$note,
-  col_spanners = model_tables_pa_mostactivehr$physical_activity$col_spanners,
+  model_tables_by_pa_mostactivehr$physical_activity$data,
+  caption = model_tables_by_pa_mostactivehr$physical_activity$caption,
+  note = model_tables_by_pa_mostactivehr$physical_activity$note,
+  col_spanners = model_tables_by_pa_mostactivehr$physical_activity$col_spanners,
   escape = FALSE,
@@
 ```{r PA-by-sleep-duration-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep duration moderated by most active hour"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-efficiency-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep efficiency moderated by most active hour"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 
-We estimated the effect of sleep onset on physical activity by most active hour
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).
+We estimated the effect of sleep onset on physical activity by most active hour.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).
 
 ```{r PA-by-sleep-onset-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep onset moderated by most active hour"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 ```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
-knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Pa_mostactivehr.jpg"), error = FALSE)
+knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_regularity_lag), error = FALSE)
 ```
-
-<!-- Finish auto-generated chunks go here: -->

### 2023-04-13 R/make_model_list.R

@@ -74,7 +74,15 @@ make_model_list <- function(data_imp,
     }
   )
 
+  # Add some attributes used in other targets
   names(out) <- instructions[, "model_name"]
   attr(out, "vars") <- list(sleep_vars = sleep_vars, pa_vars = pa_vars)
+  attr(out, "filename_suffix") <-
+    dplyr::case_when(
+      "studyid" %in% control_vars ~ "_fixedef",
+      "scale_pa_volume" %in% pa_vars ~ "_nolog",
+      TRUE ~ ""
+    )
+
   out
 }

### 2023-04-13 R/make_multiverse_file.R

@@ -1,0 +1,34 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param multiverse_skeleton
+#' @param multiverse_chunk
+#' @param models_df
+#' @return
+#' @export
+make_multiverse_file <- function(multiverse_skeleton,
+                                 multiverse_chunk, models_df) {
+  multiverse_skeleton_lines <- readLines(multiverse_skeleton)
+
+  moderator_df <- models_df %>%
+    dplyr::select(model_name, moderator, mod_formal) %>%
+    dplyr::filter(moderator != "age")
+
+  pattern <- readLines(multiverse_chunk) |> paste(collapse = "\n")
+
+  results_chunks <- lapply(seq_len(nrow(moderator_df)), function(r) {
+    moderator <- moderator_df$moderator[r]
+    moderator_fig <- gsub("_", "-", moderator)
+    moderator_formal <- moderator_df$mod_formal[r]
+    model_name <- moderator_df$model_name[r]
+
+    glue::glue(pattern, .open = "_::", .close = "::_")
+  })
+
+  write(multiverse_skeleton_lines, "doc/multiverse.Rmd")
+  write(unlist(results_chunks), "doc/multiverse.Rmd", append = TRUE)
+
+  return("doc/multiverse.Rmd")
+}

### 2023-04-13 R/produce_purdy_pictures.R

@@ -4,15 +4,14 @@
 #' @details I check the proporiton of models that converged. If less then 75% of models converged
 #' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge
 
-produce_purdy_pictures <- function(model_list) {
+produce_purdy_pictures <- function(model_list, ...) {
   dat_list <- lapply(seq_len(length(model_list)), function(i) {
     model_list[[i]]$model_assets$effects
   })
 
   moderator <- attr(model_list[[1]], "moderator")
 
-  add_filename <-
-    if ("studyid" %in% model_list[[1]]$control_vars) "_fixedef" else ""
+  add_filename <- attr(model_list, "filename_suffix")
 
   # Additional labels
   f_df <- data.frame(

### 2023-04-13 _targets.R

@@ -25,29 +25,31 @@ if (Sys.getenv("GCS_AUTH_FILE") != "") {
 }
 
 # Model parameters
-default_pa <- c("log_pa_volume", "scale_pa_intensity")
+dflt_pa <- c("log_pa_volume", "scale_pa_intensity")
 scale_pa <- c("scale_pa_volume", "scale_pa_intensity")
-default_sleep <- c(
+dflt_sleep <- c(
   "scale_sleep_duration", "scale_sleep_efficiency", "scale_sleep_onset",
   "scale_sleep_regularity"
 )
-default_ranef <- "(1|studyid) + (1|participant_id)"
-fixedef <- "(1 | measurement_day) + (1 | participant_id)"
+dflt_ranef <- "(1|studyid) + (1|participant_id)"
+fixedef <- "(1|measurement_day) + (1|participant_id)"
+dflt_con <- c("ses", "age", "sex", "bmi")
 
 # nolint start styler: off
-models <- dplyr::tribble(
-  ~model_name,          ~moderator,        ~moderator_term,  ~pa_vars,   ~sleep_vars,   ~ranef,
-  "by_age",             "age",             "11, 18, 35, 65", default_pa, default_sleep, default_ranef,
-  "by_age_fixedef",     "age",             "11, 18, 35, 65", default_pa, default_sleep, fixedef,
-  "by_age_nolog",       "age",             "11, 18, 35, 65", scale_pa,   default_sleep, default_ranef,
-  "by_bmi",             "bmi",             "18, 22, 25, 30", default_pa, default_sleep, default_ranef,
-  "by_ses",             "ses",             "all",            default_pa, default_sleep, default_ranef,
-  "by_weekday",         "weekday_x",       "all",            default_pa, default_sleep, default_ranef,
-  "by_season",          "season",          "all",            default_pa, default_sleep, default_ranef,
-  "by_region",          "region",          "all",            default_pa, default_sleep, default_ranef,
-  "by_daylight",        "daylight_hours",  "8, 10, 12, 14",  default_pa, default_sleep, default_ranef,
-  "by_wear_location",   "acc_wear_loc",    "all",            default_pa, default_sleep, default_ranef,
-  "by_pa_mostactivehr", "pa_mostactivehr", "5, 9, 14, 19",   default_pa, default_sleep, default_ranef
+models_df <- dplyr::tribble(
[…]

### 2023-04-13 R/models.R
Move models to seperate file and rerun pipeline

@@ -1,0 +1,28 @@
+# Model parameters
+dflt_pa <- c("log_pa_volume", "scale_pa_intensity")
+scale_pa <- c("scale_pa_volume", "scale_pa_intensity")
+dflt_sleep <- c(
+  "scale_sleep_duration", "scale_sleep_efficiency", "scale_sleep_onset",
+  "scale_sleep_regularity"
+)
+dflt_ranef <- "(1|studyid) + (1|participant_id)"
+fixedef <- "(1|participant_id)"
+dflt_con <- c("ses", "age", "sex", "bmi")
+
+# nolint start styler: off
+models_df <- dplyr::tribble(
+  ~model_name,          ~moderator,        ~mod_term,        ~mod_formal,        ~pa_vars, ~sleep_vars, ~ranef,     ~cont_vars,
+  "by_age",             "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_age_fixedef",     "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  fixedef,    c(dflt_con, "studyid"),
+  "by_age_nolog",       "age",             "11, 18, 35, 65", "age",              scale_pa, dflt_sleep,  dflt_ranef, dflt_con,
+  "by_bmi",             "bmi",             "18, 22, 25, 30", "BMI",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_ses",             "ses",             "all",            "SES",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_sex",             "sex",             "all",            "sex",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_weekday",         "weekday",         "all",            "weekday",          dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_season",          "season",          "all",            "season",           dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_region",          "region",          "all",            "region",           dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
+  "by_daylight",        "daylight_hours",  "8, 10, 12, 14",  "daylight hours",   dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
[…]

### 2023-04-13 _targets.R

@@ -24,35 +24,6 @@ if (Sys.getenv("GCS_AUTH_FILE") != "") {
   repository <- targets::tar_option_get("repository")
 }
 
-# Model parameters
-dflt_pa <- c("log_pa_volume", "scale_pa_intensity")
-scale_pa <- c("scale_pa_volume", "scale_pa_intensity")
-dflt_sleep <- c(
-  "scale_sleep_duration", "scale_sleep_efficiency", "scale_sleep_onset",
-  "scale_sleep_regularity"
-)
-dflt_ranef <- "(1|studyid) + (1|participant_id)"
-fixedef <- "(1|measurement_day) + (1|participant_id)"
-dflt_con <- c("ses", "age", "sex", "bmi")
-
-# nolint start styler: off
-models_df <- dplyr::tribble(
-  ~model_name,          ~moderator,        ~mod_term,        ~mod_formal,        ~pa_vars, ~sleep_vars, ~ranef,     ~cont_vars,
-  "by_age",             "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_age_fixedef",     "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  fixedef,    c(dflt_con, "studyid"),
-  "by_age_nolog",       "age",             "11, 18, 35, 65", "age",              scale_pa, dflt_sleep,  dflt_ranef, dflt_con,
-  "by_bmi",             "bmi",             "18, 22, 25, 30", "BMI",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_ses",             "ses",             "all",            "SES",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_sex",             "sex",             "all",            "sex",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_weekday",         "weekday",         "all",            "weekday",          dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_season",          "season",          "all",            "season",           dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
-  "by_region",          "region",          "all",            "region",           dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
[…]

### 2023-04-13 doc/multiverse_skeleton.Rmd
Move to static branching (#87)
* make_model_list takes pa and sleep vars as args

* Fix number of imputations

Fixes #86

* Add log_pa_volume variable

* Clear up linting message in data_imp

* Manage control vars dynamically

* Use static branching

* Add vars attribute to model_list

Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

* Add pipeline tweaks to allow for log variable

Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

* Rerun pipeline

* rename weekday_x

* Automate docs

Co-authored-by: James Conigrave <12742211+conig@users.norep

--- 2023-04-13 doc/multiverse.Rmd
@@
 In the following section we present models for a range of moderators which were pre-defined in our protocol.
-\clearpage
-
-## BMI
-
-```{r}
-tar_load(model_tables_by_bmi)
-tar_load(purdy_pictures_by_bmi)
-```
-
-### The effects of physical activity volume on sleep by BMI
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)
-
-```{r sleep-outcomes-by-bmi}
-papaja::apa_table(
-  model_tables_by_bmi$sleep$data,
-  caption = model_tables_by_bmi$sleep$caption,
-  note = model_tables_by_bmi$sleep$note,
-  col_spanners = model_tables_by_bmi$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by BMI
-
-We estimated how physical activity intensity affects sleep across BMI.
-We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).
-
-```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by BMI.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).
-
-```{r pa-outcomes-by-bmi}
-papaja::apa_table(
-  model_tables_by_bmi$physical_activity$data,
-  caption = model_tables_by_bmi$physical_activity$caption,
-  note = model_tables_by_bmi$physical_activity$note,
-  col_spanners = model_tables_by_bmi$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by BMI.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-bmi).
-
-```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by BMI.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).
-
-```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by BMI.
-Results are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).
-
-```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
-knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## SES
-
-```{r}
-tar_load(model_tables_by_ses)
-tar_load(purdy_pictures_by_ses)
-```
-
-### The effects of physical activity volume on sleep by SES
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)
-
-```{r sleep-outcomes-by-ses}
-papaja::apa_table(
-  model_tables_by_ses$sleep$data,
-  caption = model_tables_by_ses$sleep$caption,
-  note = model_tables_by_ses$sleep$note,
-  col_spanners = model_tables_by_ses$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by SES
-
-We estimated how physical activity intensity affects sleep across SES.
-We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).
-
-```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by SES.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).
-
-```{r pa-outcomes-by-ses}
-papaja::apa_table(
-  model_tables_by_ses$physical_activity$data,
-  caption = model_tables_by_ses$physical_activity$caption,
-  note = model_tables_by_ses$physical_activity$note,
-  col_spanners = model_tables_by_ses$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by SES.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ses).
-
-```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by SES.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).
-
-```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by SES.
-Results are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).
-
-```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
-knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## sex
-
-```{r}
-tar_load(model_tables_by_sex)
-tar_load(purdy_pictures_by_sex)
-```
-
-### The effects of physical activity volume on sleep by sex
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)
-
-```{r sleep-outcomes-by-sex}
-papaja::apa_table(
-  model_tables_by_sex$sleep$data,
-  caption = model_tables_by_sex$sleep$caption,
-  note = model_tables_by_sex$sleep$note,
-  col_spanners = model_tables_by_sex$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by sex
-
-We estimated how physical activity intensity affects sleep across sex.
-We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).
-
-```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by sex.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).
-
-```{r pa-outcomes-by-sex}
-papaja::apa_table(
-  model_tables_by_sex$physical_activity$data,
-  caption = model_tables_by_sex$physical_activity$caption,
-  note = model_tables_by_sex$physical_activity$note,
-  col_spanners = model_tables_by_sex$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by sex.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-sex).
-
-```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by sex.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).
-
-```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by sex.
-Results are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).
-
-```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
-knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## weekday
-
-```{r}
-tar_load(model_tables_by_weekday)
-tar_load(purdy_pictures_by_weekday)
-```
-
-### The effects of physical activity volume on sleep by weekday
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)
-
-```{r sleep-outcomes-by-weekday}
-papaja::apa_table(
-  model_tables_by_weekday$sleep$data,
-  caption = model_tables_by_weekday$sleep$caption,
-  note = model_tables_by_weekday$sleep$note,
-  col_spanners = model_tables_by_weekday$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by weekday
-
-We estimated how physical activity intensity affects sleep across weekday.
-We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).
-
-```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by weekday.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).
-
-```{r pa-outcomes-by-weekday}
-papaja::apa_table(
-  model_tables_by_weekday$physical_activity$data,
-  caption = model_tables_by_weekday$physical_activity$caption,
-  note = model_tables_by_weekday$physical_activity$note,
-  col_spanners = model_tables_by_weekday$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by weekday.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-weekday).
-
-```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by weekday.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).
-
-```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by weekday.
-Results are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).
-
-```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
-knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## season
-
-```{r}
-tar_load(model_tables_by_season)
-tar_load(purdy_pictures_by_season)
-```
-
-### The effects of physical activity volume on sleep by season
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by season, and the results are presented in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-volume-fig-by-season)
-
-```{r sleep-outcomes-by-season}
-papaja::apa_table(
-  model_tables_by_season$sleep$data,
-  caption = model_tables_by_season$sleep$caption,
-  note = model_tables_by_season$sleep$note,
-  col_spanners = model_tables_by_season$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-season, fig.cap = "Sleep metrics on Physical activity volume by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by season
-
-We estimated how physical activity intensity affects sleep across season.
-We present the results in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-intensity-fig-by-season).
-
-```{r sleep-by-intensity-fig-by-season, fig.cap = "Sleep metrics on Physical activity intensity moderated by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by season.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).
-
-```{r pa-outcomes-by-season}
-papaja::apa_table(
-  model_tables_by_season$physical_activity$data,
-  caption = model_tables_by_season$physical_activity$caption,
-  note = model_tables_by_season$physical_activity$note,
-  col_spanners = model_tables_by_season$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by season.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-season).
-
-```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by season.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).
-
-```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by season.
-Results are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).
-
-```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
-knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## region
-
-```{r}
-tar_load(model_tables_by_region)
-tar_load(purdy_pictures_by_region)
-```
-
-### The effects of physical activity volume on sleep by region
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by region, and the results are presented in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-volume-fig-by-region)
-
-```{r sleep-outcomes-by-region}
-papaja::apa_table(
-  model_tables_by_region$sleep$data,
-  caption = model_tables_by_region$sleep$caption,
-  note = model_tables_by_region$sleep$note,
-  col_spanners = model_tables_by_region$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-region, fig.cap = "Sleep metrics on Physical activity volume by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by region
-
-We estimated how physical activity intensity affects sleep across region.
-We present the results in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-intensity-fig-by-region).
-
-```{r sleep-by-intensity-fig-by-region, fig.cap = "Sleep metrics on Physical activity intensity moderated by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by region.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).
-
-```{r pa-outcomes-by-region}
-papaja::apa_table(
-  model_tables_by_region$physical_activity$data,
-  caption = model_tables_by_region$physical_activity$caption,
-  note = model_tables_by_region$physical_activity$note,
-  col_spanners = model_tables_by_region$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by region.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-region).
-
-```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by region.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).
-
-```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by region.
-Results are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).
-
-```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
-knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## daylight hours
-
-```{r}
-tar_load(model_tables_by_daylight)
-tar_load(purdy_pictures_by_daylight)
-```
-
-### The effects of physical activity volume on sleep by daylight hours
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight-hours)
-
-```{r sleep-outcomes-by-daylight-hours}
-papaja::apa_table(
-  model_tables_by_daylight$sleep$data,
-  caption = model_tables_by_daylight$sleep$caption,
-  note = model_tables_by_daylight$sleep$note,
-  col_spanners = model_tables_by_daylight$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by daylight hours
-
-We estimated how physical activity intensity affects sleep across daylight hours.
-We present the results in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight-hours).
-
-```{r sleep-by-intensity-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by daylight hours.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight-hours).
-
-```{r pa-outcomes-by-daylight-hours}
-papaja::apa_table(
-  model_tables_by_daylight$physical_activity$data,
-  caption = model_tables_by_daylight$physical_activity$caption,
-  note = model_tables_by_daylight$physical_activity$note,
-  col_spanners = model_tables_by_daylight$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-daylight-hours, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by daylight hours.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight-hours).
-
-```{r PA-by-sleep-efficiency-fig-by-daylight-hours, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by daylight hours.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight-hours).
-
-```{r PA-by-sleep-onset-fig-by-daylight-hours, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by daylight hours.
-Results are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight-hours).
-
-```{r PA-by-sleep-regularity-fig-by-daylight-hours, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
-knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## wear location
-
-```{r}
-tar_load(model_tables_by_wear_location)
-tar_load(purdy_pictures_by_wear_location)
-```
-
-### The effects of physical activity volume on sleep by wear location
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-volume-fig-by-acc-wear-loc)
-
-```{r sleep-outcomes-by-acc-wear-loc}
-papaja::apa_table(
-  model_tables_by_wear_location$sleep$data,
-  caption = model_tables_by_wear_location$sleep$caption,
-  note = model_tables_by_wear_location$sleep$note,
-  col_spanners = model_tables_by_wear_location$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by wear location
-
-We estimated how physical activity intensity affects sleep across wear location.
-We present the results in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-intensity-fig-by-acc-wear-loc).
-
-```{r sleep-by-intensity-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-acc-wear-loc).
-
-```{r pa-outcomes-by-acc-wear-loc}
-papaja::apa_table(
-  model_tables_by_wear_location$physical_activity$data,
-  caption = model_tables_by_wear_location$physical_activity$caption,
-  note = model_tables_by_wear_location$physical_activity$note,
-  col_spanners = model_tables_by_wear_location$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep duration moderated by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-acc-wear-loc).
-
-```{r PA-by-sleep-efficiency-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by wear location.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-acc-wear-loc).
-
-```{r PA-by-sleep-onset-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep onset moderated by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by wear location.
-Results are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-acc-wear-loc).
-
-```{r PA-by-sleep-regularity-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
-knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_regularity_lag), error = FALSE)
-```
-\clearpage
-
-## most active hour
-
-```{r}
-tar_load(model_tables_by_pa_mostactivehr)
-tar_load(purdy_pictures_by_pa_mostactivehr)
-```
-
-### The effects of physical activity volume on sleep by most active hour
-
-We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by most active hour, and the results are presented in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-volume-fig-by-pa-mostactivehr)
-
-```{r sleep-outcomes-by-pa-mostactivehr}
-papaja::apa_table(
-  model_tables_by_pa_mostactivehr$sleep$data,
-  caption = model_tables_by_pa_mostactivehr$sleep$caption,
-  note = model_tables_by_pa_mostactivehr$sleep$note,
-  col_spanners = model_tables_by_pa_mostactivehr$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity volume by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_volume), error = FALSE)
-```
-
-### The effects of physical activity intensity on sleep by most active hour
-
-We estimated how physical activity intensity affects sleep across most active hour.
-We present the results in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-intensity-fig-by-pa-mostactivehr).
-
-```{r sleep-by-intensity-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity intensity moderated by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_intensity), error = FALSE)
-```
-
-### The effects of sleep duration on physical activity
-
-We estimated the effect of sleep duration on physical activity by most active hour.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-pa-mostactivehr).
-
-```{r pa-outcomes-by-pa-mostactivehr}
-papaja::apa_table(
-  model_tables_by_pa_mostactivehr$physical_activity$data,
-  caption = model_tables_by_pa_mostactivehr$physical_activity$caption,
-  note = model_tables_by_pa_mostactivehr$physical_activity$note,
-  col_spanners = model_tables_by_pa_mostactivehr$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep duration moderated by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_duration_lag), error = FALSE)
-```
-
-### The effects of sleep efficiency on physical activity
-
-We estimated the effect of sleep efficiency on physical activity by most active hour.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-pa-mostactivehr).
-
-```{r PA-by-sleep-efficiency-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep efficiency moderated by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_efficiency_lag), error = FALSE)
-```
-
-### The effects of sleep onset on physical activity
-
-We estimated the effect of sleep onset on physical activity by most active hour.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).
-
-```{r PA-by-sleep-onset-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep onset moderated by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_onset_lag), error = FALSE)
-```
-
-### The effects of sleep regularity on physical activity
-
-We estimated the effect of sleep regularity on physical activity by most active hour.
-Results are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-pa-mostactivehr).
-
-```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
-knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_regularity_lag), error = FALSE)
-```

### 2023-04-13 R/clean_data.R

@@ -27,7 +27,8 @@ clean_data <- function(data_joined, region_lookup) {
       sleep_wakeup = wakeup_p5,
       sleep_onset_time = sleeponset_ts_p5,
       sleep_wakeup_time = wakeup_ts_p5,
-      sleep_regularity = sleep_regularity_index
+      sleep_regularity = sleep_regularity_index,
+      acc_wear_loc = accelerometer_wear_location
     ) %>%
     # remove all the ggir data execpt the columns that we're using
     select(
@@ -46,11 +47,10 @@ clean_data <- function(data_joined, region_lookup) {
     ), as.numeric)) %>%
     # convert charcter variables to factors
     mutate(across(c(
-      studyid, sex, ethnicity,
-      ses, sleep_medications, sleep_conditions,
-      country, season, accelerometer_wear_location,
-      weekday_x, accelerometer_model
+      studyid, sex, ethnicity, ses, sleep_medications, sleep_conditions,
+      country, season, acc_wear_loc, weekday_x, accelerometer_model
     ), as.factor)) %>%
+    rename(weekday = weekday_x) %>%
     # convert calendar_date to date
     mutate(calendar_date = as.Date(calendar_date)) %>%
     # Add participant ID using the study and filename

### 2023-04-13 R/make_data_imp.R

@@ -24,8 +24,8 @@ make_data_imp <- function(data, n_imps = 3) {
   dont_imp <- c("filename", "calendar_date")
   dont_use <- c(
     "age_cat", "studyid", "participant_id", "country", "region",
-    "accelerometer_wear_location", "accelerometer_model", "pa_intensity_m16",
-    "pa_mostactivehr", "weekday_x"
+    "acc_wear_loc", "accelerometer_model", "pa_intensity_m16",
+    "pa_mostactivehr", "weekday"
   )
   # Don't imp some vars, and disable some as predictors
   meth <- m0$method
@@ -33,10 +33,11 @@ make_data_imp <- function(data, n_imps = 3) {
   meth[names(meth) %in% dont_imp] <- ""
   pred[, colnames(pred) %in% c(dont_use, dont_imp)] <- 0
 
-  participant_invar <- c("age","weight","height","bmi")
+  participant_invar <- c("age", "weight", "height", "bmi")
 
   participant_cont <-
-    c("pa_volume",
+    c(
+      "pa_volume",
       "pa_intensity",
       "pa_intensity_m16",
       "pa_mostactivehr",
@@ -53,8 +54,8 @@ make_data_imp <- function(data, n_imps = 3) {
     )
 
   # Multi-level imputation, consider correlations within participant
-  pred["sex",] <- 0
-  pred["sex", c("age","bmi","pa_intensity","screen_time","sleep_regularity")] <- 1
+  pred["sex", ] <- 0
+  pred["sex", c("age", "bmi", "pa_intensity", "screen_time", "sleep_regularity")] <- 1
   pred[c(participant_cont, participant_invar, "sex"), "participant_id"] <- -2L
   meth[c(participant_cont)] <- "2l.pmm"
   meth[c(participant_invar)] <- "2lonly.pmm"
@@ -63,17 +64,20 @@ make_data_imp <- function(data, n_imps = 3) {
   # Run imps with better settings
   future_cores <- min(parallel::detectCores() - 1, n_imps)
 
-  dist.core <- cut(1:n_imps, future_cores, labels = paste0("core", 1:future_cores))
-  n.imp.core <- as.vector(table(dist.core))
+  dist_core <- cut(
+    1:n_imps, future_cores,
+    labels = paste0("core", 1:future_cores)
+  )
+  n_imp_core <- as.vector(table(dist_core))
 
   future::plan("multisession",
     workers = future_cores
[…]

### 2023-04-13 R/make_model_list.R

@@ -7,42 +7,51 @@
 #' @return
 #' @author conig
 #' @export
-make_model_list <- function(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65", control_vars = c("ses", "sex", "bmi"), ranef  = "(1|studyid) + (1|participant_id)") {
-  sleep_vars <- c("scale_sleep_duration",
-                    "scale_sleep_efficiency",
-                    "scale_sleep_onset",
-                    "scale_sleep_regularity")
+make_model_list <- function(data_imp,
+                            moderator = "age",
+                            moderator_term = "11, 18, 35, 65",
+                            control_vars = c("ses", "age", "sex", "bmi"),
+                            ranef = "(1|studyid) + (1|participant_id)",
+                            sleep_vars = c(
+                              "scale_sleep_duration", "scale_sleep_efficiency",
+                              "scale_sleep_onset", "scale_sleep_regularity"
+                            ),
+                            pa_vars = c(
+                              "log_pa_volume", "scale_pa_intensity"
+                            )) {
+  control_vars <- control_vars[!control_vars == moderator]
 
   sleep_lag_vars <- paste0(sleep_vars, "_lag")
 
-  PA_vars <- c("scale_pa_volume", "scale_pa_intensity")
+  quadratic_pattern <- "{x} * {moderator} + I({x}^2) * {moderator}"
+  make_quadratic <- function(x) glue::glue(quadratic_pattern)
 
-  make_quadratic <- function(x) glue::glue("{x} * {moderator} + I({x}^2) * {moderator}")
-
-  instructions.rq1 <-
+  instructions_rq1 <-
     expand.grid(
       outcome = sleep_vars,
-      predictors = make_quadratic(PA_vars),
+      predictors = make_quadratic(pa_vars),
       RQ = 1,
       stringsAsFactors = FALSE
     )
 
-  instructions.rq3 <-
+  instructions_rq3 <-
     expand.grid(
-      outcome = PA_vars,
+      outcome = pa_vars,
       predictors = make_quadratic(sleep_lag_vars),
       RQ = 3,
       stringsAsFactors = FALSE
     )
 
-  instructions <- rbind(instructions.rq1, instructions.rq3)
+  instructions <- rbind(instructions_rq1, instructions_rq3)
 
[…]

### 2023-04-13 R/make_table1.R

@@ -8,32 +8,37 @@
 #' @author noetel & conigrave
 #' @export
 make_participant_summary <- function(data_clean) {
-
   require(dplyr)
   require(labelled)
 
   d <- data_clean %>%
-    select(n_valid_hours, accelerometer_wear_location,
-    pa_volume, pa_intensity,
-    sleep_duration, sleep_efficiency,
-    sleep_onset, sleep_wakeup,
-    sleep_regularity, # sleep_onset_time, sleep_wakeup_time,
-    sleep_duration, sleep_efficiency,
-    sex, age, height, weight, bmi, waist_circumference,
-    ses, screen_time, daylight_hours, city, eligible,
-    sleep_conditions, country, season, region, studyid, participant_id) %>%
-    mutate(studyid = as.factor(studyid),
-            city = as.factor(city),
-            season = as.factor(season))
+    select(
+      n_valid_hours, acc_wear_loc,
+      pa_volume, pa_intensity,
+      sleep_duration, sleep_efficiency,
+      sleep_onset, sleep_wakeup,
+      sleep_regularity, # sleep_onset_time, sleep_wakeup_time,
+      sleep_duration, sleep_efficiency,
+      sex, age, height, weight, bmi, waist_circumference,
+      ses, screen_time, daylight_hours, city, eligible,
+      sleep_conditions, country, season, region, studyid, participant_id
+    ) %>%
+    mutate(
+      studyid = as.factor(studyid),
+      city = as.factor(city),
+      season = as.factor(season)
+    )
 
   participants <- d %>%
     group_by(participant_id) %>%
-    summarise(across(where(is.numeric), mean, na.rm = TRUE),
-              across(where(is.factor), find_max),
-              across(where(is.logical), any)) %>%
+    summarise(
+      across(where(is.numeric), mean, na.rm = TRUE),
+      across(where(is.factor), find_max),
+      across(where(is.logical), any)
+    ) %>%
     mutate(sleep_conditions = as.factor(sleep_conditions))
 
-var_label(participants) <- c(
+  var_label(participants) <- c(
     "Participant ID",
     "Valid Weartime Hours",
     "PA Volume",
@@ -58,8 +63,8 @@ var_label(participants) <- c(
     "Season",
     "Region",
     "Study ID",
-    "Any Observations Met Weartime Criteria")
+    "Any Observations Met Weartime Criteria"
+  )
 
-participants
-
+  participants
 }

### 2023-04-13 R/produce_purdy_pictures.R

@@ -1,20 +1,32 @@
 #' produce_purdy_pictures
 #' @param model_list model_list
-#' @param paste_facet_labels character. String to paste to facet labels
-#' @param add_filename character. String to add to end of filenames
 #' @example  model_list <- model_list_by_age
 #' @details I check the proporiton of models that converged. If less then 75% of models converged
 #' then I overlay the message "DID NOT CONVERGE" providing the percent of models which did not converge
 
-produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_filename = "") {
+produce_purdy_pictures <- function(model_list, ...) {
   dat_list <- lapply(seq_len(length(model_list)), function(i) {
     model_list[[i]]$model_assets$effects
   })
 
+  moderator <- attr(model_list[[1]], "moderator")
+
+  add_filename <- attr(model_list, "filename_suffix")
+
+  # Additional labels
+  f_df <- data.frame(
+    moderator = c("age", "daylight_hours"),
+    facet_label = c(" years", " hours")
+  )
+
+  if (moderator %in% f_df$moderator) {
+    paste_facet_labels <- f_df$facet_label[f_df$moderator == moderator]
+  } else {
+    paste_facet_labels <- ""
+  }
+
   plot_dat <- data.table::rbindlist(dat_list) |>
     prepare_plot_data(paste_facet_labels)
-
-  moderator <- attr(model_list[[1]], "moderator")
 
   # Im the moderator is age, then, retrieve granular age predictions
 
@@ -38,7 +50,14 @@ produce_purdy_pictures <- function(model_list, paste_facet_labels = "", add_file
     pdat <- plot_dat[x_name == x_var & RQ == rq]
 
     conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
-    fig <- ggplot(pdat, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = group, fill = group)) +
+    fig <- ggplot(
+      pdat,
+      aes(
+        x = x, y = predicted,
+        ymin = conf.low, ymax = conf.high,
+        group = group, fill = group
+      )
+    ) +
       geom_line() +
[…]

### 2023-04-13 _targets.R

@@ -46,9 +46,10 @@ list(
   tar_target(region_lookup, make_region_lookup()),
   tar_target(demog_table, make_demog_table(participant_summary)),
   tar_target(
-    data_imp, make_data_imp(data_holdout, n_imps = 3), deployment = "main",
+    data_imp, make_data_imp(data_holdout, n_imps = 3),
+    deployment = "main",
     format = format, repository = repository
-    ),
+  ),
   tar_target(imputation_checks, check_imps(data_imp),
     format = "file",
     priority = 1
@@ -57,90 +58,20 @@ list(
   #################################################################
   ##                          MODELLING                          ##
   #################################################################
-
-  tar_target(
-    model_list_by_age,
-    make_model_list(data_imp, moderator = "age", moderator_term = "11, 18, 35, 65")
-  ),
-  tar_target(
-    model_list_by_bmi,
-    make_model_list(
-      data_imp,
-      moderator = "bmi",
-      moderator_term = "18, 22, 25, 30",
-      control_vars = c("ses", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_ses,
-    make_model_list(
-      data_imp,
-      moderator = "ses",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_sex,
-    make_model_list(
-      data_imp,
-      moderator = "sex",
-      moderator_term = "all",
-      control_vars = c("ses", "age", "bmi")
-    )
-  ),
-  tar_target(
-    model_list_by_weekday,
-    make_model_list(
-      data_imp,
-      moderator = "weekday_x",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_season,
-    make_model_list(
-      data_imp,
-      moderator = "season",
-      moderator_term = "all",
-      control_vars = c("bmi", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_region,
-    make_model_list(
-      data_imp,
-      moderator = "region",
-      moderator_term = "all",
-      control_vars = c("ses", "age", "sex")
-    )
-  ),
-  tar_target(
-    model_list_by_daylight,
-    make_model_list(
-      data_imp,
-      moderator = "daylight_hours",
[…]

### 2023-04-14 doc/multiverse.Rmd
Rerun pipeline
Add ethnicity to models
Closes #54

@@
 ```
+\clearpage
+
+## ethnicity
+
+```{r}
+tar_load(model_tables_by_ethnicity)
+tar_load(purdy_pictures_by_ethnicity)
+```
+
+### The effects of physical activity volume on sleep by ethnicity
+
+We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
+We estimated the effect of physical activity volume on sleep by ethnicity, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ethnicity) and Figure \@ref(fig:sleep-by-volume-fig-by-ethnicity)
+
+```{r sleep-outcomes-by-ethnicity}
+papaja::apa_table(
+  model_tables_by_ethnicity$sleep$data,
+  caption = model_tables_by_ethnicity$sleep$caption,
+  note = model_tables_by_ethnicity$sleep$note,
+  col_spanners = model_tables_by_ethnicity$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r sleep-by-volume-fig-by-ethnicity, fig.cap = "Sleep metrics on Physical activity volume by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_pa_volume), error = FALSE)
+```
+
+### The effects of physical activity intensity on sleep by ethnicity
+
+We estimated how physical activity intensity affects sleep across ethnicity.
+We present the results in Table \@ref(tab:sleep-outcomes-by-ethnicity) and Figure \@ref(fig:sleep-by-intensity-fig-by-ethnicity).
+
+```{r sleep-by-intensity-fig-by-ethnicity, fig.cap = "Sleep metrics on Physical activity intensity moderated by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_pa_intensity), error = FALSE)
+```
+
+### The effects of sleep duration on physical activity
+
+We estimated the effect of sleep duration on physical activity by ethnicity.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ethnicity).
+
+```{r pa-outcomes-by-ethnicity}
+papaja::apa_table(
+  model_tables_by_ethnicity$physical_activity$data,
+  caption = model_tables_by_ethnicity$physical_activity$caption,
+  note = model_tables_by_ethnicity$physical_activity$note,
+  col_spanners = model_tables_by_ethnicity$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r PA-by-sleep-duration-fig-by-ethnicity, fig.cap = "Physical activity by sleep duration moderated by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_duration_lag), error = FALSE)
+```
+
+### The effects of sleep efficiency on physical activity
+
+We estimated the effect of sleep efficiency on physical activity by ethnicity.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ethnicity).
+
+```{r PA-by-sleep-efficiency-fig-by-ethnicity, fig.cap = "Physical activity by sleep efficiency moderated by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_efficiency_lag), error = FALSE)
+```
+
+### The effects of sleep onset on physical activity
+
+We estimated the effect of sleep onset on physical activity by ethnicity.
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ethnicity).
+
+```{r PA-by-sleep-onset-fig-by-ethnicity, fig.cap = "Physical activity by sleep onset moderated by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_onset_lag), error = FALSE)
+```
+
+### The effects of sleep regularity on physical activity
+
+We estimated the effect of sleep regularity on physical activity by ethnicity.
+Results are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ethnicity).
+
+```{r PA-by-sleep-regularity-fig-by-ethnicity, fig.cap = "Physical activity by sleep regularity moderated by ethnicity"}
+knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_regularity_lag), error = FALSE)
+```

### 2023-04-14 _targets.R

@@ -58,6 +58,7 @@ list(
   #################################################################
   ##                          MODELLING                          ##
   #################################################################
+  tar_target(model_definitions, models_df),
   tar_map(
     values = models_df,
     names = model_name,
@@ -111,8 +112,9 @@ list(
   ),
   tar_target(multiverse_chunk, "doc/results_chunk.md", format = "file"),
   tar_target(multiverse_file,
-    make_multiverse_file(multiverse_skeleton, multiverse_chunk, models_df),
-    format = "file"
+    make_multiverse_file(
+      multiverse_skeleton, multiverse_chunk, model_definitions),
+    format = "file", priority = 1
   ),
   ### Produce supplementary material
   tar_render(multiverse, "doc/multiverse.Rmd", output_format = c(

### 2023-04-19 doc/multiverse.Rmd
Change PA-volume back to unlogged.

--- 2023-04-13 doc/multiverse.Rmd
@@
 
-## Without Log Transforming PA Volume
+## Log Transforming PA Volume
 
 ```{r}
-tar_load(model_tables_by_age_nolog)
-tar_load(purdy_pictures_by_age_nolog)
-```
-
-Based on preliminary modelling on a subset of the data, we chose to log transform the physical activity volume variable.
+tar_load(model_tables_by_age_log)
+tar_load(purdy_pictures_by_age_log)
+```
+
+Based on preliminary modelling on a subset of the data, we chose to leave physical activity volume in its natural form to enhance interpretability.
+The log scale meant that the variable became unintepretable towards the edge of its range.
 Below, we present the results had we not made this decision.
 These results are all moderated by age, as this was our primary analysis.
+The associated figures are back-transformed to the scale range.
 
@@
 We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-nolog) and Figure \@ref(fig:sleep-by-volume-fig-nolog).
-
-```{r sleep-outcomes-nolog}
-papaja::apa_table(
-  model_tables_by_age_nolog$sleep$data,
-  caption = model_tables_by_age_nolog$sleep$caption,
-  note = model_tables_by_age_nolog$sleep$note,
-  col_spanners = model_tables_by_age_nolog$sleep$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r sleep-by-volume-fig-nolog, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_pa_volume), error = FALSE)
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-log) and Figure \@ref(fig:sleep-by-volume-fig-log).
+
+```{r sleep-outcomes-log}
+papaja::apa_table(
+  model_tables_by_age_log$sleep$data,
+  caption = model_tables_by_age_log$sleep$caption,
+  note = model_tables_by_age_log$sleep$note,
+  col_spanners = model_tables_by_age_log$sleep$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r sleep-by-volume-fig-log, fig.cap = "Sleep metrics on Physical activity volume"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_pa_volume), error = FALSE)
 ```
@@
 We estimated the effect of sleep duration on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-duration-fig-nolog).
-
-```{r pa-outcomes-nolog}
-papaja::apa_table(
-  model_tables_by_age_nolog$physical_activity$data,
-  caption = model_tables_by_age_nolog$physical_activity$caption,
-  note = model_tables_by_age_nolog$physical_activity$note,
-  col_spanners = model_tables_by_age_nolog$physical_activity$col_spanners,
-  escape = FALSE,
-  landscape = TRUE
-)
-```
-
-```{r PA-by-sleep-duration-fig-nolog, fig.cap = "Physical activity by sleep duration"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_duration_lag), error = FALSE)
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-duration-fig-log).
+
+```{r pa-outcomes-log}
+papaja::apa_table(
+  model_tables_by_age_log$physical_activity$data,
+  caption = model_tables_by_age_log$physical_activity$caption,
+  note = model_tables_by_age_log$physical_activity$note,
+  col_spanners = model_tables_by_age_log$physical_activity$col_spanners,
+  escape = FALSE,
+  landscape = TRUE
+)
+```
+
+```{r PA-by-sleep-duration-fig-log, fig.cap = "Physical activity by sleep duration"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep efficiency on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-nolog).
-
-```{r PA-by-sleep-efficiency-fig-nolog, fig.cap = "Physical activity by sleep efficiency"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_efficiency_lag), error = FALSE)
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-log).
+
+```{r PA-by-sleep-efficiency-fig-log, fig.cap = "Physical activity by sleep efficiency"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep onset on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-onset-fig-nolog).
-
-```{r PA-by-sleep-onset-fig-nolog, fig.cap = "Physical activity by sleep onset"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_onset_lag), error = FALSE)
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-onset-fig-log).
+
+```{r PA-by-sleep-onset-fig-log, fig.cap = "Physical activity by sleep onset"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep regularity on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-regularity-fig-nolog).
-
-```{r PA-by-sleep-regularity-fig-nolog, fig.cap = "Physical activity by sleep regularity"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_regularity_lag), error = FALSE)
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-regularity-fig-log).
+
+```{r PA-by-sleep-regularity-fig-log, fig.cap = "Physical activity by sleep regularity"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-19 R/models.R

@@ -1,6 +1,6 @@
 # Model parameters
-dflt_pa <- c("log_pa_volume", "scale_pa_intensity")
-scale_pa <- c("scale_pa_volume", "scale_pa_intensity")
+dflt_pa <- c("scale_pa_volume", "scale_pa_intensity")
+log_pa <- c("log_pa_volume", "scale_pa_intensity")
 dflt_sleep <- c(
   "scale_sleep_duration", "scale_sleep_efficiency", "scale_sleep_onset",
   "scale_sleep_regularity"
@@ -14,7 +14,7 @@ models_df <- dplyr::tribble(
   ~model_name,          ~moderator,        ~mod_term,        ~mod_formal,        ~pa_vars, ~sleep_vars, ~ranef,     ~cont_vars,
   "by_age",             "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
   "by_age_fixedef",     "age",             "11, 18, 35, 65", "age",              dflt_pa,  dflt_sleep,  fixedef,    c(dflt_con, "studyid"),
-  "by_age_nolog",       "age",             "11, 18, 35, 65", "age",              scale_pa, dflt_sleep,  dflt_ranef, dflt_con,
+  "by_age_log",         "age",             "11, 18, 35, 65", "age",              log_pa,   dflt_sleep,  dflt_ranef, dflt_con,
   "by_bmi",             "bmi",             "18, 22, 25, 30", "BMI",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
   "by_ses",             "ses",             "all",            "SES",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,
   "by_sex",             "sex",             "all",            "sex",              dflt_pa,  dflt_sleep,  dflt_ranef, dflt_con,

### 2023-04-19 R/produce_purdy_pictures.R

@@ -40,7 +40,7 @@ produce_purdy_pictures <- function(model_list, ...) {
     tile_dat <- tile_dat |>
       prepare_plot_data(paste_facet_labels,
                         scale_descriptives = attr(model_list, "scale_descriptives"),
-                        debug = FALSE)
+                        debug = TRUE)
 
     tile_dat$includes_zero <- tile_dat$conf.low <= 0 & tile_dat$conf.high >= 0
     tile_dat$predicted[tile_dat$includes_zero == TRUE] <- 0

### 2023-04-19 R/utils.R

@@ -20,8 +20,6 @@ load_packages <- function() {
   invisible(source("./packages.R"))
 }
 
-
-
 #' figure_theme
 #'
 #' Attractive ggplot2 theme defaults

### 2023-04-19 _targets.R

@@ -94,7 +94,7 @@ list(
     make_model_diagnostics(
       model_list_by_age,
       model_list_by_age_fixedef,
-      model_list_by_age_nolog,
+      model_list_by_age_log,
       model_list_by_bmi,
       model_list_by_ses,
       model_list_by_weekday,

### 2023-04-21 doc/multiverse_skeleton.Rmd
Generate presentation names for tables. Back transform figs (#90)
* Generate presentation names for tables.

* Send scale var descriptives down with the model_list for exact transformation.

* Back transform figures.

* Increase range of variables to facilitate back-transformed variables.

* Fix kurtosis, set range for tile plots.

* Change PA-volume back to unlogged.

* Clean up empty function.

@@
 
-## Without Log Transforming PA Volume
+## Log Transforming PA Volume
 
 ```{r}
-tar_load(model_tables_by_age_nolog)
-tar_load(purdy_pictures_by_age_nolog)
+tar_load(model_tables_by_age_log)
+tar_load(purdy_pictures_by_age_log)
 ```
 
-Based on preliminary modelling on a subset of the data, we chose to log transform the physical activity volume variable.
+Based on preliminary modelling on a subset of the data, we chose to leave physical activity volume in its natural form to enhance interpretability.
+The log scale meant that the variable became unintepretable towards the edge of its range.
 Below, we present the results had we not made this decision.
 These results are all moderated by age, as this was our primary analysis.
+The associated figures are back-transformed to the scale range.
 
@@
 We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
-We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-nolog) and Figure \@ref(fig:sleep-by-volume-fig-nolog).
+We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-log) and Figure \@ref(fig:sleep-by-volume-fig-log).
 
-```{r sleep-outcomes-nolog}
+```{r sleep-outcomes-log}
 papaja::apa_table(
-  model_tables_by_age_nolog$sleep$data,
-  caption = model_tables_by_age_nolog$sleep$caption,
-  note = model_tables_by_age_nolog$sleep$note,
-  col_spanners = model_tables_by_age_nolog$sleep$col_spanners,
+  model_tables_by_age_log$sleep$data,
+  caption = model_tables_by_age_log$sleep$caption,
+  note = model_tables_by_age_log$sleep$note,
+  col_spanners = model_tables_by_age_log$sleep$col_spanners,
   escape = FALSE,
@@
 
-```{r sleep-by-volume-fig-nolog, fig.cap = "Sleep metrics on Physical activity volume"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_pa_volume), error = FALSE)
+```{r sleep-by-volume-fig-log, fig.cap = "Sleep metrics on Physical activity volume"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_pa_volume), error = FALSE)
 ```
@@
 We estimated the effect of sleep duration on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-duration-fig-nolog).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-duration-fig-log).
 
-```{r pa-outcomes-nolog}
+```{r pa-outcomes-log}
 papaja::apa_table(
-  model_tables_by_age_nolog$physical_activity$data,
-  caption = model_tables_by_age_nolog$physical_activity$caption,
-  note = model_tables_by_age_nolog$physical_activity$note,
-  col_spanners = model_tables_by_age_nolog$physical_activity$col_spanners,
+  model_tables_by_age_log$physical_activity$data,
+  caption = model_tables_by_age_log$physical_activity$caption,
+  note = model_tables_by_age_log$physical_activity$note,
+  col_spanners = model_tables_by_age_log$physical_activity$col_spanners,
   escape = FALSE,
@@
 
-```{r PA-by-sleep-duration-fig-nolog, fig.cap = "Physical activity by sleep duration"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_duration_lag), error = FALSE)
+```{r PA-by-sleep-duration-fig-log, fig.cap = "Physical activity by sleep duration"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_duration_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep efficiency on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-nolog).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-log).
 
-```{r PA-by-sleep-efficiency-fig-nolog, fig.cap = "Physical activity by sleep efficiency"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_efficiency_lag), error = FALSE)
+```{r PA-by-sleep-efficiency-fig-log, fig.cap = "Physical activity by sleep efficiency"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_efficiency_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep onset on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-onset-fig-nolog).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-onset-fig-log).
 
-```{r PA-by-sleep-onset-fig-nolog, fig.cap = "Physical activity by sleep onset"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_onset_lag), error = FALSE)
+```{r PA-by-sleep-onset-fig-log, fig.cap = "Physical activity by sleep onset"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_onset_lag), error = FALSE)
 ```
@@
 We estimated the effect of sleep regularity on physical activity by age.
-Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-regularity-fig-nolog).
+Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-regularity-fig-log).
 
-```{r PA-by-sleep-regularity-fig-nolog, fig.cap = "Physical activity by sleep regularity"}
-knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_regularity_lag), error = FALSE)
+```{r PA-by-sleep-regularity-fig-log, fig.cap = "Physical activity by sleep regularity"}
+knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_regularity_lag), error = FALSE)
 ```

### 2023-04-21 R/make_model_diagnostics.R

@@ -67,7 +67,7 @@ check_resids <- function(model){
   dt <- model |> lapply(function(x){
     resid <- residuals(x)
     tibble(Skewness = moments::skewness(resid),
-           Kurtosis = 3 - moments::kurtosis(resid))
+           Kurtosis = moments::kurtosis(resid) - 3)
 
   }) |> data.table::rbindlist()
   dt[, lapply(.SD, function(x) mean(x, na.rm = TRUE))]

### 2023-04-21 R/make_model_list.R

@@ -23,6 +23,11 @@ make_model_list <- function(data_imp,
 
   sleep_lag_vars <- paste0(sleep_vars, "_lag")
 
+  # Apply display names
+  names(sleep_vars) <- display_names(sleep_vars)
+  names(sleep_lag_vars) <- display_names(sleep_lag_vars)
+  names(pa_vars) <- display_names(pa_vars)
+
   quadratic_pattern <- "{x} * {moderator} + I({x}^2) * {moderator}"
   make_quadratic <- function(x) glue::glue(quadratic_pattern)
 
@@ -61,7 +66,7 @@ make_model_list <- function(data_imp,
         ranef = ranef,
         terms = c(
           paste0(
-            gsub(" .*", "", instructions[i, "predictors"]), "[-4:4 by = 0.1]"),
+            gsub(" .*", "", instructions[i, "predictors"]), "[-5:5 by = 0.05]"),
           glue::glue("{moderator} [{moderator_term}]")
         ),
         RQ = instructions[i, "RQ"]
@@ -77,6 +82,7 @@ make_model_list <- function(data_imp,
   # Add some attributes used in other targets
   names(out) <- instructions[, "model_name"]
   attr(out, "vars") <- list(sleep_vars = sleep_vars, pa_vars = pa_vars)
+  attr(out, "scale_descriptives") <- get_scale_descriptives(data_imp, sleep_vars, sleep_lag_vars, pa_vars)
   attr(out, "filename_suffix") <-
     dplyr::case_when(
       "studyid" %in% control_vars ~ "_fixedef",
@@ -86,3 +92,4 @@ make_model_list <- function(data_imp,
 
   out
 }
+

### 2023-04-21 R/model_builder.R

@@ -141,7 +141,7 @@ model_builder <-
     if(moderator == "age"){
       predictor_term <- terms[1]
       predictor_term <- gsub("\\[.*","",predictor_term)
-      predictor_term <- paste0(predictor_term,"[-4:4 by=0.1]")
+      predictor_term <- paste0(predictor_term,"[-5:5 by=0.1]")
       pred_mat <- get_effects(m,
                   moderator = "age",
                   terms = c(predictor_term, "age[10:80 by = 1]"),

### 2023-04-21 R/produce_purdy_pictures.R

@@ -26,7 +26,7 @@ produce_purdy_pictures <- function(model_list, ...) {
   }
 
   plot_dat <- data.table::rbindlist(dat_list) |>
-    prepare_plot_data(paste_facet_labels)
+    prepare_plot_data(paste_facet_labels, scale_descriptives = attr(model_list, "scale_descriptives"))
 
   # Im the moderator is age, then, retrieve granular age predictions
 
@@ -35,18 +35,24 @@ produce_purdy_pictures <- function(model_list, ...) {
       model_list[[i]]$model_assets$pred_matrix
     }) |> rbindlist()
     tile_dat$group <- as.numeric(tile_dat$group)
-    tile_dat$includes_zero <- tile_dat$conf.low <= 0 & tile_dat$conf.high >= 0
     # hide non-sig predictions
+
+    tile_dat <- tile_dat |>
+      prepare_plot_data(paste_facet_labels,
+                        scale_descriptives = attr(model_list, "scale_descriptives"),
+                        debug = TRUE)
+
+    tile_dat$includes_zero <- tile_dat$conf.low <= 0 & tile_dat$conf.high >= 0
     tile_dat$predicted[tile_dat$includes_zero == TRUE] <- 0
     tile_dat$predicted[tile_dat$predicted >= 2] <- 2
     tile_dat$predicted[tile_dat$predicted <= -2] <- -2
-    tile_dat <- tile_dat |> prepare_plot_data(paste_facet_labels)
   }
 
   # Plotting function
   require(ggplot2)
 
   p <- function(x_var, x_lab, rq) {
+
     pdat <- plot_dat[x_name == x_var & RQ == rq]
 
     conv_message_dat <- unique(pdat[, c("outcome", "group", "message")])
@@ -67,8 +73,8 @@ produce_purdy_pictures <- function(model_list, ...) {
       ) +
       figure_theme() +
       theme(legend.position = "none") +
-      scale_x_continuous(limits = c(-4, 4)) +
-      scale_y_continuous(limits = c(-4, 4)) +
+      scale_x_continuous(limits = c(-2, 2)) +
+      scale_y_continuous(limits = c(-2, 2)) +
       geom_text(
         data = conv_message_dat, aes(x = 0, y = 0, label = message, ),
         hjust = .5, vjust = .5, size = 2, color = "black", family = "serif",
[…]

### 2023-04-21 R/utils.R

@@ -20,8 +20,6 @@ load_packages <- function() {
   invisible(source("./packages.R"))
 }
 
-
-
 #' figure_theme
 #'
 #' Attractive ggplot2 theme defaults
@@ -89,4 +87,69 @@ get_season <- function(date, lat){
 }
 
 find_max  <- function(x) {names(which.max(table(x)))}
+
+#' Generates display names for variables
+#' @param x a list containing variables e.g. pa_vars
+
+display_names <- function(x){
+
+  is_scale <- grepl("^scale",x)
+  is_log <- grepl("^log",x)
+
+  out <- gsub("(scale_|log_)", "", x) |>
+    gsub("_", " ", x = _) |>
+    gsub("pa","physical activity", x = _) |>
+    stringr::str_to_sentence()
+
+  out[is_scale] <- paste(out[is_scale], "(z)")
+  out[is_log] <- paste(out[is_log], "(ln)")
+  out
+
+}
+
+#' get_scale_descriptives
+#'
+#' Get descriptives for multiply imputed data for scale variables
+
+get_scale_descriptives <- function(data, ...) {
+  vars <- unlist(list(...))
+  # We want descriptives to convert log back to scale
+  # So we need the scale descriptives, not the log descriptives
+  vars <- gsub("(log_|scale_)", "", vars)
+  dat <- mice::complete(data, action = "long", include = FALSE) |>
+    data.table()
+
+  # Get all imp data, make long form
+  dt <- dat[, c(vars, ".imp"), with = FALSE] |>
+    tidyr::pivot_longer(-.imp, names_to = "var") |>
+    data.table()
+  # get mean and sd by variable and imp
+  dt_2 <- dt[, .(mean = mean(value, na.rm = TRUE),
+                 sd = sd(value, na.rm = TRUE)) , by = c(".imp", "var")] |>
+    tidyr::pivot_longer(-c(.imp, var)) |>
+    data.table()
+
+  # get mean of each mean and sd across imps
+  descriptives <-
+    dt_2[, .(value = mean(value)), by = c("name", "var")] |>
+    tidyr::pivot_wider(values_from = value, names_from = name) |>
+    data.table()
+
+  descriptives
+
+}
+
+plot_percentile <- function(var){
+  require(ggplot2)
+
+  p <- lapply(seq(0,1,by = 0.005), function(x){
+    data.frame(p = x*100, value = quantile(var, x, na.rm = TRUE))
+
[…]

### 2023-04-21 _targets.R

@@ -95,7 +95,7 @@ list(
     make_model_diagnostics(
       model_list_by_age,
       model_list_by_age_fixedef,
-      model_list_by_age_nolog,
+      model_list_by_age_log,
       model_list_by_bmi,
       model_list_by_ses,
       model_list_by_weekday,

### 2023-12-14 doc/manuscript.Rmd
Adjust manuscript to match results

@@
 pretty <- function(x) format(x, big.mark = ",")
-
 ```
@@
 weekday <- chisq.test(weekday_table)
-weekday_res <-glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")
-
+weekday_res <- glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")
 ```
@@
 We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
-There was no meaningful relationship between physical activity volume and sleep duration.
-However, we observed a curvilinear relationships between physical activity volume and sleep efficiency, onset, and regularity, all of which interacted with age.
-Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
-Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
+There was no meaningful relationship between physical activity volume and sleep duration or sleep efficiency.
+Physical activity volume and sleep onset had a very weak positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
 There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
@@
 We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
-We found that higher physical activity intensity is directly proportional to longer sleep duration and better sleep efficiency.
-In the case of older participants, physical activity intensity had a U-shaped relationship with sleep onset, meaning that individuals with very low or very high physical activity intensity had longer sleep onset.
-We also found a strong link between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
+We found no evidence that physical activity intensity is related to sleep duration, sleep efficiency, or sleep onset.
+However, we did find evidence for an association between physical activity intensity and improved sleep regularity, which weakened at higher intensity levels.
 
@@
 
-We estimated the effect of sleep duration on physical activity by age
+We estimated the effect of sleep duration on physical activity by age.
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
 As age increases, both physical activity volume and intensity decrease.
-We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.
+We found no evidence for an association between average sleep duration and physical activity volume.
 
@@
 We did not find a relationship between physical activity volume and sleep efficiency.
-However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.
+However, there was a weak linear association between sleep efficiency and more intense physical activity.
 
@@
 Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
-There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
+There were weak curvilinear relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
 The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.
@@
 Increases in regularity above the average were linked to greater physical activity volume.
-There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
+There was a linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
 Greater sleep regularity was associated with greater physical activity the following day.
